---
title: "interation-analysis"
author: "Olivier GAUFRÈS"
date: "2024-04-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)
library(lubridate)
library(ggplot2)
```

## File paths
```{r}
wd <- getwd()
knitr::opts_chunk$set(root.dir = wd)
observed_path <- file.path(wd,"..", "..", "data","data-observed")
synthetic_path <- file.path(wd, "..", "..", "data", "data-synthetic-graphs")
simplified_path <- file.path(wd, "..", "..", "data", "data-simplified")
expanded_path <- file.path(wd,"..", "..", "data","data-expanded")
```

## i-Bird study data
```{r}
begin_date <- as.POSIXct("2009-07-06 00:00:00", tz="GMT")
end_date <- as.POSIXct("2009-09-28 00:00:00", tz="GMT")
time_spent <- end_date - begin_date
n_subdivisions <- as.integer(time_spent) * 24 * 60 * 2 ## Time spent * hours * minutes * 2 (number of time subdivisions)
```

## Data import
```{r}
## NA when the individual is still in the hospital --> we fill these NAs
admission <- read.csv2(file = file.path(simplified_path, "admission.csv"))
admission <- admission %>% mutate(lastDate = ifelse(nchar(lastDate) == 0, "2999-01-01", lastDate))
admission <- admission %>% mutate(firstDate = as.POSIXct(firstDate, tz="GMT"), lastDate = as.POSIXct(lastDate, tz="GMT") ) 
admission <- admission %>% filter(!lastDate < begin_date)  ## unnecessary data
admission <- admission %>% filter(!firstDate > end_date) ## unnecessary data


## id of all individuals in the 84 days range
id_individual <- admission %>% distinct(id)

## MENARD 1 HAS 28 BEDS
n_beds <- 28

## Observed data from i-Bird study
data <- read.csv2(file = file.path(simplified_path, "mat_ctc.csv"), header = TRUE, sep = ";") %>% 
                      mutate(date_posix = as.POSIXct(date_posix, tz="GMT"))
                      #mutate(date_posix = format(as.POSIXct(date_posix, tz="GMT"), format="%Y-%m-%d %H:%M:%S")) ##TEMPORARY, FIX TO AVOID YYYY-MM-DD 00:00:00 formated as YYYY-MM-DD



## Date range of 84 days ($time_spent)
data <- data  %>% filter(date(date_posix) <= date(end_date))%>% filter(date(date_posix) >= date(begin_date))
```


## Interaction's duration of 30sec
```{r}
k_30 = data %>% filter(length == 30) %>% mutate(from = gsub("-.*", "", from), to = gsub("-.*", "", to)) %>% select(-date_posix)
print("Interaction's duration of 30sec")
table(k_30$from, k_30$to)

## Proportions of interaction of 30s in all the int
print("Proportions of interaction of 30s")
prop.table(table(k_30$from, k_30$to))


print("Proportions of 30s int in all the int")
print(paste0(nrow(k_30)/nrow(data) * 100, " %"))
rm(k_30)
```


## Interaction's duration < 300sec
```{r}
k_300= data %>% filter(length < 300) %>% mutate(from = gsub("-.*", "", from), to = gsub("-.*", "", to)) %>% select(-date_posix)
prop.table(table(k_300$from, k_300$to))

print("Proportions of interaction < 300s in all the int")
print(paste0(nrow(k_300)/nrow(data) * 100, " %"))
rm(k_300)
```





## ROOM INFERENCE BASED ON NIGHT INTERACTIONS






## Night interactions (22pm-6am)
```{r}
night_data <- data  %>%
  filter(hour(data$date_posix) <= 5 | hour(data$date_posix) >= 22) 

## Check if there is PE in night's interactions
which(substr(night_data$from, 1, 2) == "PE" | substr(night_data$to, 1, 2) == "PE" )

## Filter to keep only long interactions
night_data <- data %>%
  filter(length >= 300)
```


```{r}
tot <- NULL
## Range of amount of interactions happening at night + distinct individuals involved + number of days there is less than n_beds individuals interacting at night
for (i in 0:60){
  temp <- data  %>% filter(hour(data$date_posix) <=  5 | hour(data$date_posix) >= 22)  %>%
  filter (length >= 60 * 5 * i) %>%
  group_by(date(date_posix)) %>%
  summarise(count = n(), count_distinct = length(unique(c(from, to)))) %>%
  summarise(min_count = min(count),
            median_count = median(count),
            max_count = max(count),
            min_distinct = min(count_distinct),
            median_distinct = median(count_distinct),
            max_distinct = max(count_distinct),
            count_under_beds = sum((count_distinct) < n_beds)
            )
  
  temp$time_night_s <- 60 * 5 * i
  temp$time_night_min <- i * 5
  tot <- bind_rows(tot, temp)
  rm(temp)
}

tot <- tot %>% select(time_night_min,
                      min_count,
                      median_count,
                      max_count,
                      min_distinct,
                      median_distinct,
                      max_distinct,
                      count_under_beds)


## ELBOW RULE TO FIND TIME

ggplot(data = tot[1:30,]) +
#ggplot(data = tot) +
  geom_point(mapping = aes(x = time_night_min, y = min_count, color = "Minimum Count"), show.legend = TRUE) +
  geom_line(mapping = aes(x = time_night_min, y = min_count), linetype = "dashed") +
  
  geom_point(mapping = aes(x = time_night_min, y = max_count, color = "Maximum Count"), show.legend = TRUE) +
  geom_line(mapping = aes(x = time_night_min, y = max_count), linetype = "dashed") +
  
  geom_point(mapping = aes(x = time_night_min, y = min_distinct, color = "Minimum Distinct"), show.legend = TRUE) +
  geom_line(mapping = aes(x = time_night_min, y = min_distinct), linetype = "dashed") +
  
  geom_point(mapping = aes(x = time_night_min, y = max_distinct, color = "Maximum Distinct"), show.legend = TRUE) +
  geom_line(mapping = aes(x = time_night_min, y = max_distinct), linetype = "dashed") +
  
  scale_color_manual(values = c("Minimum Count" = "red", 
                                 "Maximum Count" = "darkred",
                                 "Minimum Distinct" = "blue",
                                 "Maximum Distinct" = "darkblue")) +
  labs( x = "Time (min)", y = "Interactions (red) & Distinct individuals (blue)") +
  labs(title = "Interactions at night in Menard 1") +
  scale_y_continuous(trans = "log10") +
  theme(legend.position = "top")

print(tot)

## issue w/ the colors???


```

## Filtration according to these assumptions
```{r}
## WE CHOOSE TO HAVE MORE INTERACTIONS THAN DISTINCT INDIVIDUALS INTERACTING
## WE CHOOSE TO SET THE THRESHOLD OF LENGTH FOR A NIGHT INTERACTION TO 40 minutes -> 2400 seconds

length_thresold <- 40 * 60
hour_thresold <- 5


## TEMP
# admission$id == ind & between(date_posix, lastDate, firstDate) # --> check which admission of the individual is 
admission <- admission %>% mutate(room = NA)









## ALL INTERACTIONS
for (ind in id_individual %>% filter(substr(id,1,2) == "PA") %>% pull(id)){
  #all_ind <- data %>% filter(length > length_thresold & hour(date_posix) < hour_thresold) %>% filter(from == ind | to == ind) ## SOME IND DONT HAVE INT DURING NIGHT
  all_ind <- data  %>% filter(from == ind | to == ind)
  for (adm in seq_len(admission %>% filter(id == ind) %>% nrow())) {
    date_adm <- admission %>% filter(id == ind) %>% nth(adm) %>% pull(firstDate)
    date_departure <- admission %>% filter(id == ind) %>% nth(adm) %>% pull(lastDate)
    assign(paste0("int_",adm), all_ind %>% filter(between(date_posix, date_adm, date_departure)))
    print(paste0("ALL INTERACTIONS : ", ind," -> ",adm, " nb int = ", all_ind %>% filter(between(date_posix, date_adm, date_departure) ) %>% nrow()))
    
    if(all_ind %>% filter(between(date_posix, date_adm, date_departure) ) %>% nrow() == 0){
      print(paste0("Individual id: ", ind, " has 0 interaction during his admission n° ", adm))
    }
  }
}
```


## CUMULATIVE TIME OF NIGHT INTERACTION FOR EACH INDIVIDUAL
```{r}
ind_NA <- list()
df_night <- data.frame()
df_alone <- data.frame()
for (ind in id_individual %>% filter(substr(id,1,2) == "PA") %>% pull(id)){
  night_ind <- data %>% filter((hour(date_posix) < hour_thresold | hour(date_posix) > 21)) %>% filter(from == ind | to == ind)
  night_ind <- night_ind %>%  filter(length > 2*3600)
  for (adm in seq_len(admission %>% filter(id == ind) %>% nrow())) {
    date_adm <- admission %>% filter(id == ind) %>% nth(adm) %>% pull(firstDate)
    date_departure <- admission %>% filter(id == ind) %>% nth(adm) %>% pull(lastDate)
    
    int_ind_adm <- night_ind %>% filter(between(date_posix, date_adm, date_departure))
    
    int_median <- night_ind %>%
      filter(between(date_posix, date_adm, date_departure) ) %>%
      group_by(date(date_posix)) %>%
      summarise(count = n()) %>%
      summarise(median_count =median(count)) %>%
      pull()
    
    unique_ind_adm <- unique(c(int_ind_adm$from,int_ind_adm$to))
    
    for (ind_adm in unique_ind_adm[which(unique_ind_adm != ind)]){
      cumulated_time_ind_adm <- int_ind_adm %>%
        filter(from == ind_adm | to == ind_adm) %>%
        select(-c("from","to")) %>%
        group_by(date(date_posix)) %>%
        summarise(sum_l = sum(length))
  
      df_night <- bind_rows(df_night, data.frame(id1 = ind, date = cumulated_time_ind_adm$`date(date_posix)` , admis = adm, id2 = ind_adm, cumulative_length = cumulated_time_ind_adm$'sum_l'))
    }

    if(night_ind %>% filter(between(date_posix, date_adm, date_departure) ) %>% nrow() == 0){
      #print(paste0("Individual id: ", ind, " has 0 interaction during night in his admission n° ", adm))
      df_alone <- bind_rows(df_alone, dataframe(id1 = ind, status = "alone"))
    }
  }
}

for (ind in (df_night %>% distinct(id1) %>% pull(id1))){
  print(paste0(ind, " :  ", df_night %>% filter(id1 == ind) %>% distinct(id2) %>% nrow()))
  
}

##CONC
df_night_cumulative <- df_night %>% group_by(id1) %>%  group_by(id2, .add = TRUE) %>% summarise(cum_len_id = sum(cumulative_length)) %>% ungroup()


#View(df_night %>% filter(id1 == "PA-001-LAM"))
#View(df_night %>% filter(id1 == "PA-001-LAM") %>% group_by(id2) %>% summarise(cum_len_id = sum(cumulative_length)) %>% ungroup())
```





```{r}
all_individuals <- unique(c(df_night_cumulative$id1, df_night_cumulative$id2))

# Initialiser une liste vide pour stocker les classements
ranking_list <- list()

# Boucle à travers chaque individu
for (ind in all_individuals) {
  # Sélectionner les lignes où l'individu est impliqué
  interactions <- df_night_cumulative[df_night_cumulative$id1 == ind | df_night_cumulative$id2 == ind, ]
  # Calculer le temps total passé avec chaque individu
  total_time <- aggregate(cum_len_id ~ ifelse(id1 == ind, id2, id1), data = interactions, sum)
  # Renommer les colonnes pour plus de clarté
  names(total_time) <- c("other_individual", "total_time_with_individual")
  # Trier les individus par temps passé
  total_time <- total_time[order(-total_time$total_time_with_individual), ]
  # Ajouter le classement à la liste
  ranking_list[[as.character(ind)]] <- total_time
}

#Example
print(ranking_list[["PA-008-SLP"]])
```








```{r}
stable_marriage <- function(ranking_list) {
  engagements <- list()
  engaged <- vector(mode = "logical", length = length(ranking_list))
  
  while (!all(engaged)) {
    proposer <- which(!engaged)[1]
    # Sélectionner les personnes avec lesquelles il n'est pas encore engagé et qui sont classées
    candidates <- ranking_list[[proposer]]$other_individual[ranking_list[[proposer]]$other_individual %in% names(engagements)]
    for (candidate in candidates) {
      if (!candidate %in% names(engagements)) {
        engagements[[as.character(proposer)]] <- candidate
        engagements[[as.character(candidate)]] <- proposer
        engaged[proposer] <- TRUE
        engaged[candidate] <- TRUE
        break
      } else {
        if (which(ranking_list[[candidate]]$other_individual == proposer) < which(ranking_list[[candidate]]$other_individual == engagements[[as.character(candidate)]])) {
          engaged[as.numeric(engagements[[as.character(candidate)]])] <- FALSE
          engagements[[as.character(proposer)]] <- candidate
          engagements[[as.character(candidate)]] <- proposer
          engaged[proposer] <- TRUE
          break
        }
      }
    }
  }
  
  return(engagements)
}

# Utiliser l'algorithme de mariage stable avec le classement des individus
result <- stable_marriage(ranking_list)
```




```{r}
View(data %>% filter(from == "PA-053-CHK" | to == "PA-053-CHK") %>% filter(substr(from,1,2) == "PA" & substr(to,1,2) == "PA") %>% filter((hour(date_posix) < hour_thresold | hour(date_posix) > 21))  )
#(paste0("NIGHT TIME : ", ind," -> ",adm, " nb int = ", night_ind %>% filter(between(date_posix, date_adm, date_departure) ) %>% nrow()))
```



```{r}
## Inspection (for 1 day = begin_date)
test_graph <- data  %>%
  filter(hour(data$date_posix) <= hour_thresold) %>%
  filter(length >= length_thresold) %>% filter( date(date_posix) == date(begin_date)) 

## Nb of interactions during the night & distinct individuals involved
print (data  %>%
  filter(hour(data$date_posix) <= hour_thresold) %>%
  filter(length >= length_thresold) %>% filter( date(date_posix) == date(begin_date)) %>%
  group_by(date(date_posix)) %>%
  summarise(count = n(), count_distinct = length(unique(c(from, to)))))


id_unique <- sort(unique(c(test_graph$from,test_graph$to)))


## INDIVIDUALS IN THE WARD ACCORDING TO ADMISSION DATA
id_present <- admission_modified %>% filter(firstDate <= begin_date & lastDate >= begin_date + days(1)) %>% distinct(id) %>% filter(substr(id,1,2) == "PA")

date_distinct <- data %>% group_by(date(date_posix)) %>% select(-c(from,to,length,date_posix)) %>% distinct()

interaction_list <- list()



for (ide in test_unique) {
df_id_time <- test_graph[test_graph$from == ide | test_graph$to == ide, ]
interaction_list[[paste0("int_", ide)]] <- df_id_time
}


data_nuit <- data  %>%
  filter(hour(data$date_posix) <= hour_thresold) %>%
  filter(length >= length_thresold)

```

```{r}
#####data %>% filter(id == "PA-001-LAM") %>% filter(date_posix <= begin_date )
```

