---
title: "Interaction-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-05-03"
output: html_document
---


## Libraries
```{r setup, include=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(tidyr)
library(viridis)
library(purrr)
library(igraph)
library(ggtext)
library(ggnetwork)
rm(list = ls())

# Source functions, dictionaries and helpful variables
source("helper-functions.R")

# Working directories and paths
nodscov2_path = file.path("..", "..", "data", "data-nodscov2") 
synthetic_path = file.path("..", "..", "data", "data-synthetic-graphs")
fig_path = file.path("..", "..", "fig")
```

## Load Nods-CoV-2 data (not shared)
```{r load data, echo=FALSE}
# Admission dates
load(file.path(nodscov2_path, "raw", "admission_ctc_nodscov2.RData"))
Encoding(admission$hospital) <- 'latin1'

# Interactions 
list_ward = read.csv(file.path(nodscov2_path, "raw", "list_ward_complete.csv")) %>%
  rename(date_posix = date_posix_first)

# Sensor distribution 
sensor = read.csv(file.path(nodscov2_path, "raw", "met_timespent_mins_complete.csv"))

# Change id of individuals to add PA- or PE- suffix
sensor = sensor %>% 
  left_join(., admission %>% select(id, status), by = "id") %>%
  mutate(id = paste0(status, "-", id)) %>%
  select(-status)

list_ward = list_ward %>%
  left_join(., admission %>% select(id, status), by = c("from"="id")) %>%
  mutate(from = paste0(status, "-", from)) %>%
  select(-status) %>%
  left_join(., admission %>% select(id, status), by = c("to"="id")) %>%
  mutate(to = paste0(status, "-", to)) %>%
  select(-status)

admission = admission %>% mutate(id = paste0(status, "-", id))
```

## Initial composition of Raymond Poincaré ICU
```{r initial composition}
# Number of participants
# Investigation staff are excluded as they were part of the staff deploying the sensors
# and do not belong to the medical wards per se
admission %>%
  filter(hospital == "APHP - RAYMOND POINCARÉ", ward == "Reanimation", !cat %in% "investigation") %>%
  distinct(id) %>%
  nrow()

# Number of participants by individual category
admission %>%
  filter(hospital == "APHP - RAYMOND POINCARÉ", ward == "Reanimation", !cat %in% "investigation") %>%
  group_by(status, cat) %>%
  summarize(n = n(), .groups = "drop")

```

## Create input dataframes for the synthetic network algorithm 
### Create admission and sensor dataframes
```{r synthetic data}
# Create dataframe with admission dates for the synthetic network algorithm
admission_nodscov2 = admission %>%
  filter(
    hospital == "APHP - RAYMOND POINCARÉ", 
    ward == "Reanimation",
    cat %in% names(dict_cat) | is.na(cat)
    ) %>%
  mutate(cat = recode(cat, !!!dict_cat)) %>%
  mutate(cat = ifelse(is.na(cat), "Patient", cat)) %>%
  select(-hospital)
nrow(admission_nodscov2) # Number of individuals in the database after filtering

# Sensor distribution data 
# Keep individuals from the ICU of Raymond Poincaré
sensor_nodscov2 = sensor %>%
  mutate(
    DATEREMISEJ1 = as_datetime(DATEREMISEJ1),
    DATERECJ1 = as_datetime(DATERECJ1),
    DATEREMISEJ2 = as_datetime(DATEREMISEJ2),
    DATERECJ2 = as_datetime(DATERECJ2),
    J1 = as_datetime(J1),
    N1 = as_datetime(N1),
    J2 = as_datetime(J2),
    N2 = as_datetime(N2),
    firstDate_sensor = as.Date(cut(DATEREMISEJ1, "day")), 
    lastDate_sensor = as.Date(case_when(is.na(DATERECJ2) ~ cut(DATERECJ1, "day"), .default = cut(DATERECJ2, "day")))
  ) %>%
  select(id, DATEREMISEJ1, DATERECJ1, DATEREMISEJ2, DATERECJ2) %>%
  pivot_longer(-id, names_to = c(".value", "Day"), names_sep = "J") %>% 
  rename(firstDate_sensor = DATEREMISE, lastDate_sensor = DATEREC) %>%
  mutate(ward = "Reanimation") %>%
  inner_join(., admission_nodscov2 %>% select(id, status, cat), by = "id") %>%
  select(id, status, cat, ward, firstDate_sensor, lastDate_sensor) %>%
  filter(!is.na(lastDate_sensor), !is.na(firstDate_sensor))

length(unique(admission_nodscov2$id)) - length(unique(sensor_nodscov2$id)) # Individuals with no sensor during the study period
```

### Explore interaction data  
```{r}
# Rearrange interaction data 
verify_pair_distribution = list_ward %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  filter(
    # Raymond Poincaré ICU
    newID == "Medical ICU #1",
    # Only categories of interest
    from %in% sensor_nodscov2$id, to %in% sensor_nodscov2$id,
    ) %>%
  group_by(from, to, date_posix, ward_id, wardType, newID) %>%
  summarise(length = max(length), .groups = "drop") %>%
  distinct() %>%
  mutate(id = 1:n()) %>%
  nest(.by = id) %>%
  mutate(data = map(data, get_pair_id)) %>%
  unnest(data) 

# Get number of pairs that are not stored with the correct ids 
verify_pair_distribution %>%
  distinct(from, to, pair) %>%
  group_by(pair) %>%
  mutate(n = n()) %>%
  filter(n>1) %>%
  nrow()

# Get number of overlapping contacts (duplicates and starting at the same time are not included)
verify_pair_distribution %>%
  nest(.by = c(from, to, ward_id, wardType, newID)) %>%
  mutate(data = map(data, get_overlapping_contacts)) %>%
  unnest(data) %>%
  filter(overlap == T) %>%
  nrow()

# Save overlapping and duplicated contacts
list_ward %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  filter(
    # Raymond Poincaré ICU
    newID == "Medical ICU #1",
    # Only categories of interest
    from %in% sensor_nodscov2$id, to %in% sensor_nodscov2$id
    ) %>%
  nest(.by = c(from, to, ward_id, wardType, newID)) %>%
  mutate(data = map(data, get_overlapping_contacts)) %>%
  unnest(data) %>%
  filter(overlap == T) %>%
  arrange(from, to, date_posix) %>%
  select(from, to, date_posix, length, ward_id, wardType, newID) %>%
  write.csv2(file.path(nodscov2_path, "raw", "duplicated_and_overlaping_contacts.csv"), quote = F, row.names = F)

```

### Create cleaned admission, schedule and interaction data 
````{r}
# Interaction data from Raymond Poincaré
interaction_nodscov2 = list_ward %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  filter(
    # Raymond Poincaré ICU
    newID == "Medical ICU #1",
    # Only categories of interest
    from %in% sensor_nodscov2$id, to %in% sensor_nodscov2$id
    ) %>%
  # Keep longest contacts when several start at the same time for a specific pair of participants
  group_by(from, to, date_posix, ward_id, wardType, newID) %>%
  summarise(length = max(length), .groups = "drop") %>%
  # Remove duplicates 
  distinct() %>%
  # Fusion overlapping contacts
  nest(.by = c(from, to, ward_id, wardType, newID)) %>%
  mutate(data = map(data, fusion_overlapping_contacts)) %>%
  unnest(data) %>%
  distinct() %>%
  # Remove interactions when individuals do not wear sensors 
  mutate(n = 1:n()) %>%
  nest(.by = n) %>%
  mutate(data = map(data, outside_schedule, sensor_nodscov2)) %>%
  unnest(data) %>%
  filter(in_schedule == T) %>%
  # Reorder columns 
  select(from, to, date_posix, length, ward_id, wardType, newID)

# Dataframe to compare the 1st and last date of every individual across the 
# interaction data, admission data and sensor data
interaction_first_last = interaction_nodscov2 %>%
  mutate(date_day = as.Date(floor_date(date_posix, "day")),
         date_day_end = as.Date(floor_date(date_posix+length, "day"))) %>%
  pivot_longer(cols = c(from, to), values_to = "id") %>%
  group_by(id) %>%
  summarise(firstDate_interaction = min(date_day), lastDate_interaction = max(date_day_end))

# Compare first date and last date in the admission data, sensor distribution data 
# and interaction data
admission_nodscov2 %>%
  left_join(., sensor_nodscov2 %>% select(id, firstDate_sensor, lastDate_sensor) %>% group_by(id) %>% summarise(firstDate_sensor = min(firstDate_sensor), lastDate_sensor = max(lastDate_sensor), .groups = "drop"), by = "id") %>%
  left_join(., interaction_first_last, by = "id") %>%
  mutate(firstDate_sensor = as.Date(firstDate_sensor)) %>%
  filter(firstDate_sensor > firstDate_interaction) %>%
  select(id, firstDate, firstDate_sensor, firstDate_interaction)

admission_nodscov2 %>%
  left_join(., sensor_nodscov2 %>% select(id, firstDate_sensor, lastDate_sensor) %>% group_by(id) %>% summarise(firstDate_sensor = min(firstDate_sensor), lastDate_sensor = max(lastDate_sensor), .groups = "drop"), by = "id") %>%
  left_join(., interaction_first_last, by = "id") %>%
  mutate(lastDate_sensor = as.Date(lastDate_sensor)) %>%
  filter(lastDate_sensor < lastDate_interaction) %>%
  select(id, lastDate, lastDate_sensor, lastDate_interaction)

# Use sensor distribution data for the first and last date in admission
admission_nodscov2 = admission_nodscov2 %>%
  select(-c(firstDate, lastDate)) %>%
  inner_join(., sensor_nodscov2 %>% 
               select(id, firstDate_sensor, lastDate_sensor) %>%
               group_by(id) %>%
               summarise(firstDate_sensor = as_date(floor_date(min(firstDate_sensor), "day")), 
                         lastDate_sensor = as_date(floor_date(max(lastDate_sensor), "day")), 
                         .groups = "drop"), 
             by = "id") %>%
  rename(firstDate = firstDate_sensor, lastDate = lastDate_sensor) %>%
  select(id, status, firstDate, lastDate, ward, sex, hospitalization, cat)

# Verify that we have the same participants in all three databases
identical(sort(unique(admission_nodscov2$id)), sort(unique(sensor_nodscov2$id)))
all(c(interaction_nodscov2$from, interaction_nodscov2$to) %in% admission_nodscov2$id)

# Agenda of healthcare workers
agenda_nodscov2 = sensor_nodscov2 %>%
  rename(firstDate = firstDate_sensor, lastDate = lastDate_sensor) %>%
  filter(status != "PA")

# Number of participants by category retained from the real data
admission_nodscov2 %>%
  group_by(status, cat) %>%
  summarise(n = n(), .groups = "drop")

# Individuals with no interaction when wearing the sensor 
admission_nodscov2 %>% 
  filter(!id %in% c(interaction_nodscov2$from, interaction_nodscov2$to)) %>%
  group_by(status, cat) %>%
  summarise(n = n(), .groups = "drop")

```


### Save cleaned and selected real data 
```{r}
if (!dir.exists(file.path(nodscov2_path, "clean"))) dir.create(file.path(nodscov2_path, "clean"))

# Admission data 
write.csv2(admission_nodscov2, file.path(nodscov2_path, "clean", "admission_cleaned.csv"), row.names = F, quote = F)

# HCW schedule
write.csv2(agenda_nodscov2, file.path(nodscov2_path, "clean", "agenda_cleaned.csv"), row.names = F, quote = F)

# Interaction data
write.csv2(interaction_nodscov2, file.path(nodscov2_path, "clean", "interaction_cleaned.csv"), row.names = F, quote = F)
```


### Frequency of contacts of more than one hour
```{r file for synthetic data algo}
# Frequency of contacts that last more than 1hour
interaction_nodscov2 %>%
  summarise(
    n = n(), 
    n_more_1h = sum(length/3600 >= 1),
    percentage = sum(length/3600 >= 1) / n() * 100
    )

# Distribution of contact duration for contacts lasting more than 1h
interaction_nodscov2 %>%
  filter(length >= 3600) %>%
  mutate(length = length/3600) %>%
  select(length) %>%
  summary()
```

### Contact recurrence probability per hour
```{r contact recurrence by hour}
# Hourly individual probability of recurring contacts and mean individual
# probability
pind = rep(NA, nrow(admission_nodscov2))
for (i in seq_along(admission_nodscov2$id)) {
  ii = admission_nodscov2$id[i]
  
  # Get n hours spent in the ward with a sensor 
  all_h = sensor_nodscov2 %>%
    filter(id == ii) %>%
    mutate(DATEREMISE = floor_date(firstDate_sensor, "hour"), DATEREC = floor_date(lastDate_sensor, "hour"), k = 1:n()) %>%
    arrange(DATEREMISE) %>%
    group_by(k) %>%
    nest() %>%
    mutate(out = map(data, unroll_dates)) %>%
    unnest(out) %>%
    .$date_list
    
  if (length(all_h) > 1) {
    interaction_h = vector("list", length(all_h))
    proba_h = rep(NA, length(all_h)-1)
    
    # Get lists of contacts per hour
    for (h in seq_along(all_h)) {
      hh = all_h[h]
      contacts = interaction_nodscov2 %>%
        filter(from == ii | to == ii, date_posix >= hh, date_posix < hh+3600) %>%
        select(from, to) %>%
        unlist()
      contacts = unique(contacts[contacts != ii])
      names(contacts) = NULL
      interaction_h[[h]] = contacts 
    }
    
    # Get hourly probability of recurring contacts
    if (length(all_h)>1) {
      for (h in 2:length(all_h)) {
        if (length(interaction_h[[h]]) > 0) {
          proba_h[h-1] = sum(interaction_h[[h]] %in% unlist(interaction_h[1:(h-1)])) / length(interaction_h[[h]])
        } else {
          proba_h[h-1] = 0
        }
      }
    }
    
    # Mean individual hourly probability of recurring contacts
    pind[i] = sum(proba_h) / length(proba_h)
    
  } else {
    pind[i] = 0
  }

}

# Plot mean individual probability of recurring contacts
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  ggplot(., aes(x = cat, y = pind)) +
  geom_boxplot() +
  geom_jitter() +
  theme_bw() +
  labs(x = "", y = "Probability of hourly recurring contact")

# Mean probability of recurring contacts by individual category
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  group_by(cat) %>%
  summarise(m = mean(pind), .groups = "drop")

# Comparison by category of individual
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  rstatix::wilcox_test(pind ~ cat, ref.group = "Paramedical")

# Mean probability when aggregating paramedical and medical staff
admission_nodscov2 %>%
  mutate(pind = pind, cat = ifelse(cat == "Patient", cat, "HCW")) %>%
  group_by(cat) %>%
  summarise(m = mean(pind), .groups = "drop")
```

### Contact recurrence probability per day
```{r contact recurrence by hour}
# Daily individual probability of recurring contacts and mean individual
# probability
pind = rep(NA, nrow(admission_nodscov2))
for (i in seq_along(admission_nodscov2$id)) {
  ii = admission_nodscov2$id[i]
  
  # Get n days spent in the ward with a sensor 
  all_d = sensor_nodscov2 %>%
    filter(id == ii) %>%
    mutate(DATEREMISE = floor_date(firstDate_sensor, "day"), DATEREC = floor_date(lastDate_sensor, "day"), k = 1:n()) %>%
    arrange(DATEREMISE) %>%
    group_by(k) %>%
    nest() %>%
    mutate(out = map(data, unroll_dates)) %>%
    unnest(out) %>%
    .$date_list
    
  if (length(all_d) > 1) {
    interaction_d = vector("list", length(all_d))
    proba_d = rep(NA, length(all_d)-1)
    
    # Get lists of contacts per hour
    for (d in seq_along(all_d)) {
      dd = all_d[d]
      contacts = interaction_nodscov2 %>%
        filter(from == ii | to == ii, date_posix >= dd, date_posix < dd+3600*24) %>%
        select(from, to) %>%
        unlist()
      contacts = unique(contacts[contacts != ii])
      names(contacts) = NULL
      interaction_d[[d]] = contacts 
    }
    
    # Get hourly probability of recurring contacts
    if (length(all_d)>1) {
      for (h in 2:length(all_d)) {
        if (length(interaction_d[[d]]) > 0) {
          proba_d[d-1] = sum(interaction_d[[d]] %in% unlist(interaction_d[1:(d-1)])) / length(interaction_d[[d]])
        } else {
          proba_d[d-1] = 0
        }
      }
    }
    
    # Mean individual hourly probability of recurring contacts
    pind[i] = sum(proba_d) / length(proba_d)
    
  } else {
    pind[i] = 0
  }

}

# Plot mean individual probability of recurring contacts
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  filter(!is.na(pind)) %>%
  ggplot(., aes(x = cat, y = pind)) +
  geom_boxplot() +
  geom_jitter() +
  theme_bw() +
  labs(x = "", y = "Probability of daily recurring contact")

# Mean probability of recurring contacts by individual category
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  group_by(cat) %>%
  summarise(m = mean(pind, na.rm = T), .groups = "drop")

# Comparison by category of individual
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  filter(!is.na(pind)) %>%
  rstatix::wilcox_test(pind ~ cat, ref.group = "Paramedical")

# Mean probability when aggregating paramedical and medical staff
admission_nodscov2 %>%
  mutate(pind = pind, cat = ifelse(cat == "Patient", cat, "HCW")) %>%
  group_by(cat) %>%
  summarise(m = mean(pind, na.rm = T), .groups = "drop")
```

### Patient augmentation
```{r patient augmentation}
# Double rooms - Cumulative time
patients_ids = unique(admission_nodscov2$id[admission_nodscov2$status == "PA"])
interaction_nodscov2 %>% 
  filter(from %in% patients_ids, to %in% patients_ids) %>%
  mutate(pair = paste0(from, "_", to)) %>%
  group_by(pair) %>%
  summarise(length = sum(length)/3600, .groups = "drop")

# List of ids in double rooms
double_rooms = interaction_nodscov2 %>%
  filter(from %in% patients_ids, to %in% patients_ids) %>%
  distinct(from, to)
double_rooms = as.list(as.data.frame(t(double_rooms)))
save(double_rooms, file = file.path(nodscov2_path, "clean", "double_rooms.rda"))

# Patient rooms
patient_rooms = data.frame(
  id = admission_nodscov2$id[admission_nodscov2$status == "PA"],
  room = 1:sum(admission_nodscov2$status == "PA")
)
patient_rooms$room[patient_rooms$id %in% double_rooms[[1]]] = min(patient_rooms$room[patient_rooms$id %in% double_rooms[[1]]])
patient_rooms$room[patient_rooms$id %in% double_rooms[[2]]] = min(patient_rooms$room[patient_rooms$id %in% double_rooms[[2]]])

# Patient augmentation
set.seed(20240924)
for (id in patients_ids) {
  
  # Stay length of original individual
  if (as_date(floor_date(admission_nodscov2$lastDate[admission_nodscov2$id == id], "day")) == as_date("2020-05-07")) {
    stay_length = sample(6:13, 1)
    new_lastDate = as_date("2020-05-06") + stay_length
    admission_nodscov2$lastDate[admission_nodscov2$id == id] = new_lastDate
  } else {
    new_lastDate = as_date("2020-05-06")
  }
  
  # Augment patients by keeping incrementing the original id
  i = 1
  new_room = data.frame()
  while(new_lastDate < as_date(floor_date(noon_last_day, "day"))) {
    stay_length = sample(6:13, 1)
    to_rbind = data.frame(
      id = paste0(id, "-", i),
      status = "PA",
      firstDate = new_lastDate+1,
      lastDate = min(new_lastDate+1+stay_length, as_date(floor_date(noon_last_day, "day"))),
      ward = "Reanimation",
      sex = NA,
      hospitalization = "patient",
      cat = "Patient"
    )  
    
    patient_rooms = rbind(
      patient_rooms, 
      data.frame(
        id = paste0(id, "-", i),
        room = patient_rooms$room[patient_rooms$id == id]
      )
    )
    
    admission_nodscov2 = rbind(admission_nodscov2, to_rbind)
    new_lastDate = min(new_lastDate+1+stay_length, as_date(floor_date(noon_last_day, "day")))
    i = i+1
  }
}

# Final set of individuals in the database
admission_nodscov2 %>%
  group_by(status, cat) %>%
  summarise(n = n(), .groups = "drop") 

```

### Repeat schedule of HCWs over the 90-day period
```{r repeat schedule}
# Repeat schedule over 90 days for individuals present only one day out 
# of the two days of recording
new_agenda = agenda_nodscov2
for (d in 1:44) {
  new_agenda = rbind(
    new_agenda, 
    agenda_nodscov2 %>% 
      mutate(firstDate = firstDate+3600*48*d, lastDate = lastDate+3600*48*d))
}

# Get new admission dates for HCWs
new_admission_dates = new_agenda %>%
  group_by(id) %>%
  summarise(firstDate_new = as_date(floor_date(min(firstDate), "day")), 
            lastDate_new = as_date(floor_date(max(lastDate), "day")), .groups = "drop")

# Verify coherence and change admission dates for HCWs
admission_nodscov2 = admission_nodscov2 %>%
  left_join(., new_admission_dates, by = "id") %>%
  mutate(
    firstDate = case_when(status == "PE" ~ firstDate_new, .default = firstDate),
    lastDate = case_when(status == "PE" ~ lastDate_new, .default = lastDate)
  ) %>%
  select(-c(firstDate_new, lastDate_new))

```

### Verify the concordance between contacts and the schedule of healthcare workers
```{r}
# Schedule of healthcare workers 
ids_pe = admission_nodscov2$id[admission_nodscov2$status == "PE"]
interactions_in_schedule = data.frame()

for (i in ids_pe) {
  # Schedule of the HCW
  schedule_id = agenda_nodscov2 %>%
    filter(id == i) %>%
    select(firstDate, lastDate)
  
  # Get all interactions
  if (sum(interaction_nodscov2$to == i | interaction_nodscov2$from == i) > 0) {
    interactions_id = interaction_nodscov2 %>%
      filter(from == i| to == i) %>%
      select(date_posix, length) %>%
      mutate(n = 1:n())
  
    # Are all interactions within the schedule ?
    out_vec = expand.grid.df(
      schedule_id, 
      interactions_id
    ) %>%
      group_by(n) %>%
      summarise(out = any(date_posix >= firstDate & date_posix+length <= lastDate), .groups = "drop") %>%
      pull(out)
    
    interactions_in_schedule = bind_rows(
      interactions_in_schedule, 
      data.frame(
        id = i, 
        coherent_interactions = all(out_vec)
      )
    )
  
  } else {
    interactions_in_schedule = bind_rows(
      interactions_in_schedule, 
      data.frame(
        id = i, 
        coherent_interactions = NA
      )
    )
  }
}

# Number of HCW
admission_nodscov2 %>% filter(status == "PE") %>% nrow()

# Individuals with all interactions within schedule
sum(interactions_in_schedule$coherent_interactions, na.rm = T)

# Individuals with missing interactions
sum(is.na(interactions_in_schedule$coherent_interactions))
```


### Save data for synthetic algorithm
```{r save synthetic}
# Interaction data
write.csv2(interaction_nodscov2, file.path(synthetic_path, "input", "interactions.csv"), quote = F, row.names = F)

# Admission data
write.csv2(admission_nodscov2, file.path(synthetic_path, "input", "admission.csv"), quote = F, row.names = F)

# HCW schedule
write.csv2(new_agenda, file.path(synthetic_path, "input", "agenda.csv"),  quote = F, row.names = F)

# Patient rooms
write.csv2(patient_rooms, file.path(synthetic_path, "loc", "patient_rooms.csv"), quote = F, row.names = F)
```

## Plot raw data for supplementary materials
### Participant description
```{r plots after filtration}
# Create directory to store figures
if (!dir.exists(file.path(fig_path, "nodscov2-data"))) dir.create(file.path(fig_path, "nodscov2-data"))

# Number of individuals by category
p1 = admission_nodscov2 %>% 
  group_by(cat) %>% 
  summarise(n =n()) %>% 
  ggplot(., aes(x = cat, y = n, fill = cat)) + 
  geom_bar(stat = "identity", width = 0.5) + 
  scale_fill_manual(values = pal) +
  theme_bw() + 
  theme(legend.position = "none", axis.text.x = element_text(angle = 30, hjust = 1)) +
  labs(x = "", y = "Number of individuals")
  
# Number of interactions
p2 = interaction_nodscov2 %>%
  left_join(., admission_nodscov2 %>% select(id, cat) %>% rename(cat_from = cat), by = c("from" = "id")) %>%
  left_join(., admission_nodscov2 %>% select(id, cat) %>% rename(cat_to = cat), by = c("to" = "id")) %>%
  mutate(cat_pair = case_when(
    cat_from == "Patient" & cat_to == "Patient" ~ "Patient-Patient",
    (cat_from == "Patient" & cat_to != "Patient") | (cat_from != "Patient" & cat_to == "Patient") ~ "Patient-HCW",
    cat_from != "Patient" & cat_to != "Patient" ~ "HCW-HCW"
    ),
    id_pair = 1:n()) %>%
  filter(cat_pair != "Patient-Patient") %>%
  group_by(id_pair, from, to, cat_pair, date_posix) %>%
  nest() %>%
  mutate(out = map2(data, date_posix, function(.x, .y) data.frame(interacting = seq.POSIXt(.y, .y+.x$length, 10)))) %>%
  ungroup() %>%
  select(-data) %>%
  unnest(cols = out) %>%
  group_by(cat_pair, interacting) %>%
  summarise(n =n(), .groups = "drop") %>%
  ggplot(., aes(x= interacting, y = n, col = cat_pair)) +
  geom_line() +
  theme_bw() +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("Patient-HCW" = "orange", "HCW-HCW" = "orchid")) +
  labs(x = "Time", y="Number of interactions", col = "Type of interaction")
ggsave(file.path(fig_path, "nodscov2-data", "interactions.png"), p2, height = 4, width = 10)

# Combined plot
p = ggarrange(p1, p2, ncol = 2, align = "hv", widths = c(1,4), labels = c("A", "B"))
ggsave(file.path(fig_path, "nodscov2-data", "interactions_combined.png"), p, height = 4, width = 10)
```

### Plot interaction network
```{r}
# Create network objects
graph_data = interaction_nodscov2 %>%
  mutate(date_posix = floor_date(date_posix, "day")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length), .groups = "drop") %>%
  arrange(date_posix)

graph_data_PA_PA = graph_data %>%
  filter(grepl("PA-", from) & grepl("PA-", to))

graph_data_PE_PE = graph_data %>%
  filter(grepl("PE-", from) & grepl("PE-", to))

graph_data_PA_PE = graph_data %>%
  filter((grepl("PE-", from) & grepl("PA-", to)) | (grepl("PA-", from) & grepl("PE-", to)))

# Get all metrics 
all_metrics = get_net_metrics(graph_data, adm_data = admission_nodscov2, network = "Full")
PA_PA_metrics = get_net_metrics(graph_data_PA_PA, adm_data = admission_nodscov2, network = "PA-PA")
PE_PE_metrics = get_net_metrics(graph_data_PE_PE, adm_data = admission_nodscov2, network = "PE-PE")
PA_PE_metrics = get_net_metrics(graph_data_PA_PE, adm_data = admission_nodscov2, network = "PA-PE")

# Summary statistics of full grpah and subgraphs
cols = colnames(all_metrics)[1:7]
summary_tab = rbind(all_metrics, PA_PA_metrics, PE_PE_metrics, PA_PE_metrics) %>%
  mutate(temp_corr = replace(temp_corr, temp_corr==0, NA)) %>%
  group_by(network) %>%
  summarise(across(all_of(cols), list(mean=mean, sd=sd), na.rm=T))

summary_tab[,-1] = round(summary_tab[,-1], 2)
View(summary_tab)

# Get all degrees
all_degrees = c()
for(d in unique(graph_data$date_posix)){
  data_d = graph_data %>%
    filter(date_posix == d)
  
  graph_d = graph_from_data_frame(data_d, directed = F)
  graph_d = simplify(graph_d)
  all_degrees = c(all_degrees, degree(graph_d))
}

# Distribution of daily number of degrees (dashed red line = mean degree)
# CV: coefficient of variation (standard deviation/mean)
pe = ggplot() +
  geom_histogram(aes(all_degrees, after_stat(density)), binwidth = 1, colour = "grey") +
  geom_vline(xintercept = mean(all_degrees), linetype = "dashed", linewidth = 1, colour = "red3") +
  geom_richtext(aes(x = 35, y = 0.05,
                    label = paste0("CV<sup>2</sup> = ",
                                   round((sd(all_degrees)/mean(all_degrees))^2, 3))),
                colour = "red3", size = 6) +
  theme_bw() +
  labs(x = "Node degree", y = "Frequency") +
  theme(axis.text = element_text(size = 12),
        axis.title = element_text(size = 12)) +
  scale_x_continuous(breaks = seq(0,40,10))


# Full graph
example_date = as_datetime("2020-05-06 00:00:00")
example_data = graph_data %>%
  filter(date_posix == example_date)
graph_example = graph_from_data_frame(example_data, directed = F)
graph_example = simplify(graph_example)

vertex_atts = data.frame(id = vertex_attr(graph_example, "name")) %>%
  left_join(admission_nodscov2, "id")

graph_example = graph_example %>%
  set_vertex_attr("cat", value = vertex_atts$cat)

pa = ggplot(ggnetwork(graph_example, layout = igraph::layout_with_kk(graph_example)),
            aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges(alpha = 0.5) +
  geom_nodes(aes(colour = cat), size = 4) +
  theme_blank() +
  scale_colour_discrete(type = pal) +
  labs(colour = "Category:") +
  theme(legend.text = element_text(size=12))

# PA-PA subgraph
graph_example_PA_PA = graph_from_data_frame(graph_data_PA_PA %>% filter(date_posix == example_date),
                                            directed = F)
graph_example_PA_PA = simplify(graph_example_PA_PA)

vertex_atts = data.frame(id = vertex_attr(graph_example_PA_PA, "name")) %>%
  left_join(admission_nodscov2, "id")

graph_example_PA_PA = graph_example_PA_PA %>%
  set_vertex_attr("cat", value = vertex_atts$cat) 

pb = ggplot(ggnetwork(graph_example_PA_PA, layout = igraph::layout_with_kk(graph_example_PA_PA)),
            aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges(alpha = 0.5) +
  geom_nodes(aes(colour = cat), size = 3) +
  theme_blank() +
  scale_colour_discrete(type = pal["Patient"]) +
  labs(colour = "Category:") +
  theme(legend.text = element_text(size=12)) +
  guides(colour = "none")

# PE-PE subgraph
graph_example_PE_PE = graph_from_data_frame(graph_data_PE_PE %>% filter(date_posix == example_date),
                                            directed = F)
graph_example_PE_PE = simplify(graph_example_PE_PE)

vertex_atts = data.frame(id = vertex_attr(graph_example_PE_PE, "name")) %>%
  left_join(admission_nodscov2, "id") 

graph_example_PE_PE = graph_example_PE_PE %>%
  set_vertex_attr("cat", value = vertex_atts$cat) 

pc = ggplot(ggnetwork(graph_example_PE_PE, layout = igraph::layout_with_kk(graph_example_PE_PE)),
            aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges(alpha = 0.5) +
  geom_nodes(aes(colour = cat), size = 3) +
  theme_blank() +
  scale_colour_discrete(type = pal[c("Medical", "Paramedical")]) +
  labs(colour = "Category:") +
  theme(legend.text = element_text(size=12)) +
  guides(colour = "none")

# PA-PE subgraph
graph_example_PA_PE = graph_from_data_frame(graph_data_PA_PE %>% filter(date_posix == example_date),
                                            directed = F)
graph_example_PA_PE = simplify(graph_example_PA_PE)

vertex_atts = data.frame(id = vertex_attr(graph_example_PA_PE, "name")) %>%
  left_join(admission_nodscov2, "id")

graph_example_PA_PE = graph_example_PA_PE %>%
  set_vertex_attr("cat", value = vertex_atts$cat)

pd = ggplot(ggnetwork(graph_example_PA_PE, layout = igraph::layout_with_kk(graph_example_PA_PE)),
            aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_edges(alpha = 0.5) +
  geom_nodes(aes(colour = cat), size = 3) +
  theme_blank() +
  scale_colour_discrete(type = pal) +
  labs(colour = "Category:") +
  theme(legend.text = element_text(size=12)) +
  guides(colour = "none")

# Final plot
p = ggarrange(pa,
              ggarrange(pb,pc,pd, nrow=1, labels = c("B", "C", "D")),
              pe, 
              heights = c(1,0.7,0.5), 
              ncol = 1, 
              labels = c("A", "", "E"))

ggsave(file.path(fig_path, "nodscov2-data", "network_subnetworks.png"), p, height = 12, width = 10)

```

