---
title: "Compare synthetic and real contact data"
author: "Olivier GAUFRÈS"
date: "2024-10-08"
output: html_document
---

## Libraries
```{r setup, include=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(igraph)
library(ggnetwork)
library(ggtext)
library(cowplot)
rm(list = ls())

# Helper functions
source("helper-functions.R")

# Working directories and paths
synthetic_path = file.path("..", "..", "data", "data-synthetic-graphs")
```

## Load real and synthetic contact data
```{r data loading, echo = FALSE}
# List of individuals 
admission = read.csv2(file.path(synthetic_path, "admission_no_dup.csv")) %>%
  mutate(
    firstDate = as.Date(firstDate),
    lastDate = as.Date(lastDate)
  )

# Schedule of healthcare workers
schedule_real = read.csv2(file.path(synthetic_path, "agenda_no_dup.csv")) %>%
  mutate(
    firstDate = as_datetime(firstDate),
    lastDate = as_datetime(lastDate)
  )

# Real interaction data
interaction_real = read.csv2(file.path(synthetic_path, "interactions_no_dup.csv")) %>%
  mutate(date_posix_first = as_datetime(date_posix_first))

# Synthetic data
interaction_synthetic = data.frame()
for (f in list.files(file.path(synthetic_path, "full_0-5"), pattern = "matContact", full.names = T)) {
  interaction_synthetic = bind_rows(
    interaction_synthetic,
    read.csv2(f) %>% 
      mutate(
        nSim = gsub("^.*Networks|_oneday.*$", "", f),
        firstDate = as_datetime(date_posix),
        lastDate = as_datetime(date_posix) + length
        )
  )
}
```

```{r}
data_real = interaction_real %>%
  rename(date_posix = date_posix_first)
ids_real = sort(unique(c(data_real$from, data_real$to)))

data_syn = read.csv2(file.path(synthetic_path, "matContactBuiltSimulatedCtcNetworks1_oneday.csv")) %>%
  mutate(date_posix = floor_date(as_datetime(date_posix), "hour"))
ids_syn = sort(unique(c(data_syn$from, data_syn$to)))

all(ids_syn %in% ids_real)
sort(ids_syn[!ids_syn %in% ids_real & !grepl("-[0-9]$", ids_syn)])
sort(admission$id[!admission$id %in% ids_real & !grepl("-[0-9]+$", admission$id)])
```

## Verify whether individuals in the synthetic network have at least one interaction per hour 
```{r at least one interaction per hour}
# Do all individuals have at least one contact per hour in the synthetic data?
at_least_one_contact = data.frame()
all_contacts = data.frame()

for (i in admission$id) {
  
  # Admission date    
  admissionDate = admission$firstDate[admission$id == i]
  proceed = F
  
  if (admission$status[admission$id == i] == "PE") {
    # Vector of hours of presence in the ward
    proceed = T
    # lastHour = as_datetime("2020-08-03 23:00:00")
    hoursOfPresence = schedule_real %>%
      filter(id == i) %>%
      select(firstDate, lastDate) %>%
      mutate(r = 1:n()) %>%
      group_by(r) %>%
      nest() %>%
      mutate(seqHours = map(data, unroll_dates)) %>%
      unnest(seqHours) %>%
      ungroup() %>%
      distinct(seqHours) %>%
      pull(seqHours)
  } 
  
  if (admission$status[admission$id == i] == "PA") {
    proceed = T
    # Patient discharge date
    dischargeDate = admission$lastDate[admission$id == i]

    # Hours of presence in the ward
    firstHour = as_datetime(paste0(admissionDate, "08:00:00"))
    lastHour = as_datetime(paste0(dischargeDate, "20:00:00"))
    hoursOfPresence = seq(firstHour, lastHour, 3600)
  }
  
  if (proceed) {
    # Hours with contacts in the ward 
    all_contacts_temp = interaction_synthetic %>%
      filter(from == i | to == i) %>%
      mutate(date_posix = floor_date(as_datetime(date_posix), "hour")) %>%
      group_by(date_posix, nSim) %>%
      summarise(n = n(), .groups = "drop")
    
    hoursInteracting = all_contacts_temp %>%
      group_by(nSim) %>%
      summarise(atLeastOne = all(hoursOfPresence %in% date_posix), .groups = "drop") %>% 
      mutate(id = i)
    
    all_contacts = bind_rows(all_contacts,
                             expand.grid(nSim = as.character(1:10), date_posix = hoursOfPresence, id = i) %>%
                               left_join(., all_contacts_temp %>% select(date_posix, nSim) %>% mutate(contact = 1), by = c("nSim", "date_posix")) %>%
                               mutate(contact = ifelse(is.na(contact), 0, contact), moment = ifelse(hour(date_posix) < 12, "morning", "afternoon")) %>%
                               group_by(id, nSim, moment) %>%
                               summarise(contact = sum(contact==0), n_tot = n(), .groups = "drop")
                               )
    
    at_least_one_contact = bind_rows(
      at_least_one_contact,
      hoursInteracting
    ) 
  }
}

# Check 
at_least_one_contact %>%
  mutate(status = gsub("-.*$", "", id)) %>%
  count(status, atLeastOne)

# Individuals without interactions
inds = at_least_one_contact %>%
  group_by(id) %>%
  summarise(n=sum(atLeastOne), .groups = "drop") %>%
  filter(n == 10) %>%
  pull(id)
schedule_real %>% filter(id %in% inds)

inds_to_test = schedule_real %>% 
  filter(lastDate <= as_datetime("2020-05-07 12:00:00")) %>% 
  group_by(id) %>% 
  nest() %>% 
  mutate(firstDayInteraction = map(data, testFun)) %>% 
  select(-data) %>% 
  unnest(firstDayInteraction) %>% 
  filter(firstDayInteraction == F)
  
# Individuals with at least one contact 
ids = at_least_one_contact %>%
  filter(atLeastOne == T) %>%
  distinct(id) %>%
  pull(id)
admission %>% filter(id %in% ids)
schedule_real %>% filter(id %in% ids) %>% filter(lastDate <= "2020-05-09 00:00:00") %>% arrange(id, firstDate)
interaction_real %>% filter(from %in% ids | to %in% ids, date_posix_first <= as_datetime("2020-05-07 12:00:00")) %>%  
  mutate(lastDate = date_posix_first + length) 

# Individuals that are present only during the first afternoon 
testFun = function(df) {
  presentOnlyFirstDay = all(df$firstDate <= as_datetime("2020-05-07 00:00:00") & df$lastDate <= as_datetime("2020-05-07 00:00:00"))
  return(presentOnlyFirstDay)
}

presentFirstDayOnly = schedule_real %>% 
  filter(lastDate <= as_datetime('2020-05-07 12:00:00')) %>%
  group_by(id) %>%
  nest() %>%
  mutate(out = map(data, testFun)) %>% 
  select(-data) %>% 
  unnest(out) %>% 
  ungroup() 
count(presentFirstDayOnly, out)

presentFirstDayOnly$id[presentFirstDayOnly$out==T]

# Missing contacts
all_contacts %>% 
  ggplot(., aes(x = nSim, y = contact/n_tot, col = moment)) +
  geom_point(position = position_dodge(width = 0.5)) +
  theme_bw() +
  labs(x = "Simulation", y = "Proportion of hours with contact", col = "")

```

## Verification of the coherence between schedule and admission databases for healthcare workers
```{r}
# Schedule of healthcare workers 
ids_pe = admission$id[admission$status == "PE"]
interactions_in_schedule = data.frame()

for (i in ids_pe) {
  # Schedule of the HCW
  schedule_id = schedule_real %>%
    filter(id == i, lastDate <= as_datetime("2020-05-07 12:00:00")) %>%
    select(firstDate, lastDate)
  
  # Get all interactions
  if (sum(interaction_real$to == i | interaction_real$from == i) > 0) {
    interactions_id = interaction_real %>%
      filter(from == i| to == i) %>%
      select(date_posix_first, length) %>%
      mutate(n = 1:n())
  
    # Are all interactions within the schedule ?
    out_vec = expand.grid.df(
      schedule_id, 
      interactions_id
    ) %>%
      group_by(n) %>%
      summarise(out = any(date_posix_first >= firstDate & date_posix_first+length <= lastDate), .groups = "drop") %>%
      pull(out)
    
    interactions_in_schedule = bind_rows(
      interactions_in_schedule, 
      data.frame(
        id = i, 
        coherent_interactions = all(out_vec)
      )
    )
  
  } else {
    interactions_in_schedule = bind_rows(
      interactions_in_schedule, 
      data.frame(
        id = i, 
        coherent_interactions = NA
      )
    )
  }
}

summary(interactions_in_schedule)
```


## Compare network characteristics

Analyses are based on Quentin's codes available [here](https://gitlab.pasteur.fr/qleclerc/network_algorithm/-/tree/main/analysis?ref_type=heads).

### Number of unique contacts and contact duration 
```{r}
# Prepare observed data 
data = interaction_real %>%
  select(from, to, date_posix_first, length) %>%
  rename(date_posix = date_posix_first)

dur_observed = data %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length)/60, .groups = "drop") %>% # Convert in minutes
  pull(length)

distrib_PAPA = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-patient")

distrib_PEPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PE-PE") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Staff-staff")

distrib_PAPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PE" | type == "PE-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-staff")

distrib_real = rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
  mutate(date_posix = paste0(date_posix, ":00")) %>%
  mutate(date_posix = factor(date_posix, levels = unique(date_posix))) %>%
  mutate(network = "Observed")

# Prepare reconstructed data 
data = read.csv2(file.path(synthetic_path, "matContactBuiltSimulatedCtcNetworks2_oneday.csv"))

dur_simu = data %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length)/60, .groups = "drop") %>%
  pull(length)

distrib_PAPA = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PA") %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-patient")

distrib_PEPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PE-PE") %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Staff-staff")

distrib_PAPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PE" | type == "PE-PA") %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-staff")

distrib_simu = rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
  mutate(date_posix = paste0(date_posix, ":00")) %>%
  mutate(date_posix = factor(date_posix, levels = unique(date_posix))) %>%
  mutate(network = "Reconstructed")


# Combine datasets 
distrib_all = rbind(distrib_real, distrib_simu) %>%
  mutate(network = factor(network, levels = unique(network))) %>%
  mutate(type = factor(type, levels = unique(type))) %>%
  mutate(date_posix = factor(date_posix, levels = c("0:00","1:00","2:00","3:00","4:00",
                                                    "5:00","6:00","7:00","8:00","9:00",
                                                    "10:00","11:00","12:00","13:00","14:00",
                                                    "15:00","16:00","17:00","18:00","19:00",
                                                    "20:00","21:00","22:00","23:00")))
  
# Compare number of unique contacts
pa = ggplot(distrib_all) +
  geom_ribbon(aes(date_posix, ymin = q25, ymax = q75, fill = network, group = interaction(type, network, day)),
              alpha = 0.3) +
  geom_point(aes(date_posix, med, colour = network)) +
  geom_line(aes(date_posix, med, colour = network, group = interaction(type, network, day))) +
  scale_colour_discrete(type = pal) +
  scale_fill_discrete(type = pal) +
  scale_y_continuous(breaks = seq(0,300,75)) +
  scale_x_discrete(breaks = c("0:00", "4:00", "8:00", "12:00",
                              "16:00","20:00")) +
  facet_grid(cols = vars(type), rows = vars(day)) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14),
        strip.text = element_text(size = 14))  +
  labs(x = "Hour", y = "Number of unique contacts", colour = "Network:", fill = "Network:")

# Compare contact duration 
pb = ggplot() +
  geom_boxplot(aes(y=dur_observed, x = "1", colour = "Observed"), outlier.shape = NA) +
  geom_boxplot(aes(y=dur_simu, x = "3", colour = "Reconstructed"), outlier.shape = NA) +
  scale_color_manual(values = pal) +
  scale_x_discrete(labels = c("Observed", "Reconstructed")) +
  coord_cartesian(ylim = c(0,35)) +
  guides(colour="none") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14)) +
  labs(y = "Contact duration (minutes)", x = "Network")

# Combine plots
plot_grid(pa, pb, nrow = 2, labels = c("a)", "b)"), rel_heights = c(1,0.8), hjust=0, vjust=c(1,0))
```


```{r}
# Prepare observed data 
data = interaction_real %>%
  select(from, to, date_posix_first, length) %>%
  rename(date_posix = date_posix_first)

dur_observed = data %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length)/60, .groups = "drop") %>% # Convert in minutes
  select(length) %>%
  mutate(network = "Observed")

distrib_PAPA = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-patient")

distrib_PEPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PE-PE") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Staff-staff")

distrib_PAPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PE" | type == "PE-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-staff")

distrib_real = rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
  mutate(date_posix = paste0(date_posix, ":00")) %>%
  mutate(date_posix = factor(date_posix, levels = unique(date_posix))) %>%
  mutate(network = "Observed")

# Prepare reconstructed data 
for (prob in c("0-1", "0-5agenda", "0-5", "biased")) {
  dur_sim = data.frame()
  distrib_simu = data.frame()
  
  to_read = ifelse(prob!="biased", paste0("full_", prob), prob)
  
  for (f in list.files(file.path(synthetic_path, to_read), "matContactBuilt", full.names = T)) {
   data = read.csv2(f)
  
    dur_sim = bind_rows(
      dur_sim, 
      data %>%
        mutate(date_posix = floor_date(as_datetime(date_posix), "hour")) %>%
        # filter(date_posix >= as_datetime("2020-05-06"), date_posix <= as_datetime("2020-05-07")) %>%
        group_by(from, to, date_posix) %>%
        summarise(length = sum(length)/60, .groups = "drop") %>%
        mutate(network = paste0("Reconstructed-", gsub("^.*Networks|_oneday.csv$", "", f))) %>%
        select(length, network)
    )
    
    distrib_PAPA = data %>%
      mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
      filter(type == "PA-PA") %>%
      mutate(date_posix = as_datetime(date_posix)) %>%
      # filter(floor_date(date_posix, "day") >= as_datetime("2020-05-06"), floor_date(date_posix, "day") <= as_datetime("2020-05-07")) %>%
      mutate(date_posix = floor_date(date_posix, "hour")) %>%
      select(-length) %>%
      distinct() %>%
      count(date_posix) %>%
      ungroup() %>%
      mutate(day = wday(date_posix, week_start = 1)) %>%
      mutate(day = as.character(day)) %>%
      mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
      mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
      mutate(date_posix = hour(date_posix)) %>%
      group_by(date_posix, day) %>%
      summarise(med = median(n),
                q25 = quantile(n, 0.25),
                q75 = quantile(n, 0.75), .groups = "drop") %>%
      mutate(type = "Patient-patient")
    
    distrib_PEPE = data %>%
      mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
      filter(type == "PE-PE") %>%
      mutate(date_posix = as_datetime(date_posix)) %>%
      # filter(floor_date(date_posix, "day") >= as_datetime("2020-05-06"), floor_date(date_posix, "day") <= as_datetime("2020-05-07")) %>%
      mutate(date_posix = floor_date(date_posix, "hour")) %>%
      select(-length) %>%
      distinct() %>%
      count(date_posix) %>%
      ungroup() %>%
      mutate(day = wday(date_posix, week_start = 1)) %>%
      mutate(day = as.character(day)) %>%
      mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
      mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
      mutate(date_posix = hour(date_posix)) %>%
      group_by(date_posix, day) %>%
      summarise(med = median(n),
                q25 = quantile(n, 0.25),
                q75 = quantile(n, 0.75), .groups = "drop") %>%
      mutate(type = "Staff-staff")
    
    distrib_PAPE = data %>%
      mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
      filter(type == "PA-PE" | type == "PE-PA") %>%
      mutate(date_posix = as_datetime(date_posix)) %>%
      # filter(floor_date(date_posix, "day") >= as_datetime("2020-05-06"), floor_date(date_posix, "day") <= as_datetime("2020-05-07")) %>%
      mutate(date_posix = floor_date(date_posix, "hour")) %>%
      select(-length) %>%
      distinct() %>%
      count(date_posix) %>%
      ungroup() %>%
      mutate(day = wday(date_posix, week_start = 1)) %>%
      mutate(day = as.character(day)) %>%
      mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
      mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
      mutate(date_posix = hour(date_posix)) %>%
      group_by(date_posix, day) %>%
      summarise(med = median(n),
                q25 = quantile(n, 0.25),
                q75 = quantile(n, 0.75), .groups = "drop") %>%
      mutate(type = "Patient-staff")
    
    distrib_simu = bind_rows(
      distrib_simu,
      rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
        mutate(date_posix = paste0(date_posix, ":00")) %>%
        mutate(
          date_posix = factor(date_posix, levels = unique(date_posix)),
          network = paste0("Reconstructed-", gsub(".*Networks|_oneday.*$", "", f))
          ) 
    )
  }
  
  # Combine datasets 
  distrib_all = rbind(distrib_real, distrib_simu) %>%
    mutate(
      type = factor(type, levels = unique(type)),
                    date_posix = factor(date_posix, levels = c("0:00","1:00","2:00","3:00","4:00",
                                                               "5:00","6:00","7:00","8:00","9:00",
                                                               "10:00","11:00","12:00","13:00","14:00",
                                                               "15:00","16:00","17:00","18:00","19:00",
                                                               "20:00","21:00","22:00","23:00"))
      )
    
  # Compare number of unique contacts
  pa = distrib_all %>%
    filter(day != "Weekend") %>%
    ggplot() +
    geom_ribbon(aes(date_posix, ymin = q25, ymax = q75, fill = network, group = interaction(type, network, day)),
                alpha = 0.3) +
    geom_point(aes(date_posix, med, colour = network)) +
    geom_line(aes(date_posix, med, colour = network, group = interaction(type, network, day))) +
    scale_colour_discrete(type = c("orange", colorRampPalette(c("dodgerblue4", "lightskyblue"))(10))) +
    scale_fill_discrete(type = c("orange", colorRampPalette(c("dodgerblue4", "lightskyblue"))(10))) +
    scale_y_continuous(breaks = seq(0,300,75)) +
    scale_x_discrete(breaks = c("0:00", "4:00", "8:00", "12:00",
                                "16:00","20:00")) +
    facet_grid(cols = vars(type), rows = vars(day)) +
    theme_bw() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
          legend.text = element_text(size = 14),
          legend.title = element_text(size = 14),
          axis.text.y = element_text(size = 14),
          axis.title = element_text(size = 14),
          strip.text = element_text(size = 14))  +
    labs(x = "Hour", y = "Number of unique contacts", colour = "Network:", fill = "Network:")
  
  # Compare contact duration 
  pb = bind_rows(dur_observed, dur_sim) %>%
    ggplot(aes(y=length, x = network, colour = network)) +
    geom_boxplot(outlier.shape = NA) +
    scale_color_manual(values = pal) +
    coord_cartesian(ylim = c(0,35)) +
    guides(colour="none") +
    theme_bw() +
    theme(axis.text.x = element_text(size = 14, angle = 30, hjust = 1),
          axis.text.y = element_text(size = 14),
          axis.title = element_text(size = 14)) +
    labs(y = "Contact duration (minutes)", x = "Network") 
  
  # Combine plots
  p = plot_grid(pa, pb, nrow = 2, labels = c("a)", "b)"), rel_heights = c(1,0.8), hjust=0, vjust=c(1,0))
  ggsave(paste0("../../out/fig/unique_contacts_", prob, ".png"), p, height = 8, width = 10)  
}

```

### Network metrics (degree, global efficiency, transitivity, assortativity, temporal correlation, density)
```{r compare networks}
adm_data = admission %>%
  select(id, cat, ward) %>%
  distinct() %>%
  mutate(
    staff = grepl("PE-", id),
    cat_ag = cat
    )

data = interaction_real %>%
  select(from, to, date_posix_first, length) %>%
  rename(date_posix = date_posix_first)

graph_data = data %>%
  mutate(date_posix = floor_date(date_posix, "day")) %>%
  filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
  select(from, to, date_posix) %>%
  distinct() %>%
  arrange(date_posix)

for (prob in c("0-1", "0-5agenda", "0-5", "biased")) {
  
  to_read = ifelse(prob!="biased", paste0("full_", prob), prob)
  simu_files = list.files(path = file.path(synthetic_path, to_read), pattern = "matContact.*", full.names = T)

  ## Reconstructed full #####
  
  iter=1
  
  simu_data = data.frame()
  
  for(f in simu_files){
    
    data = read.csv2(f)
    
    graph_data = data %>%
      mutate(date_posix = floor_date(as_datetime(date_posix), "day")) %>%
      # filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
      select(from, to, date_posix) %>%
      distinct %>%
      arrange(date_posix)
    
    simu_data = rbind(simu_data,
                      get_net_metrics(graph_data, adm_data, iter, "Reconstructed"))
    
    iter=iter+1
  }
  
  ## Observed #####
  graph_data = interaction_real %>%
    rename(date_posix = date_posix_first) %>%
    mutate(date_posix = floor_date(date_posix, "day")) %>%
    filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
    select(from, to, date_posix) %>%
    distinct() %>%
    arrange(date_posix) %>%
    mutate(date_posix = as.Date("2020-05-06"))
  
  observed_data = get_net_metrics(graph_data, adm_data, 1, "Observed")
  
  # GROUPED #####
  
  summary_data = rbind(simu_data, observed_data)
  # for convenience, save the summary here and read it in later
  # write.csv(summary_data, here::here("Data", "summary_data.csv"), row.names = F)
  # summary_data = read.csv(here::here("Data", "summary_data.csv"))
  
  summary_data = summary_data %>%
    mutate(network = factor(network,
                            levels = c("Observed", "Reconstructed")))
  
  summary_data = summary_data %>%
    group_by(day, network) %>%
    summarise(across(everything(), median), .groups = "drop") %>%
    select(-iter)
  
  summary_data %>%
    select(-day) %>%
    group_by(network) %>%
    summarise(across(everything(), \(x) quantile(x, probs=0.75))) %>%
    View
  
  pa = ggplot() +
    geom_boxplot(data=summary_data,
                 aes(x = network, y = degrees, colour = network), linewidth = 0.8) +
    scale_colour_discrete(type = pal) +
    theme_bw() +
    guides(colour = "none") +
    labs(x = "Network", y = "Degree (daily)") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 12))
  
  pb = ggplot() +
    geom_boxplot(data=summary_data,
                 aes(x = network, y = efficiencies, colour = network), linewidth = 0.8) +
    scale_colour_discrete(type = pal) +
    theme_bw() +
    guides(colour = "none") +
    labs(x = "Network", y = "Global efficiency") +
    scale_y_continuous(breaks = seq(0,0.8,0.1)) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 12))
  
  pc = ggplot() +
    geom_boxplot(data=summary_data,
                 aes(x = network, y = transitivities, colour = network), linewidth = 0.8) +
    scale_colour_discrete(type = pal) +
    theme_bw() +
    guides(colour = "none") +
    labs(x = "Network", y = "Transitivity") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_text(size = 12),
          axis.title.y = element_text(size = 12))
  
  pd = ggplot() +
    geom_boxplot(data=summary_data,
                 aes(x = network, y = assortativities, colour = network), linewidth = 0.8) +
    scale_colour_discrete(type = pal) +
    theme_bw() +
    guides(colour = "none") +
    labs(x = "Network", y = "Assortativity (degree)") +
    theme(axis.text.x = element_text(size = 12, angle = 30, hjust = 1),
          axis.title = element_text(size = 12),
          axis.text.y = element_text(size = 12))
  
  p = plot_grid(pa,pb,pc,pd, nrow=2,
                      labels = c("a)", "b)", "c)", "d)"),
            hjust = 0, vjust=1, align = "v", rel_heights = c(0.77, 1))
  ggsave(paste0("../../out/fig/metrics_", prob, ".png"), p, height = 8, width = 8)
  # ggplot() +
  #   geom_boxplot(data=summary_data,
  #                aes(x = network, y = densities, colour = network), linewidth = 0.8) +
  #   scale_colour_discrete(type = pal) +
  #   scale_y_continuous(breaks = seq(0,0.3,0.05)) +
  #   theme_bw() +
  #   guides(colour = "none") +
  #   labs(x = "Network", y = "Density") +
  #   theme(axis.text.x = element_text(size = 12),
  #         axis.title = element_text(size = 12),
  #         axis.text.y = element_text(size = 12)) 
}
```


### Troubleshooting assortativity by degree
```{r compare networks}
adm_data = admission %>%
  select(id, cat, ward) %>%
  distinct() %>%
  mutate(
    staff = grepl("PE-", id),
    cat_ag = cat
    )

## Reconstructed full #####

simu_files = list.files(path = file.path(synthetic_path, "full_0-5agenda"), pattern = "matContact.*", full.names = T)
simu_data = data.frame()

for (time_window in c("day", "week", "month", "full")) {
  iter=1
  for(f in simu_files){
  data = read.csv2(f)
  
  graph_data = data %>%
    mutate(date_posix = floor_date(as_datetime(date_posix), "day")) %>%
    select(from, to, date_posix) %>%
    distinct %>%
    arrange(date_posix)
  
  if (time_window=="day") graph_data = graph_data %>% filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07"))
    if (time_window=="week") graph_data = graph_data %>% filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-13"))
    if (time_window=="month") graph_data = graph_data %>% filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-06-05"))
    if (time_window=="full") graph_data = graph_data %>% filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-08-04"))
    
  simu_data = rbind(simu_data,
                    get_assortativity_degree(graph_data, adm_data, iter, "Reconstructed", time_window))
  
  iter=iter+1
  } 
}

## Observed #####
graph_data = interaction_real %>%
  rename(date_posix = date_posix_first) %>%
  mutate(date_posix = floor_date(date_posix, "day")) %>%
  filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
  select(from, to, date_posix) %>%
  distinct() %>%
  arrange(date_posix) %>%
  mutate(date_posix = as.Date("2020-05-06"))

observed_data = get_assortativity_degree(graph_data, adm_data, 1, "Observed", "day")

## Plot simulated assortativity
simu_data %>%
  group_by(network, iter, time_window) %>%
  summarise(assortativities = median(assortativities), .groups = "drop") %>%
  mutate(time_window = factor(time_window, c("day", "week", "month", "full"))) %>%
  ggplot(., aes(x = time_window, y = assortativities, col = as.factor(iter), group = as.factor(iter))) +
  geom_hline(yintercept = observed_data$assortativities) +
  geom_line() +
  scale_color_manual(values = colorRampPalette(c("darkblue", "lightblue"))(10)) +
  theme_bw() +
  labs(col = "Simulation", y = "Median assortativity degree", x = "Time window")
```


```{r compare networks}
adm_data = admission %>%
  select(id, cat, ward) %>%
  distinct() %>%
  mutate(
    staff = grepl("PE-", id),
    cat_ag = cat
    )

## Reconstructed full #####

simu_files = list.files(path = file.path(synthetic_path, "full_0-5agenda"), pattern = "matContact.*", full.names = T)
simu_data = data.frame()

iter=1
for(f in simu_files){
  data = read.csv2(f)
  
  graph_data = data %>%
    mutate(date_posix = floor_date(as_datetime(date_posix), "day")) %>%
    select(from, to, date_posix) %>%
    distinct %>%
    arrange(date_posix)
    
  print(nrow(graph_data))
  simu_data = rbind(simu_data,
                    get_assortativity_degree(graph_data, adm_data, iter, "Reconstructed", NA))
  
  iter=iter+1
}

## Observed #####
graph_data = interaction_real %>%
  rename(date_posix = date_posix_first) %>%
  mutate(date_posix = floor_date(date_posix, "day")) %>%
  filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
  select(from, to, date_posix) %>%
  distinct() %>%
  arrange(date_posix) %>%
  mutate(date_posix = as.Date("2020-05-06"))

observed_data = get_assortativity_degree(graph_data, adm_data, 1, "Observed", "day")

## Plot simulated assortativity
simu_data %>% 
  ggplot(., aes(x = day, y =assortativities, group = as.factor(iter), col = as.factor(iter))) + 
  geom_hline(yintercept = observed_data$assortativities) + 
  geom_line() + 
  theme_bw() +
  labs(x = "Simulated days", y = "Assortativity degree", col = "Simulation")
```


## Compute recurring contact probability 
```{r}
# Daily individual probability of recurring contacts and mean individual
# probability
simu_files = list.files(path = file.path(synthetic_path, "full_0"), pattern = "matContact.*", full.names = T)
p_df = data.frame()

for (f in simu_files) {
  pind = rep(NA, nrow(admission))
  
  for (i in seq_along(admission$id)) {
    ii = admission$id[i]
    
    # Get n days spent in the ward with a sensor 
    if (grepl("^PA-", ii)) {
      all_d = admission %>%
        filter(id == ii) %>%
        nest() %>%
        mutate(out = map(data, unroll_days)) %>%
        unnest(out) %>%
        .$out
    }
    
    if (grepl("^PE-", ii)) {
      all_d = schedule_real %>%
        filter(id == ii) %>%
        mutate(firstDate = floor_date(firstDate, "day"), lastDate = floor_date(lastDate, "day"), k = 1:n()) %>%
        arrange(firstDate) %>%
        group_by(k) %>%
        nest() %>%
        mutate(out = map(data, unroll_dates)) %>%
        unnest(out) %>%
        select(out) %>%
        distinct(out) %>%
        .$out
    }
      
    if (length(all_d) > 1) {
      interaction_d = vector("list", length(all_d))
      proba_d = rep(NA, length(all_d)-1)
      
      # Get lists of contacts per hour
      for (d in seq_along(all_d)) {
        dd = all_d[d]
        contacts = read.csv2(f) %>%
          filter(from == ii | to == ii, date_posix >= dd, date_posix < dd+3600*24) %>%
          select(from, to) %>%
          unlist()
        contacts = unique(contacts[contacts != ii])
        names(contacts) = NULL
        interaction_d[[d]] = contacts 
      }
      
      # Get hourly probability of recurring contacts
      if (length(all_d)>1) {
        for (h in 2:length(all_d)) {
          if (length(interaction_d[[d]]) > 0) {
            proba_d[d-1] = sum(interaction_d[[d]] %in% unlist(interaction_d[1:(d-1)])) / length(interaction_d[[d]])
          } else {
            proba_d[d-1] = 0
          }
        }
      }
      
      # Mean individual hourly probability of recurring contacts
      pind[i] = sum(proba_d) / length(proba_d)
      
    } else {
      pind[i] = 0
    }
  }
  
  p_df = bind_rows(p_df, data.frame(ids = admission$id, nSim = gsub("^.*Networks|_oneday.*$", "", f), pind = pind))
}


# Plot mean individual probability of recurring contacts
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  filter(!is.na(pind)) %>%
  ggplot(., aes(x = cat, y = pind)) +
  geom_boxplot() +
  geom_jitter() +
  theme_bw() +
  labs(x = "", y = "Probability of daily recurring contact")

# Mean probability of recurring contacts by individual category
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  group_by(cat) %>%
  summarise(m = mean(pind, na.rm = T), .groups = "drop")

# Comparison by category of individual
admission_nodscov2 %>%
  mutate(pind = pind) %>%
  filter(!is.na(pind)) %>%
  rstatix::wilcox_test(pind ~ cat, ref.group = "Paramedical")

# Mean probability when aggregating paramedical and medical staff
admission_nodscov2 %>%
  mutate(pind = pind, cat = ifelse(cat == "Patient", cat, "HCW")) %>%
  group_by(cat) %>%
  summarise(m = mean(pind, na.rm = T), .groups = "drop")
```
