---
title: "Compare synthetic and real contact data"
author: "Olivier GAUFRÈS"
date: "2024-10-08"
output: html_document
---

## Libraries
```{r setup, include=TRUE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(igraph)
library(ggnetwork)
library(ggtext)
library(cowplot)
rm(list = ls())

# Helper functions
source("helper-functions.R")

# Working directories and paths
synthetic_path = file.path("..", "..", "data", "data-synthetic-graphs")
```

## Load real and synthetic contact data
```{r data loading, echo = FALSE}
# List of individuals 
admission = read.csv2(file.path(synthetic_path, "admission.csv")) %>%
  mutate(
    firstDate = as.Date(firstDate),
    lastDate = as.Date(lastDate)
  )

# Schedule of healthcare workers
schedule_real = read.csv2(file.path(synthetic_path, "agenda.csv")) %>%
  mutate(
    firstDate = as_datetime(firstDate),
    lastDate = as_datetime(lastDate)
  )

# Real interaction data
interaction_real = read.csv2(file.path(synthetic_path, "interactions.csv")) %>%
  mutate(date_posix_first = as_datetime(date_posix_first))

# Synthetic data
interaction_synthetic = data.frame()
for (f in list.files(file.path(synthetic_path, "test"), pattern = "matContactBuiltSimulatedCtcNetworks", full.names = T)) {
  interaction_synthetic = bind_rows(
    interaction_synthetic,
    read.csv2(f) %>% 
      mutate(
        nSim = gsub("^.*Networks|_oneday.*$", "", f),
        firstDate = as_datetime(date_posix),
        lastDate = as_datetime(date_posix) + length
        )
  )
}
```

```{r}
data_real = interaction_real %>%
  rename(date_posix = date_posix_first)
ids_real = sort(unique(c(data_real$from, data_real$to)))

data_syn = read.csv2(file.path(synthetic_path, "matContactBuiltSimulatedCtcNetworks1_oneday.csv")) %>%
  mutate(date_posix = floor_date(as_datetime(date_posix), "hour"))
ids_syn = sort(unique(c(data_syn$from, data_syn$to)))

all(ids_syn %in% ids_real)
sort(ids_syn[!ids_syn %in% ids_real & !grepl("-[0-9]$", ids_syn)])
sort(admission$id[!admission$id %in% ids_real & !grepl("-[0-9]+$", admission$id)])
```

## Verify whether individuals in the synthetic network have at least one interaction per hour 
```{r at least one interaction per hour}
# Do all individuals have at least one contact per hour in the synthetic data?
at_least_one_contact = data.frame()

for (i in admission$id) {
  
  # Admission date    
  admissionDate = admission$firstDate[admission$id == i]
  proceed = F
  
  if (admission$status[admission$id == i] == "PE") {
    # Vector of hours of presence in the ward
    proceed = T
    lastHour = as_datetime("2020-05-07 23:00:00")
    hoursOfPresence = schedule_real %>%
      filter(id == i) %>%
      select(firstDate, lastDate) %>%
      mutate(r = 1:n()) %>%
      group_by(r) %>%
      nest() %>%
      mutate(seqHours = map(data, unroll_dates)) %>%
      unnest(seqHours) %>%
      ungroup() %>%
      distinct(seqHours) %>%
      filter(seqHours <= lastHour) %>%
      pull(seqHours)
  } 
  
  if (admission$status[admission$id == i] == "PA" & admissionDate <= as.Date("2020-05-07")) {
    proceed = T
    # Patient discharge date
    dischargeDate = min(
      admission$lastDate[admission$id == i],
      as.Date("2020-05-07")
    )

    # Hours of presence in the ward
    firstHour = as_datetime(paste0(admissionDate, "12:00:00"))
    lastHour = as_datetime(paste0(dischargeDate, "23:00:00"))
    hoursOfPresence = seq(firstHour, lastHour, 3600)
  }
  
  if (proceed) {
    # Hours with contacts in the ward 
    hoursInteracting = interaction_synthetic %>%
      filter(from == i | to == i) %>%
      group_by(from, to, date_posix, nSim) %>%
      nest() %>%
      mutate(dateSeq = map(data, unroll_dates)) %>%
      unnest(dateSeq) %>%
      ungroup() %>%
      select(-c(data, date_posix)) %>%
      distinct(nSim, dateSeq) %>%
      group_by(nSim) %>%
      summarise(atLeastOne = all(hoursOfPresence %in% dateSeq), .groups = "drop") %>% 
      mutate(id = i)
    
    at_least_one_contact = bind_rows(
      at_least_one_contact,
      hoursInteracting
    ) 
  }
}

# Check 
at_least_one_contact %>%
  mutate(status = gsub("-.*$", "", id)) %>%
  count(status, atLeastOne)

```
## Verification of the coherence between schedule and admission databases for healthcare workers
```{r}
# Schedule of healthcare workers 
ids_pe = admission$id[admission$status == "PE"]
interactions_in_schedule = data.frame()

for (i in ids_pe) {
  # Schedule of the HCW
  schedule_id = schedule_real %>%
    filter(id == i, lastDate <= as_datetime("2020-05-07 12:00:00")) %>%
    select(firstDate, lastDate)
  
  # Get all interactions
  if (sum(interaction_real$to == i | interaction_real$from == i) > 0) {
    interactions_id = interaction_real %>%
      filter(from == i| to == i) %>%
      select(date_posix_first, length) %>%
      mutate(n = 1:n())
  
    # Are all interactions within the schedule ?
    out_vec = expand.grid.df(
      schedule_id, 
      interactions_id
    ) %>%
      group_by(n) %>%
      summarise(out = any(date_posix_first >= firstDate & date_posix_first+length <= lastDate), .groups = "drop") %>%
      pull(out)
    
    interactions_in_schedule = bind_rows(
      interactions_in_schedule, 
      data.frame(
        id = i, 
        coherent_interactions = all(out_df)
      )
    )
  
  } else {
    interactions_in_schedule = bind_rows(
      interactions_in_schedule, 
      data.frame(
        id = i, 
        coherent_interactions = NA
      )
    )
  }
}

summary(interactions_in_schedule)
```


## Compare network characteristics

Analyses are based on Quentin's codes available [here](https://gitlab.pasteur.fr/qleclerc/network_algorithm/-/tree/main/analysis?ref_type=heads).

### Number of unique contacts and contact duration 
```{r}
# Prepare observed data 
data = interaction_real %>%
  select(from, to, date_posix_first, length) %>%
  rename(date_posix = date_posix_first)

dur_observed = data %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length)/60, .groups = "drop") %>% # Convert in minutes
  pull(length)

distrib_PAPA = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-patient")

distrib_PEPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PE-PE") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Staff-staff")

distrib_PAPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PE" | type == "PE-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-staff")

distrib_real = rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
  mutate(date_posix = paste0(date_posix, ":00")) %>%
  mutate(date_posix = factor(date_posix, levels = unique(date_posix))) %>%
  mutate(network = "Observed")

# Prepare reconstructed data 
data = read.csv2(file.path(synthetic_path, "matContactBuiltSimulatedCtcNetworks2_oneday.csv"))

dur_simu = data %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length)/60, .groups = "drop") %>%
  pull(length)

distrib_PAPA = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PA") %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-patient")

distrib_PEPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PE-PE") %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Staff-staff")

distrib_PAPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PE" | type == "PE-PA") %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-staff")

distrib_simu = rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
  mutate(date_posix = paste0(date_posix, ":00")) %>%
  mutate(date_posix = factor(date_posix, levels = unique(date_posix))) %>%
  mutate(network = "Reconstructed")


# Combine datasets 
distrib_all = rbind(distrib_real, distrib_simu) %>%
  mutate(network = factor(network, levels = unique(network))) %>%
  mutate(type = factor(type, levels = unique(type))) %>%
  mutate(date_posix = factor(date_posix, levels = c("0:00","1:00","2:00","3:00","4:00",
                                                    "5:00","6:00","7:00","8:00","9:00",
                                                    "10:00","11:00","12:00","13:00","14:00",
                                                    "15:00","16:00","17:00","18:00","19:00",
                                                    "20:00","21:00","22:00","23:00")))
  
# Compare number of unique contacts
pa = ggplot(distrib_all) +
  geom_ribbon(aes(date_posix, ymin = q25, ymax = q75, fill = network, group = interaction(type, network, day)),
              alpha = 0.3) +
  geom_point(aes(date_posix, med, colour = network)) +
  geom_line(aes(date_posix, med, colour = network, group = interaction(type, network, day))) +
  scale_colour_discrete(type = pal) +
  scale_fill_discrete(type = pal) +
  scale_y_continuous(breaks = seq(0,300,75)) +
  scale_x_discrete(breaks = c("0:00", "4:00", "8:00", "12:00",
                              "16:00","20:00")) +
  facet_grid(cols = vars(type), rows = vars(day)) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14),
        strip.text = element_text(size = 14))  +
  labs(x = "Hour", y = "Number of unique contacts", colour = "Network:", fill = "Network:")

# Compare contact duration 
pb = ggplot() +
  geom_boxplot(aes(y=dur_observed, x = "1", colour = "Observed"), outlier.shape = NA) +
  geom_boxplot(aes(y=dur_simu, x = "3", colour = "Reconstructed"), outlier.shape = NA) +
  scale_color_manual(values = pal) +
  scale_x_discrete(labels = c("Observed", "Reconstructed")) +
  coord_cartesian(ylim = c(0,35)) +
  guides(colour="none") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14)) +
  labs(y = "Contact duration (minutes)", x = "Network")

# Combine plots
plot_grid(pa, pb, nrow = 2, labels = c("a)", "b)"), rel_heights = c(1,0.8), hjust=0, vjust=c(1,0))
```


```{r}
# Prepare observed data 
data = interaction_real %>%
  select(from, to, date_posix_first, length) %>%
  rename(date_posix = date_posix_first)

dur_observed = data %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  group_by(from, to, date_posix) %>%
  summarise(length = sum(length)/60, .groups = "drop") %>% # Convert in minutes
  select(length) %>%
  mutate(network = "Observed")

distrib_PAPA = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-patient")

distrib_PEPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PE-PE") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Staff-staff")

distrib_PAPE = data %>%
  mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
  filter(type == "PA-PE" | type == "PE-PA") %>%
  mutate(date_posix = floor_date(date_posix, "hour")) %>%
  select(-length) %>%
  distinct() %>%
  count(date_posix) %>%
  ungroup() %>%
  mutate(day = wday(date_posix, week_start = 1)) %>%
  mutate(day = as.character(day)) %>%
  mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
  mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
  mutate(date_posix = hour(date_posix)) %>%
  group_by(date_posix, day) %>%
  summarise(med = median(n),
            q25 = quantile(n, 0.25),
            q75 = quantile(n, 0.75), .groups = "drop") %>%
  mutate(type = "Patient-staff")

distrib_real = rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
  mutate(date_posix = paste0(date_posix, ":00")) %>%
  mutate(date_posix = factor(date_posix, levels = unique(date_posix))) %>%
  mutate(network = "Observed")

# Prepare reconstructed data 
dur_sim = data.frame()
distrib_simu = data.frame()

for (f in list.files(file.path(synthetic_path, "test"), "matContactBuilt", full.names = T)) {
 data = read.csv2(f)

  dur_simu = data %>%
    mutate(date_posix = as_datetime(date_posix)) %>%
    mutate(date_posix = floor_date(date_posix, "hour")) %>%
    group_by(from, to, date_posix) %>%
    summarise(length = sum(length)/60, .groups = "drop") %>%
    mutate(network = paste0("Reconstructed-", gsub("^.*Networks|oneday.*$", "", f)))
  
  distrib_PAPA = data %>%
    mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
    filter(type == "PA-PA") %>%
    mutate(date_posix = as_datetime(date_posix)) %>%
    mutate(date_posix = floor_date(date_posix, "hour")) %>%
    select(-length) %>%
    distinct() %>%
    count(date_posix) %>%
    ungroup() %>%
    mutate(day = wday(date_posix, week_start = 1)) %>%
    mutate(day = as.character(day)) %>%
    mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
    mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
    mutate(date_posix = hour(date_posix)) %>%
    group_by(date_posix, day) %>%
    summarise(med = median(n),
              q25 = quantile(n, 0.25),
              q75 = quantile(n, 0.75), .groups = "drop") %>%
    mutate(type = "Patient-patient")
  
  distrib_PEPE = data %>%
    mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
    filter(type == "PE-PE") %>%
    mutate(date_posix = as_datetime(date_posix)) %>%
    mutate(date_posix = floor_date(date_posix, "hour")) %>%
    select(-length) %>%
    distinct() %>%
    count(date_posix) %>%
    ungroup() %>%
    mutate(day = wday(date_posix, week_start = 1)) %>%
    mutate(day = as.character(day)) %>%
    mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
    mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
    mutate(date_posix = hour(date_posix)) %>%
    group_by(date_posix, day) %>%
    summarise(med = median(n),
              q25 = quantile(n, 0.25),
              q75 = quantile(n, 0.75), .groups = "drop") %>%
    mutate(type = "Staff-staff")
  
  distrib_PAPE = data %>%
    mutate(type = paste0(substr(from, 1, 2), "-", substr(to, 1, 2))) %>%
    filter(type == "PA-PE" | type == "PE-PA") %>%
    mutate(date_posix = as_datetime(date_posix)) %>%
    mutate(date_posix = floor_date(date_posix, "hour")) %>%
    select(-length) %>%
    distinct() %>%
    count(date_posix) %>%
    ungroup() %>%
    mutate(day = wday(date_posix, week_start = 1)) %>%
    mutate(day = as.character(day)) %>%
    mutate(day = replace(day, day %in% c("6", "7"), "Weekend")) %>%
    mutate(day = replace(day, day != "Weekend", "Weekday")) %>%
    mutate(date_posix = hour(date_posix)) %>%
    group_by(date_posix, day) %>%
    summarise(med = median(n),
              q25 = quantile(n, 0.25),
              q75 = quantile(n, 0.75), .groups = "drop") %>%
    mutate(type = "Patient-staff")
  
  distrib_simu = bind_rows(
    distrib_simu,
    rbind(distrib_PAPA, distrib_PEPE, distrib_PAPE) %>%
      mutate(date_posix = paste0(date_posix, ":00")) %>%
      mutate(
        date_posix = factor(date_posix, levels = unique(date_posix)),
        network = paste0("Reconstructed-", gsub(".*Networks|_oneday.*$", "", f))
        ) 
  )
}

# Combine datasets 
distrib_all = rbind(distrib_real, distrib_simu) %>%
  mutate(
    type = factor(type, levels = unique(type)),
                  date_posix = factor(date_posix, levels = c("0:00","1:00","2:00","3:00","4:00",
                                                             "5:00","6:00","7:00","8:00","9:00",
                                                             "10:00","11:00","12:00","13:00","14:00",
                                                             "15:00","16:00","17:00","18:00","19:00",
                                                             "20:00","21:00","22:00","23:00"))
    )
  
# Compare number of unique contacts
pa = ggplot(distrib_all) +
  geom_ribbon(aes(date_posix, ymin = q25, ymax = q75, fill = network, group = interaction(type, network, day)),
              alpha = 0.3) +
  geom_point(aes(date_posix, med, colour = network)) +
  geom_line(aes(date_posix, med, colour = network, group = interaction(type, network, day))) +
  scale_colour_discrete(type = c("orange", colorRampPalette(c("dodgerblue4", "lightskyblue"))(10))) +
  scale_fill_discrete(type = c("orange", colorRampPalette(c("dodgerblue4", "lightskyblue"))(10))) +
  scale_y_continuous(breaks = seq(0,300,75)) +
  scale_x_discrete(breaks = c("0:00", "4:00", "8:00", "12:00",
                              "16:00","20:00")) +
  facet_grid(cols = vars(type), rows = vars(day)) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14),
        strip.text = element_text(size = 14))  +
  labs(x = "Hour", y = "Number of unique contacts", colour = "Network:", fill = "Network:")

# Compare contact duration 
pb = bind_rows(dur_observed, dur_simu) %>%
  ggplot() +
  geom_boxplot(aes(y=dur_observed, x = "1", colour = "Observed"), outlier.shape = NA) +
  geom_boxplot(aes(y=dur_simu, x = "3", colour = "Reconstructed"), outlier.shape = NA) +
  scale_color_manual(values = pal) +
  scale_x_discrete(labels = c("Observed", "Reconstructed")) +
  coord_cartesian(ylim = c(0,35)) +
  guides(colour="none") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14)) +
  labs(y = "Contact duration (minutes)", x = "Network")

# Combine plots
# plot_grid(pa, pb, nrow = 2, labels = c("a)", "b)"), rel_heights = c(1,0.8), hjust=0, vjust=c(1,0))
```

### Network metrics (degree, global efficiency, transitivity, assortativity, temporal correlation, density)
```{r compare networks}
adm_data = admission %>%
  select(id, cat, ward) %>%
  distinct() %>%
  mutate(
    staff = grepl("PE-", id),
    cat_ag = cat
    )

data = interaction_real %>%
  select(from, to, date_posix_first, length) %>%
  rename(date_posix = date_posix_first)

graph_data = data %>%
  mutate(date_posix = floor_date(date_posix, "day")) %>%
  filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
  select(from, to, date_posix) %>%
  distinct() %>%
  arrange(date_posix)

simu_files = list.files(path = file.path(synthetic_path, "test"), pattern = "matContact.*", full.names = T)

## Reconstructed full #####

iter=1

simu_data = data.frame()

for(f in simu_files){
  
  data = read.csv2(f)
  
  graph_data = data %>%
    mutate(date_posix = floor_date(as_datetime(date_posix), "day")) %>%
    filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
    select(from, to, date_posix) %>%
    distinct %>%
    arrange(date_posix)
  
  simu_data = rbind(simu_data,
                    get_net_metrics(graph_data, adm_data, iter, "Reconstructed"))
  
  iter=iter+1
}

## Observed #####
graph_data = interaction_real %>%
  rename(date_posix = date_posix_first) %>%
  mutate(date_posix = floor_date(date_posix, "day")) %>%
  filter(date_posix >= as_date("2020-05-06") & date_posix <= as_date("2020-05-07")) %>%
  select(from, to, date_posix) %>%
  distinct() %>%
  arrange(date_posix) %>%
  mutate(date_posix = as.Date("2020-05-06"))

observed_data = get_net_metrics(graph_data, adm_data, 1, "Observed")


# GROUPED #####

summary_data = rbind(simu_data, observed_data)

# for convenience, save the summary here and read it in later
# write.csv(summary_data, here::here("Data", "summary_data.csv"), row.names = F)
# summary_data = read.csv(here::here("Data", "summary_data.csv"))

summary_data = summary_data %>%
  mutate(network = factor(network,
                          levels = c("Observed", "Reconstructed")))

summary_data = summary_data %>%
  group_by(day, network) %>%
  summarise(across(everything(), median), .groups = "drop") %>%
  select(-iter)

summary_data %>%
  select(-day) %>%
  group_by(network) %>%
  summarise(across(everything(), \(x) quantile(x, probs=0.75))) %>%
  View

pa = ggplot() +
  geom_boxplot(data=summary_data,
               aes(x = network, y = degrees, colour = network), linewidth = 0.8) +
  scale_colour_discrete(type = pal) +
  theme_bw() +
  guides(colour = "none") +
  labs(x = "Network", y = "Degree (daily)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12))

pb = ggplot() +
  geom_boxplot(data=summary_data,
               aes(x = network, y = efficiencies, colour = network), linewidth = 0.8) +
  scale_colour_discrete(type = pal) +
  theme_bw() +
  guides(colour = "none") +
  labs(x = "Network", y = "Global efficiency") +
  scale_y_continuous(breaks = seq(0,0.8,0.1)) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12))

pc = ggplot() +
  geom_boxplot(data=summary_data,
               aes(x = network, y = transitivities, colour = network), linewidth = 0.8) +
  scale_colour_discrete(type = pal) +
  theme_bw() +
  guides(colour = "none") +
  labs(x = "Network", y = "Transitivity") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.y = element_text(size = 12))

pd = ggplot() +
  geom_boxplot(data=summary_data,
               aes(x = network, y = assortativities, colour = network), linewidth = 0.8) +
  scale_colour_discrete(type = pal) +
  theme_bw() +
  guides(colour = "none") +
  labs(x = "Network", y = "Assortativity (degree)") +
  theme(axis.text.x = element_text(size = 12, angle = 30, hjust = 1),
        axis.title = element_text(size = 12),
        axis.text.y = element_text(size = 12))

plot_grid(pa,pb,pc,pd, nrow=2,
                    labels = c("a)", "b)", "c)", "d)"),
          hjust = 0, vjust=1, align = "v", rel_heights = c(0.77, 1))


ggplot() +
  geom_boxplot(data=summary_data,
               aes(x = network, y = densities, colour = network), linewidth = 0.8) +
  scale_colour_discrete(type = pal) +
  scale_y_continuous(breaks = seq(0,0.3,0.05)) +
  theme_bw() +
  guides(colour = "none") +
  labs(x = "Network", y = "Density") +
  theme(axis.text.x = element_text(size = 12),
        axis.title = element_text(size = 12),
        axis.text.y = element_text(size = 12))
```