---
title: "location-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-05-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Librairies
library(dplyr)
library(ggplot2)
library(lubridate)
library(igraph)
library(tidyr)
library(viridis)
library(purrr)
library(stringr)
rm(list = ls())

# Source helper functions
source("helper-functions.R")

# Paths
nodscov2_path = file.path("..", "..", "data", "data-nodscov2")
nodscov2_synthetic_path <- file.path("..", "..", "data", "data-synthetic-graphs") 
loc_nodscov2_path <- file.path(nodscov2_path, "loc")

if (!dir.exists(loc_nodscov2_path)) dir.create(loc_nodscov2_path, recursive = TRUE)
```

## Load Nods-Cov-2 data 
```{r Load data}
# Admission data
admission = read.csv2(file.path(nodscov2_path, "clean", "admission_cleaned.csv")) %>%
  mutate(firstDate = as_date(firstDate), lastDate = as_date(lastDate)) 

# HCW schedule 
agenda = read.csv2(file.path(nodscov2_path, "clean", "agenda_cleaned.csv")) %>%
  mutate(firstDate = as_datetime(firstDate), lastDate = as_datetime(lastDate)) 

# Patient rooms 
patient_rooms = read.csv2(file.path(nodscov2_synthetic_path, "loc", "patient_rooms.csv")) %>%
  filter(id %in% admission$id)

# Interaction data 
interactions = read.csv2(file.path(nodscov2_path, "clean", "interaction_cleaned.csv")) %>%
  mutate(date_posix = as_datetime(date_posix)) %>%
  left_join(., admission %>% select(id, status), by = c("from" = "id")) %>%
  rename(from_status = status) %>%
  left_join(., admission %>% select(id, status), by = c("to" = "id")) %>%
  rename(to_status = status)
```


## Retrieve ids of different categories
```{r}
## Ids of participants by category
id_paramedical <- admission %>% filter(cat == "Paramedical") %>% pull(id)
id_medical <- admission %>% filter(cat == "Medical") %>% pull(id)
id_hcw <- admission %>% filter(status == "PE") %>% pull(id)
id_patient <- admission %>% filter(status == "PA") %>% pull(id)

# Verify that all individuals interact
id_interacting <- interactions %>%
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
  distinct(individual) %>% 
  arrange(individual) %>%
  pull()
id_total <- admission %>% distinct(id) %>% arrange(id) %>% pull()
identical(id_total, id_interacting)

# Individuals with no interactions are patients present only in the morning 
# of the last day of the simulation
# We keep them in the simulations but they won't participate much in the 
# transmission dynamics 
id_not_interacting <- setdiff(id_total, id_interacting)
admission %>%
  filter(id %in% id_not_interacting)
```

## Create the room dataframe 
```{r}
# Last id of patient rooms
n_patient_rooms = max(patient_rooms$room)

# Ids of patient rooms
id_room_patient = as.character(unique(patient_rooms$room))

# Id of double room
load(file.path(nodscov2_path, "clean", "double_rooms.rda"))
double_rooms_id = sort(unique(patient_rooms$room[patient_rooms$id %in% unlist(double_rooms)]))

# Dataframe with all rooms
rooms = patient_rooms %>%
  mutate(
    volume = ifelse(room %in% double_rooms_id, 30*2.2, 20*2.2), #18 square meters * 2.2 height except for double room
    id_room = as.character(room),
    room = as.character(room)
    ) %>% 
  bind_rows(.,
            data.frame(room = "Medical Restroom", id = "R-M-PE", volume = 30 * 2.2, id_room = as.character(n_patient_rooms+1)),
            data.frame(room = "Paramedical Restroom", id = "R-PM-PE", volume =  40 * 2.2, id_room = as.character(n_patient_rooms+2)),
            data.frame(room = "Nursing station", id = "PM-PE", volume = 20 * 2.2, id_room = as.character(n_patient_rooms+3)),
            data.frame(room = "Office", id = "M-PE", volume = 20 * 2.2, id_room = as.character(n_patient_rooms+4)),
            data.frame(room = "Corridor", id = "ALL", volume = 200 * 2.2, id_room = as.character(n_patient_rooms+5))
            ) 
```

## Subdivide contact data into 30 seconds time steps and save interaction clusters 
```{r Subdividing interactions}
# Global interaction object
begin_date <- min(interactions$date_posix)
end_date <- max(interactions$date_posix + interactions$length)
time_spent <- difftime(end_date, begin_date, units = "secs")  

n_subdivisions <- floor(as.numeric(time_spent) / 30) ## Time spent * hours * minutes * 2 (number of time subdivisions)
## floor because of the manner we extract the interactions (=30sec, i.e. at  the end, interactions are <30sec -> we dont take these)

# # t = 1 -> [0,30[sec
global_interaction <- lapply(1:n_subdivisions, function(t){
  interactions_t <- interactions %>%
    filter(date_posix <= (begin_date + (t-1)*30), date_posix + length >= begin_date + (t)*30 ) %>%
    mutate(time = t) %>%
    select(from, to, time, from_status, to_status)

  return(interactions_t)
})
save(global_interaction, file = file.path(nodscov2_path, "loc", "global_interaction.rda"))

# List of interaction clusters
clusters <- lapply(global_interaction, function(df) {
  # df to non oriented graph based on interaction happening at time t
  graph <- graph_from_data_frame(df, directed = FALSE)
  # Extract connected component
  clusters <- components(graph)$membership
  # clusters to list (unique list of individual)
  clusters_list <- lapply(unique(clusters), function(i) {
    #for each cluster i, we extract the vertices/nodes of the graph -> individual names in each clusters
    as.character(V(graph)[clusters == i]$name)
  })
  return(clusters_list)
})
save(clusters, file = file.path(nodscov2_path, "loc", "clusters.rda"))

load(file.path(nodscov2_path, "loc", "global_interaction.rda"))
load(file.path(nodscov2_path, "loc", "clusters.rda"))
```

## Location inference for all individuals during close-proximity interactions
```{r Loc for interactions}
############################################################
## ASSIGNING location FOR THE INDIVIDUALS INTERACTING ##
############################################################
# This code chunk uses the following input data
    # n_subdivisions
    # id_total
    # id_medical
    # id_paramedical
    # begin_date
    # global_interaction
    # clusters

# It returns the following objects
    # global_location : list with the localisation of all interaction clusters
    # cluster info list


## Store info when there is more than one patient in clusters -> fix later
cluster_info_list <- list()
global_location <- list()

global_location <- lapply(1:n_subdivisions, function(t) {
  location_t <- data.frame(id = id_total, location = NA, time = t) ##only for individuals that interact
  # Interactions at time t
  interactions_t <- global_interaction[[t]] %>% mutate(location = NA)
  clusters_t <- clusters[[t]]
  # For each clusters of individuals at time t
  lapply(clusters_t, function(cluster) {

    # Remove duplicates if any
    cluster = sort(unique(cluster))

    ###########################
    ## CLUSTER WITH PATIENTS ##
    ###########################
    # IF THERE IS NO PATIENTS
    NO_PATIENT <- all(!grepl("^PA-", cluster))
    # IF THERE IS ONLY ONE PATIENT IN THE CLUSTER
    ONE_PATIENT <- sum(grepl("^PA-", cluster)) == 1
    one_patient_room <- ifelse(ONE_PATIENT, rooms$id_room[rooms$id == cluster[grepl("^PA-", cluster)]], "-2")
    ## IF IN DOUBLE ROOM (MUST BE ONLY THE TWO PATIENTS, NOT THE TWO PATIENT + ANOTHER PATIENT)
    IN_DOUBLE_ROOM_N1 <- !NO_PATIENT & all(cluster[grepl("^PA-", cluster)] %in% double_rooms[[1]])
    IN_DOUBLE_ROOM_N2 <- !NO_PATIENT & all(cluster[grepl("^PA-", cluster)] %in% double_rooms[[2]])
    # IF THERE IS MULTIPLE PATIENTS IN THE CLUSTER (AND NOT IN DOUBLE ROOM)
    MULTIPLE_PATIENT <- sum(grepl("^PA-", cluster)) > 1 & !(IN_DOUBLE_ROOM_N1 | IN_DOUBLE_ROOM_N2)

    ##############################
    ## CLUSTER WITHOUT PATIENTS ##
    ##############################
    NO_MEDICAL <- sum(cluster %in% id_medical) == 0
    NO_PARAMEDICAL <- sum(cluster %in% id_paramedical) == 0

    ONLY_PARAMEDICAL <- NO_PATIENT & NO_MEDICAL
    ONLY_MEDICAL <- NO_PATIENT & NO_PARAMEDICAL
    MEDICAL_AND_PARAMEDICAL <- NO_PATIENT & !NO_MEDICAL & !NO_PARAMEDICAL

    #####################
    ## TIME CONDITIONS ##
    #####################
    time_t <- begin_date + (t-1)*30
    DAY <- between(hour(time_t), 7, 20)
    NIGHT <- between(hour(time_t), 21, 24) | between(hour(time_t), 0, 6)

    #################################
    ## location OF THE CLUSTER ##
    #################################
    cluster_location <- case_when(
      MULTIPLE_PATIENT ~ rooms$id_room[rooms$id == "ALL"],
      IN_DOUBLE_ROOM_N1 ~ as.character(double_rooms_id[1]),
      IN_DOUBLE_ROOM_N2 ~ as.character(double_rooms_id[2]),
      ONE_PATIENT ~ one_patient_room,
      ONLY_MEDICAL ~ rooms$id_room[rooms$id == "M-PE"], ## ONLY MEDICAL INTERACTING -> OFFICE
      ONLY_PARAMEDICAL ~ rooms$id_room[rooms$id == "PM-PE"], ## ONLY PARAMEDICAL INTERACTING -> NURSING STATION
      MEDICAL_AND_PARAMEDICAL ~ rooms$id_room[rooms$id == "PM-PE"], ## ONLY MED AND PARAMED -> NURSING STATION
      .default = "-3"
    )
    ## Assign the location for individuals inside the cluster
    # <<- to edit location_t defined outside clusters_t's lapply scope
    interactions_t$location[interactions_t$from %in% cluster] <<- cluster_location ## if from is in the cluster, to will be also
    location_t$location[location_t$id %in% cluster] <<- cluster_location

    ## MULTIPLE PATIENTS IN THE CLUSTER --> TEMPORARY, FIXED LATER
    if (MULTIPLE_PATIENT) {
      cluster_possible_location <- rooms$id_room[rooms$id %in% cluster[grepl("^PA-", cluster)]]
      cluster_info <- data.frame(time = t, Patients = cluster[grepl("^PA-", cluster)], cluster = toString(cluster))
      cluster_info_list <<- append(cluster_info_list, list(cluster_info))
    }
  })

  ## ADD THE location IN GLOBAL_INTERACTION (we could have added the cluster id but its useless for now)
  global_interaction[[t]] <<- interactions_t
  return(location_t)
})

save(global_location, file = file.path(nodscov2_path, "loc", "global_location.rda"))
load(file.path(nodscov2_path, "loc", "global_location.rda"))
```

## Smooth individual trajectories and associate location when individuals are 
## present without close-proximity interactions  
```{r}
# SMOOTH INDIVIDUAL TRAJECTORIES
# Get the data in wide format
locations = do.call("rbind", global_location) %>%
  pivot_wider(names_from = id, values_from = location) %>%
  arrange(time) %>%
  select(-time) 
rm(global_location)

# Add when individuals are not present in the ward and add their room 
# otherwise (Patients)
identical(names(locations[, id_patient]), id_patient)
locations[,id_patient[id_patient %in% id_interacting]] = as_tibble(mapply(function(x, y) {
  # Assign "NOT HERE" when not present in the ward
  firstDate = as_datetime(paste(admission$firstDate[admission$id==y], "00:00:00"))
  firstDate = case_when(begin_date>firstDate ~ begin_date, .default = firstDate)
  lastDate = as_datetime(paste(admission$lastDate[admission$id==y], "23:59:30"))
  lastDate = case_when(end_date<lastDate ~ end_date, .default = lastDate)
  allDates = seq(begin_date, end_date-30, 30)
  present = seq(firstDate, lastDate-30, 30)
  not_present = which(!allDates %in% present)
  if (length(not_present) != sum(is.na(x[not_present]))) stop(paste(y, "has assigned location when individual not in the ward"))
  x[not_present] = -1
  
  # Assign patient room when present in the ward and not interacting
  x[is.na(x)] = patient_rooms$room[patient_rooms$id==y]
  return(x)
},
locations[, id_patient[id_patient %in% id_interacting]],
id_patient[id_patient %in% id_interacting]))

# Add when individuals are not present in the ward and smooth
# their individual trajectory (HCW)
identical(names(locations[, id_hcw]), id_hcw)
patient_rooms_ids = as.character(sort(unique(patient_rooms$room)))
locations[,id_hcw] = as_tibble(mapply(function(x, y) {
  # Assign "NOT HERE" when not present in the ward
  allDates = seq(begin_date, end_date-30, 30)
  present = agenda %>% 
    filter(id == y) %>%
    select(firstDate, lastDate) %>%
    mutate(n = 1:n()) %>%
    nest(.by = n) %>%
    mutate(data=map(data, unroll_30s)) %>%
    unnest(data) %>%
    pull(data)
  not_present = which(!allDates %in% present)
  if (!all(is.na(x[not_present]))) stop(paste(y, "has location assigned when not present in the ward"))
  x[not_present] = -1
  
  # Split vector into elements of consecutive identical values  
  x_split = split(x, data.table::rleid(x))
  
  # Assign locations to elements
  for (k in seq_along(x_split)) {
    
    current = x_split[[k]]
    if (!is.na(unique(current))) next()
    
    before = ifelse(k == 1, "-1", unique(x_split[[k-1]]))
    after = ifelse(k == length(x_split), "-1", unique(x_split[[k+1]]))
    
      # If between patient room and less than 5 mins
    if (before == after & length(current) <= 10 & before %in% patient_rooms_ids) {
      x_split[[k]] = rep(before, length(current))
    } else if (length(current) == 1) {
      # If between two different rooms and only 30 seconds --> corridor
      x_split[[k]] = c("22")
    } else {
      # If between two different rooms and/or more than 5 mins
      resting_room = ifelse(y %in% id_medical, "18", "19")
      x_split[[k]] = c("22", rep(resting_room, length(current)-2), "22")
    }
  }

  # Return 
  out = unlist(x_split)
  return(out)
},
locations[,id_hcw], 
id_hcw))

# Convert locations into a list
write.csv2(locations, file.path(nodscov2_path, "loc", "locations_long_format.csv"), quote = F, row.names = F)
locations = locations %>%
    mutate(time = 1:n()) %>%
    pivot_longer(-time, names_to = "id", values_to = "location")
global_location = split(locations, f = locations$time)
rm(locations)
```

## Save to an .RData file
```{r Save to .RData}
save(clusters,
     global_location,
     global_interaction,
     admission,
     rooms,
     # shifts, # Check whether to remove or not 
     id_hcw,
     id_patient,
     begin_date,
     end_date,
     n_subdivisions,
     file = file.path(nodscov2_path, "loc", "nodscov2-reconstructed-locations.rda"))
```
