---
title: "dev-figures-loc-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-07-09"
output: html_document
---

## Load helper functions and data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
library(dplyr)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(igraph)
library(tidyr)
library(viridis)
library(purrr)
library(stringr)
library(extrafont)
library(extrafontdb)
library(cowplot)
rm(list=ls())

# Helper functions
source("helper-functions.R")

# Input data paths
data_to_load = "simulated"
if (data_to_load == "observed") data_path <- file.path("..", "..", "data", "data-nodscov2") 
if (data_to_load == "simulated") data_path <- file.path("..", "..", "data", "data-synthetic-graphs") 

# Fgrue paths
fig_loc_path <- file.path("..","..", "fig", "loc-reconstruction")
ind_paths_path <- file.path("..","..", "fig", "individual-paths")
if (!dir.exists(fig_loc_path)) dir.create(fig_loc_path, recursive = TRUE)
if (!dir.exists(ind_paths_path)) dir.create(ind_paths_path, recursive = TRUE)

# Load data
load(file.path(data_path, "loc", "nodscov2-reconstructed-locations.rda"))
rm(global_interaction)

if (exists("global_localization")) global_location = global_localization
```


## Plots
### Dictionaries
```{r}
## Dictionaries
dict_rooms = setNames(as.character(rooms %>% mutate(room = ifelse(room == id_room, "Patient rooms", room)) %>% distinct(room, id_room) %>% pull(room)), 
                      rooms %>% mutate(room = ifelse(room == id_room, "Patient rooms", room)) %>% distinct(room, id_room) %>% pull(id_room))

dict_times = setNames(as.character(seq(begin_date, end_date-30, 30)),
                      as.character(1:length(global_location)))

dict_id_cat = setNames(admission %>% select(id, cat) %>% pull(cat),
                       admission %>% select(id, cat) %>% pull(id))
```

### Plot distribution of time spent in resting rooms/corridor stratified by category of HCW
```{r Time spent in Restroom/Corridor by HCW cat}
## Load location data in long format
paths = read.csv2(file.path(data_path, "loc", "locations_long_format.csv"))

## Boxplot
ids_to_analyze = colnames(paths)[-1]
ids_to_analyze = ids_to_analyze[!ids_to_analyze %in% c("PA.001.0073.O.D.9", "PA.001.0115.D.P.9")]
cumulative_time = do.call("rbind", mapply(
  function(x,y) {
     out = data.frame(
       time = floor_date(seq(begin_date, end_date-30, 30), "day"),
       loc = x
       ) %>%
       filter(loc != "-1") %>%
       mutate(loc = recode(loc, !!!dict_rooms), time = as_date(floor_date(time, "day"))) %>%
       group_by(time, loc) %>%
       # Convert time spent in each room into hours 
       summarise(time_spent = n()*30/3600, .groups = "drop") #%>%
       # filter(!time %in% floor_date(c(begin_date, end_date-24*3600, end_date), "day")) %>%
       # group_by(loc) %>%
       # summarise(time_spent = mean(time_spent), .groups = "drop") %>%
       # mutate(id = y)
     
     if (grepl("^PE-", y)) {
       time_per_day_in_ward = data.frame(
         time = floor_date(seq(begin_date, end_date-30, 30), "day"),
         loc = x
       ) %>%
         filter(loc == "-1") %>%
         mutate(time = as_date(floor_date(time, "day"))) %>%
         group_by(time) %>%
         # Convert time spent in each room into hours 
         summarise(time_in_ward = 24-n()*30/3600, .groups = "drop") %>%
         filter(time_in_ward > 0) #%>%
         # summarise(time_in_ward = median(time_in_ward), .groups = "drop") %>%
         # pull(time_in_ward)
       
       out = out %>%
         left_join(., time_per_day_in_ward, by = "time") %>%
         mutate(time_spent = time_spent / time_in_ward) %>%
         group_by(loc) %>%
         summarise(time_spent = mean(time_spent), .groups = "drop")

     } else {
       out = out %>%
         group_by(time) %>%
         mutate(time_spent = time_spent/sum(time_spent)) %>%
         ungroup() %>%
         group_by(loc) %>%
         summarise(time_spent = mean(time_spent), .groups = "drop")
     }
     out$id = y
     return(out)
  },
  paths[, ids_to_analyze],
  ids_to_analyze,
  SIMPLIFY = F
))
  
# Boxplot with the cumulative time spent in the different rooms
p = cumulative_time %>%
  mutate(
    id = gsub("\\.", "-", id), 
    loc = gsub("Restroom", "resting room", loc)
    ) %>%
  left_join(., admission %>% select(id, cat), by = "id") %>%
  ggplot(., aes(x = cat, y = time_spent, fill = cat)) +
  geom_boxplot(outliers = F) +
  geom_jitter(size = 0.1) +
  expand_limits(y = c(0,1)) +
  facet_grid(cols = vars(loc)) +
  # ggh4x::facet_grid2(cols = vars(loc), scales = "free_y", independent  ="y") +
  scale_fill_manual(values = pal) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(), 
        legend.position = "none") +
  labs(y = "Mean proportion of cumulative time spent\nin room per day")
ggsave(file.path(fig_loc_path, paste0("cumulative_time_", data_to_load, ".png")), p, height = 4, width = 11)

# Same data but displayed in a different way (all locations for each individual category)
p = cumulative_time %>%
  mutate(
    id = gsub("\\.", "-", id),
    loc = gsub("Restroom", "resting room", loc)
    ) %>%
  left_join(., admission %>% select(id, cat), by = "id") %>%
  ggplot(., aes(x = loc, y = time_spent, fill = loc)) +
  geom_boxplot(outliers = F) +
  geom_jitter(size = 0.1) +
  expand_limits(y = c(0,1)) +
  facet_grid(cols = vars(cat)) +
  # ggh4x::facet_grid2(cols = vars(cat), scales = "free_y", independent  ="y") +
  # scale_fill_manual(values = pal) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(), 
        legend.position = "none") +
  labs(y = "Mean proportion of cumulative time spent\nin room per day")
ggsave(file.path(fig_loc_path, paste0("cumulative_time_", data_to_load, "_v2.png")), p, height = 4, width = 11)
```

### Plot individual trajectories for randomly selected individuals and days
```{r individual trajectories}
# Example of individual trajectories 
set.seed(123)
agenda = read.csv2(file.path(nodscov2_synthetic_path, "agenda.csv"))
individuals_to_show = c(
  sample(admission$id[admission$cat == "Paramedical"], 5),
  sample(admission$id[admission$cat == "Medical"], 5),
  sample(id_patient, 5)
  )

for (y in individuals_to_show) {
  if (grepl("^PA-", y)) {
    days_of_presence = seq(admission %>% filter(id == y) %>% pull(firstDate), 
                           admission %>% filter(id == y) %>% pull(lastDate), 
                           1)
  } else {
    days_of_presence = agenda %>% 
      filter(id == y) %>% 
      mutate(k = 1:n(), firstDate = as_date(floor_date(as_datetime(firstDate), "day")), lastDate = as_date(floor_date(as_datetime(lastDate), "day"))) %>%
      nest(.by = k) %>%
      mutate(data = map(data, unroll_days)) %>%
      unnest(data) %>%
      pull(data)
  }
  
  random_day = sample(unique(days_of_presence), 1)
  individual_path = data.frame(
    time = seq(begin_date, end_date-30, 30),
    loc = paths[[gsub("-", ".", y)]],
    cat = admission$cat[admission$id == y] 
    ) %>%
    filter(floor_date(time, "day") == random_day) %>%
    mutate(loc = recode(loc, !!!c(dict_rooms, "-1" = "Absent")))
  individual_cat = unique(individual_path$cat)
  
  p = ggplot(individual_path, aes(x = time, y = loc, group=cat)) +
    geom_path(col = pal[individual_cat]) +
    theme_bw() +
    labs(x = "", y = paste("Location of", y))
  ggsave(file.path(ind_paths_path, paste0(gsub("\\.", "-", y), ".png")), p, height = 4, width = 10)
}

# Plot one week for the same individual
y = individuals_to_show[1]
if (grepl("^PA-", y)) {
  days_of_presence = seq(admission %>% filter(id == y) %>% pull(firstDate), 
                         admission %>% filter(id == y) %>% pull(lastDate), 
                         1)
} else {
  days_of_presence = agenda %>% 
    filter(id == y) %>% 
    mutate(k = 1:n(), firstDate = as_date(floor_date(as_datetime(firstDate), "day")), lastDate = as_date(floor_date(as_datetime(lastDate), "day"))) %>%
    nest(.by = k) %>%
    mutate(data = map(data, unroll_days)) %>%
    unnest(data) %>%
    pull(data)
}

random_day = sample(unique(days_of_presence), 1)
individual_path = data.frame(
  time = seq(begin_date, end_date-30, 30),
  loc = paths[[gsub("-", ".", y)]],
  cat = admission$cat[admission$id == y] 
  ) %>%
  filter(floor_date(time, "day") %in% seq(random_day, random_day+7, 1)) %>%
  mutate(loc = recode(loc, !!!c(dict_rooms, "-1" = "Absent")))
individual_cat = unique(individual_path$cat)

p = ggplot(individual_path, aes(x = time, y = loc, group=cat)) +
  geom_path(col = pal[individual_cat]) +
  theme_bw() +
  labs(x = "", y = paste("Location of", y))
# ggsave(file.path(ind_paths_path, paste0(gsub("\\.", "-", y), ".png")), p, height = 4, width = 10)

```

### Plot contact-related information
```{r}
# Patient - Patient contact rate per hour 
interactions_synthetic = read.csv2(file.path(data_path, "input", "interactions_trimmed.csv")) %>%
  mutate(
    interaction_type = case_when(
      from_status == "PA" & to_status == "PA" ~ "PA-PA",
      from_status != to_status ~ "PA-PE",
      from_status == "PE" & to_status == "PE" ~ "PE-PE"
      ),
    date_hour = floor_date(as_datetime(date_posix), "hour")
  ) %>%
  group_by(interaction_type, date_hour) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(data = "synthetic")

interactions_observed = read.csv2(file.path("..", "..", "data", "data-nodscov2", "clean", "interaction_cleaned.csv")) %>%
  mutate(
    interaction_type = case_when(
      grepl("^PA-", from) & grepl("^PA-", to) ~ "PA-PA",
      grepl("^PA-", from) != grepl("^PA-", to) ~ "PA-PE",
      grepl("^PE-", to) & grepl("^PE-", to) ~ "PE-PE"
      ),
    date_hour = floor_date(as_datetime(date_posix), "hour")
  ) %>%
  group_by(interaction_type, date_hour) %>%
  summarise(n = n(), .groups = "drop") %>%
  mutate(data = "observed")

# Plot
bind_rows(interactions_observed, interactions_synthetic) %>%
  ggplot(., aes(x = data, y = n)) +
  ggh4x::facet_grid2(cols = vars(interaction_type), scales = "free_y", independent  ="y") +
  geom_boxplot(outliers = F) +
  geom_jitter(size = 0.5) +
  theme_bw() +
  labs(x = "Contact dataset", y = "Distribution of the number of interactions per hour")
```

```{r}
# Load cluster data 
id_paramedical = admission$id[admission$cat =="Paramedical"]
id_medical = admission$id[admission$cat =="Medical"]

cluster_composition = lapply(seq_along(clusters), function(x) {
  out = sapply(clusters[[x]], function(y) {
    out2 = data.frame(patient = sum(y %in% id_patient), 
                      medical = sum(y %in% id_medical), 
                      paramedical = sum(y %in% id_paramedical),
                      n = length(y))
    return(out2)
  })
  out=data.frame(t(out))
  out$time = x
  return(out)
}
)

# Plot custer composition
p = do.call("rbind", cluster_composition) %>%
  mutate(cluster_type = case_when(
    paramedical > 0 & medical == 0 & patient == 0 ~ "Paramedical",
    paramedical == 0 & medical > 0 & patient == 0 ~ "Medical",
    paramedical == 0 & medical == 0 & patient > 0 ~ "Patient",
    paramedical > 0 & medical == 0 & patient > 0 ~ "Paramed-Patient",
    paramedical == 0 & medical > 0 & patient > 0 ~ "Medical-Patient",
    .default = "All"
  ), 
  time = floor_date(as_datetime(recode(time, !!!dict_times)), "hour")
    ) %>%
  group_by(time, cluster_type) %>%
  summarise(n=n(), .groups = "drop") %>%
  ggplot(., aes(x = time, y = n, col = cluster_type)) +
  geom_line() +
  theme_bw()

```



```{r}
# ggplot(paths %>% filter(id == ind), aes(x = time * 30 + begin_date, y = room, colour = ind_type)) +
#     geom_path(aes(group = id)) +  # geom_path -> connected lines
#     geom_point(aes(shape = id)) +  # geom_point -> points
#     labs(title = title, x = "Time", y = "") +
#     theme_bw() +
#     scale_colour_manual(values = pal) +
#     scale_x_continuous(breaks = time_breaks, labels = time_labels) +
#     theme(
#     plot.title = element_text(size = 25, hjust = 0.5, family = "Arial monospaced for SAP"), #use extrafont package if the font is not installed locally
#     axis.text = element_text(size = 20, family = "Arial monospaced for SAP"),
#     axis.title = element_text(size = 20, family = "Arial monospaced for SAP"),
#     legend.text = element_text(size = 20, family = "Arial monospaced for SAP"),
#     legend.title = element_text(size = 20, family = "Arial monospaced for SAP"),
#     legend.position="none") 
# 
# 
# 
# paths <- do.call(rbind, global_location) %>% filter(between(time, 600, 600+2880)) %>% ## FILTER TO KEEP ONLY THE 24H OF INTEREST
#   left_join(rooms %>%
#               distinct(id_room, .keep_all = T) %>%
#               select(id_room,room), by = c("location" = "id_room")) %>%
#   mutate(room = ifelse(is.na(room), "Not here", room)) 
# 
# 
# ## FIX ISSUE WITH Y LABELS OF DIFF LENGTH
# max_n <- max(nchar(unique(paths$room)))
# paths <- paths %>%
#   mutate(room = str_pad(room ,max_n, side = "right")) 
# 
# not_here_long <- as.character(unique(paths[grep('Not here', paths$room), 'room']))
# ## FACTOR TO HAVE Not here down YAXIS
# paths <- paths %>% 
#   mutate(room = factor(room, levels = c(not_here_long , setdiff(stringr::str_sort(unique(paths$room), numeric=T), not_here_long))))
# 
# time_breaks <- seq(as.POSIXct(begin_date) + 600 * 30 , as.POSIXct(begin_date) + (600 + 2880)* 30, by = 480*30) # Breaks every 4 hours
# time_labels <- format(time_breaks, "%m/%d %H:%M")
# start_time <- as.POSIXct(begin_date + 600*30)
# end_time <- start_time + (max(time_breaks) - min(time_breaks))
# 
# 
# save_individual_path <- function(ind) {
#   ind_cat <- ifelse(!is.na(admission[admission$id == ind, "cat"]), admission[admission$id == ind, "cat"], "patient")
#   ind_type <- case_when(ind %in% id_medical ~ 'Medical',
#                         ind %in% id_paramedical ~ 'Paramedical',
#                         ind %in% id_patient ~ 'Patient')
# 
#   title <-paste0('Individual trajectory over time - ', ind, ' - ', ind_type, ' - ', ind_cat) 
#   p <- ggplot(paths %>% filter(id == ind), aes(x = time * 30 + begin_date, y = room, colour = ind_type)) +
#     geom_path(aes(group = id)) +  # geom_path -> connected lines
#     geom_point(aes(shape = id)) +  # geom_point -> points
#     labs(title = title, x = "Time", y = "") +
#     theme_bw() +
#     scale_colour_manual(values = pal) +
#     scale_x_continuous(breaks = time_breaks, labels = time_labels) +
#     theme(
#     plot.title = element_text(size = 25, hjust = 0.5, family = "Arial monospaced for SAP"), #use extrafont package if the font is not installed locally
#     axis.text = element_text(size = 20, family = "Arial monospaced for SAP"),
#     axis.title = element_text(size = 20, family = "Arial monospaced for SAP"),
#     legend.text = element_text(size = 20, family = "Arial monospaced for SAP"),
#     legend.title = element_text(size = 20, family = "Arial monospaced for SAP"),
#     legend.position="none") 
#     
#   # filename
#   file_name <- file.path(ind_paths_path, paste0(ind, "_", ind_cat, "_", ind_type, "_fig-traj", ".png"))
#   ggsave(file = file_name, plot = p, height = 6, width = 30, units = "in")
# }
# 
# #map -> apply function for each individual
# invisible(map(id_interacting, save_individual_path))
```


## CUMULATIVE NUMBER OF INTERACTION OVER TIME
```{r}
p_number_int <- do.call(rbind, global_interaction) %>%
  mutate(type_int = paste0(from_status, "-", to_status)) %>%
  mutate(type_int = ifelse(type_int == "PA-PE", "PE-PA", type_int)) %>%
  filter(type_int != "PA-PA") %>%
  #filter(between(time,600, 600 + 24*60*2)) %>%
  group_by(time, type_int) %>%
  summarise(n = n()) %>%
  ggplot(aes(x=begin_date + time*30, y=n, color = type_int))+
    geom_line(linewidth = 0.3) +
    annotate("rect", xmin = as.POSIXct("2020-05-06 12:00:00"), xmax = as.POSIXct("2020-05-07 12:00:00"), ymin = -Inf, ymax = Inf, alpha = 0.3, fill = "darkgrey") +  
    #annotate("rect", xmin = as.POSIXct("2020-05-06 22:00:00"), xmax = as.POSIXct("2020-05-07 06:00:00"), ymin = -Inf, ymax = Inf, alpha = 0.2, fill = "darkgrey") +
  
    theme_bw() +
    #theme(axis.text.x = element_text(angle = 35, hjust = 1)) +
    labs(x = "Time", y = "Number of interactions", color = "Type of interaction") +
    # labs(title = "Number of interaction over time") +
    scale_color_manual(values = c("PE-PA" = "darkorange", "PE-PE" = "orchid"), 
                       labels = c("PE-PA" = "Patient - HCW", 
                                  "PE-PE" = "HCW - HCW")) +
    theme(legend.position="top")

print(p_number_int)
ggsave(file = file.path(fig_path, 'number-int-icu-rp.png'), plot = p_number_int, height = 3, width = 14)
```


```{r}
## TRUNCATE TO KEEP ONLY 24H (24/05/06 12:00 TO 24/05/07 12:00)
end_date - begin_date ##end of last interaction
new_begin_date <- begin_date + (5*60*60) ## OFFSET TO START THE DAY AT 12AM
new_end_date <- new_begin_date + (24*60*60)
print(new_end_date - new_begin_date)
t_begin <- 5*60*2 ## OFFSET t
t_end <- (t_begin + 24*60*2) - 1

# load(file.path(loc_nodscov2_path,"dev-location-nodscov2.RData")) ##overwrite admission

# global_location_bis <- global_location


test_loc <- do.call(rbind, global_location) %>%
  # filter(between(time, 600, 600+2880)) %>%
  left_join(admission %>% select(id, cat), by = join_by(id)) %>% 
  left_join(rooms %>% distinct(id_room, .keep_all = T) %>% select(id_room, room), by = c("location" = "id_room")) %>%
  mutate(type = ifelse(id %in% id_medical , "MEDICAL", NA)) %>%
  mutate(type = ifelse(id %in% id_paramedical , "PARAMEDICAL", type)) %>%
  mutate(type = ifelse(id %in% id_patient , "PATIENT", type)) %>%
  group_by(id, cat, location, room, type) %>%
  summarise(
    sum_room = n() * 30,
    n = n(),
    .groups = 'drop'
  )

test_loc$room <- factor(test_loc$room, levels = c("Corridor", "Office", "Nursing station", "Medical resting room", "Paramedical resting room"))

# Boxplot & jittered points (Restroom & Corridor)
test_loc %>% filter(location %in% c(19,20,21,22,23,24)) %>%
  ggplot( aes(x=type, y=sum_room/3600, fill=type)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    ggh4x::facet_grid2(cols = vars(room), scales = "free_y", independent  ="y") +
    theme_bw() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    #ggtitle("Cumulative time spent in restroom or corridor by category of HCW") +
    xlab("") +
    ylab("Cumulative time (h)")

# Violin plot (Restroom & Corridor)    
test_loc %>% filter(location %in% c(19,20,21,22,23,24)) %>%
  ggplot( aes(x=type, y=sum_room/3600, fill=type)) +
    geom_violin() +
    geom_boxplot(width=.1) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    ggh4x::facet_grid2(cols = vars(room), scales = "free_y", independent  ="y") +
    theme_bw() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    #ggtitle("Cumulative time spent in restroom or corridor by category of HCW") +
    xlab("") +
    ylab("Cumulative time (h)")
    
# Violin plot (Restroom)
test_loc %>% filter(room == "Medical Restroom" | room == "Paramedical Restroom") %>%
  ggplot( aes(x=type, y=sum_room/3600, fill=type)) +
    geom_violin() +
    geom_boxplot(width=.1) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_bw() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    #ggtitle("Cumulative time spent in Restrooms by category of HCW") +
    xlab("") +
    ylab("Cumulative time (h)")
```

## ORDERED CUMULATIVE TIME SPENT IN ROOMS
```{r}
pal = c('MEDICAL' = "#5CD6D6", 'PARAMEDICAL' = "#A9B9E8", 'PATIENT' = "#FFA766", 'ROOM' = "#666699")
pal = c('MEDICAL' = "#5CD6D6BF", 'PARAMEDICAL' = "#A9B9E8BF", 'PATIENT' = "#FFA766BF", 'ROOM' = "#666699BF") #ALPHA = 0.75


## Cumulative time in patients rooms
patients_room <- test_loc %>% filter(location %in% id_room_patient) %>%
  group_by(id, .drop = "group") %>% 
  summarise(sum_patient = sum(sum_room)) %>%
  mutate(sum_room = sum_patient) %>%
  mutate(room = "Patients Rooms") %>% 
  left_join(test_loc %>% distinct(id, .keep_all = T) %>% select(id,type), by = join_by("id")) %>%
  select(id, sum_room, room, type)

other_room <- test_loc %>% filter(!location %in% id_room_patient) %>% filter(!is.na(room)) %>%
  select(id, sum_room, room, type)

total_room <- bind_rows(other_room, patients_room)
total_room$room <- factor(total_room$room, levels = c("Corridor", "Patients Rooms",  "Nursing station", "Office", "Paramedical Restroom", "Medical Restroom"))

p_cumulative_loc <- total_room %>%
  ggplot( aes(x=type, y=sum_room/3600, fill=type)) +
    geom_boxplot() +
    # scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    scale_fill_manual(values = pal) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    ggh4x::facet_grid2(cols = vars(room), scales = "free_y", independent  ="y") +
    
    theme_bw() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11,hjust = 0.5),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    # labs(title = "Cumulative time spent in rooms") +
    labs(x = "", y = "Cumulative time (h)")
    

print(p_cumulative_loc)
ggsave(file = file.path(fig_path, paste0("cumulative-time-rooms", ".png")), plot = p_cumulative_loc, height = 5, width = 12)
```

```{r IDS interactings}
## IDS INTERACTING
id_interacting <- do.call(rbind, global_interaction) %>%
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>% distinct(individual) %>% pull()
id_total <- admission %>% distinct(id) %>% pull()
id_not_interacting <- setdiff(id_total, id_interacting)

admission %>% distinct(cat) %>% pull()
cat_paramedical <- c("nurse", "student nurse", "aux nurse")
cat_medical <- c("physician", "ext physician", "reeducation staff", "other")
## IDS BY CATEGORY
id_paramedical <- admission %>% filter(id %in% id_interacting & cat %in% cat_paramedical) %>% pull(id)
id_medical <- admission %>% filter(id %in% id_interacting & cat %in% cat_medical) %>% pull(id)
id_hcw <- admission %>% filter(id %in% id_interacting & status == "PE") %>% pull(id)
id_patient <- admission %>% filter(id %in% id_interacting & status == "PA") %>% pull(id)

id_room_patient <- rooms %>% 
  filter(id %in% (admission %>% filter(status == "PA") %>% pull(id))) %>%
  distinct(id_room) %>%
  pull()
```

## NUMBER OF INDIVIDUAL BEFORE/AFTER TRUNCATION
```{r}
load(file.path(nodscov2_path, "admission_ctc_nodscov2.RData"))
Encoding(admission$hospital) <- 'latin1'
admission <- admission %>%
  ## Remove visitors/admin/logistics/investigators
  filter(ward == "Reanimation") %>% 
  filter(hospital == "APHP - RAYMOND POINCARÉ")

## CATEGORY GROUPING INTO TYPE
cat_other <- c('logistic', 'visitor', 'investigation', 'administration')
cat_paramedical <- c("nurse", "student nurse", "aux nurse")
cat_medical <- c("physician", "ext physician", "reeducation staff", "other")

## BEFORE REMOVING INDIVIDUALS WHO ARE NOT HCW/PATIENTS
adm_raw <- admission %>%
  filter(ward == "Reanimation" ) %>%
  filter(hospital == "APHP - RAYMOND POINCARÉ") %>%
  mutate(cat = ifelse(is.na(cat), "patient", cat)) %>%
  mutate(Type = case_when(
    cat %in% cat_paramedical ~ 'Paramedical',
    cat %in% cat_medical ~ 'Medical',
    cat == 'patient' ~ 'Patient',
    .default = 'Other'
  )) %>% 
  group_by(hospital, cat, Type) %>%
  summarise(n = n(), .groups = "drop")
adm_raw$Type <- factor(adm_raw$Type, levels = c('Paramedical', 'Medical', 'Patient', 'Other'))
adm_raw <- adm_raw %>%
  arrange(Type, desc(n))
adm_raw$cat <- factor(adm_raw$cat, levels = adm_raw$cat)


## AFTER 36h->24h truncation + removing ids not interacting
t_begin <- 5*60*2 ## OFFSET t
t_end <- (t_begin + 24*60*2) - 1

# TRUNCATED INFO EXTRACTED FROM TOTAL STUDY (KEEP 24HOURS OF THE 36HOURS)
truncated_interaction <- global_interaction[(u <- seq_along(global_interaction)) %in% t_begin:(t_end)]

id_interacting <- do.call(rbind, truncated_interaction) %>%
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>% distinct(individual) %>% pull()

adm_trunc <- admission %>%
  filter(id %in% id_interacting) %>%
  filter(ward == "Reanimation" ) %>%
  filter(hospital == "APHP - RAYMOND POINCARÉ") %>%
  mutate(cat = ifelse(is.na(cat), "patient", cat)) %>%
  mutate(Type = case_when(
    cat %in% cat_paramedical ~ 'Paramedical',
    cat %in% cat_medical ~ 'Medical',
    cat == 'patient' ~ 'Patient',
    .default = 'Other'
  )) %>% 
  group_by(hospital, cat, Type) %>%
  summarise(n = n(), .groups = "drop")
adm_trunc$Type <- factor(adm_trunc$Type, levels = c('Paramedical', 'Medical', 'Patient', 'Other'))
adm_trunc <- adm_trunc %>%
  arrange(Type, desc(n))
adm_trunc$cat <- factor(adm_trunc$cat, levels = adm_trunc$cat)


## PLOTS 
pal = c('Medical' = "#5CD6D6", 'Paramedical' = "#A9B9E8", 'Patient' = "#FFA766", 'Other' = "#666699")

p_n_RP_1 <- ggplot(adm_raw, aes(x = cat, y = n, fill = Type)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = pal) +
  labs(title = "" ,x = "", y = "Number of individuals") +
  #labs(title = "APHP - RAYMOND POINCARÉ" ,x = "Categories", y = "Number of individuals") +
  theme(
    axis.text.x = element_text(angle = 35, hjust = 1)) +
  geom_text(aes(label=n), vjust=-0.25, size=3) +
  theme(legend.position="none")

p_n_RP_2 <- ggplot(adm_trunc, aes(x = cat, y = n, fill = Type)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = pal) +
  labs(title = "" ,x = "", y = "") +
  #labs(title = "APHP - RAYMOND POINCARÉ" ,x = "Categories", y = "Number of individuals") +
  theme(
    axis.text.x = element_text(angle = 35, hjust = 1)) +
  geom_text(aes(label=n), vjust=-0.25, size=3)

p_n_RP <- ggarrange(p_n_RP_1, p_n_RP_2, labels = c("A", "B"), nrow = 1, ncol = 2, common.legend = TRUE, legend="right")

print(p_n_RP)
ggsave(filename = file.path(wd, '..', '..', 'out', 'fig', 'RP-number-individual.png'), plot = p_n_RP, height = 4, width = 8)


### RETRIEVING FILTERED ADMISSION
admission <- admission %>%
  ## Remove visitors/admin/logistics/investigators
  filter(ward == "Reanimation") %>% 
  filter(hospital == "APHP - RAYMOND POINCARÉ") %>%
  filter(!(cat %in% c("administration",
                  "investigation",
                  "logistic",
                  "visitor")))
```

## TEMP - Tracking individual
```{r}
pal = c('Medical' = "#5CD6D6", 'Paramedical' = "#A9B9E8", 'Patient' = "#FFA766", 'Room' = "#666699")
paths <- do.call(rbind, global_location) %>% filter(between(time, 600, 600+2880)) %>% ## FILTER TO KEEP ONLY THE 24H OF INTEREST
  left_join(rooms %>%
              distinct(id_room, .keep_all = T) %>%
              select(id_room,room), by = c("location" = "id_room")) %>%
  mutate(room = ifelse(is.na(room), "Not here", room)) 


## FIX ISSUE WITH Y LABELS OF DIFF LENGTH
max_n <- max(nchar(unique(paths$room)))
paths <- paths %>%
  mutate(room = str_pad(room ,max_n, side = "right")) 

not_here_long <- as.character(unique(paths[grep('Not here', paths$room), 'room']))
## FACTOR TO HAVE Not here down YAXIS
paths <- paths %>% 
  mutate(room = factor(room, levels = c(not_here_long , setdiff(stringr::str_sort(unique(paths$room), numeric=T), not_here_long))))

time_breaks <- seq(as.POSIXct(begin_date) + 600 * 30 , as.POSIXct(begin_date) + (600 + 2880)* 30, by = 480*30) # Breaks every 4 hours
time_labels <- format(time_breaks, "%m/%d %H:%M")
start_time <- as.POSIXct(begin_date + 600*30)
end_time <- start_time + (max(time_breaks) - min(time_breaks))


save_individual_path <- function(ind) {
  ind_cat <- ifelse(!is.na(admission[admission$id == ind, "cat"]), admission[admission$id == ind, "cat"], "patient")
  ind_type <- case_when(ind %in% id_medical ~ 'Medical',
                        ind %in% id_paramedical ~ 'Paramedical',
                        ind %in% id_patient ~ 'Patient')

  title <-paste0('Individual trajectory over time - ', ind, ' - ', ind_type, ' - ', ind_cat) 
  p <- ggplot(paths %>% filter(id == ind), aes(x = time * 30 + begin_date, y = room, colour = ind_type)) +
    geom_path(aes(group = id)) +  # geom_path -> connected lines
    geom_point(aes(shape = id)) +  # geom_point -> points
    labs(title = title, x = "Time", y = "") +
    theme_bw() +
    scale_colour_manual(values = pal) +
    scale_x_continuous(breaks = time_breaks, labels = time_labels) +
    theme(
    plot.title = element_text(size = 25, hjust = 0.5, family = "Arial monospaced for SAP"), #use extrafont package if the font is not installed locally
    axis.text = element_text(size = 20, family = "Arial monospaced for SAP"),
    axis.title = element_text(size = 20, family = "Arial monospaced for SAP"),
    legend.text = element_text(size = 20, family = "Arial monospaced for SAP"),
    legend.title = element_text(size = 20, family = "Arial monospaced for SAP"),
    legend.position="none") 
    
  # filename
  file_name <- file.path(ind_paths_path, paste0(ind, "_", ind_cat, "_", ind_type, "_fig-traj", ".png"))
  ggsave(file = file_name, plot = p, height = 6, width = 30, units = "in")
}

#map -> apply function for each individual
invisible(map(id_interacting, save_individual_path))
```


```{r}
selected_individuals <- c('001-0023-L-L', '001-0042-B-S', '001-0035-F-S')
categories_individuals <- c('nurse', 'physician', 'patient')
type_individual <- c('Paramedical', 'Medical', 'Patient')
```


```{r}
title <- paste0(selected_individuals, ' - ', type_individual, ' - ', categories_individuals) 
p1 <- ggplot(paths %>% filter(id == selected_individuals[1]), aes(x = time * 30 + begin_date, y = room, colour = type_individual[1])) +
    geom_path(aes(group = id)) +  # geom_path -> connected lines
    geom_point(aes(shape = id)) +  # geom_point -> points
    labs(title = title[1], x = "Time", y = "") +
    theme_bw() +
    scale_colour_manual(values = pal) +
    scale_x_continuous(breaks = time_breaks, labels = time_labels) +
    theme(
      plot.title = element_text(size = 25, hjust = 0.5, family = "Arial monospaced for SAP"), #use extrafont package if the font is not installed locally
      axis.text.x = element_blank(),
      axis.title.x = element_blank(), 
      axis.text = element_text(size = 20, family = "Arial monospaced for SAP"),
      axis.title = element_text(size = 25, family = "Arial monospaced for SAP"),
      legend.text = element_text(size = 20, family = "Arial monospaced for SAP"),
      legend.title = element_text(size = 20, family = "Arial monospaced for SAP"),
      legend.position="none") 





p2 <- ggplot(paths %>% filter(id == selected_individuals[2]), aes(x = time * 30 + begin_date, y = room, colour = type_individual[2])) +
    geom_path(aes(group = id)) +  # geom_path -> connected lines
    geom_point(aes(shape = id)) +  # geom_point -> points
    labs(title = title[2], x = "Time", y = "") +
    theme_bw() +
    scale_colour_manual(values = pal) +
    scale_x_continuous(breaks = time_breaks, labels = time_labels) +
     theme(
      plot.title = element_text(size = 25, hjust = 0.5, family = "Arial monospaced for SAP"), #use extrafont package if the font is not installed locally
      axis.text.x = element_blank(),
      axis.title.x = element_blank(), 
      axis.text = element_text(size = 20, family = "Arial monospaced for SAP"),
      axis.title = element_text(size = 25, family = "Arial monospaced for SAP"),
      legend.text = element_text(size = 20, family = "Arial monospaced for SAP"),
      legend.title = element_text(size = 20, family = "Arial monospaced for SAP"),
      legend.position="none") 


p3 <- ggplot(paths %>% filter(id == selected_individuals[3]), aes(x = time * 30 + begin_date, y = room, colour = type_individual[3])) +
    geom_path(aes(group = id)) +  # geom_path -> connected lines
    geom_point(aes(shape = id)) +  # geom_point -> points
    labs(title = title[3], x = "Time", y = "") +
    theme_bw() +
    scale_colour_manual(values = pal) +
    scale_x_continuous(breaks = time_breaks, labels = time_labels) +
    theme(
      plot.title = element_text(size = 25, hjust = 0.5, family = "Arial monospaced for SAP"), #use extrafont package if the font is not installed locally
      axis.text = element_text(size = 20, family = "Arial monospaced for SAP"),
      axis.title = element_text(size = 25, family = "Arial monospaced for SAP"),
      legend.text = element_text(size = 20, family = "Arial monospaced for SAP"),
      legend.title = element_text(size = 20, family = "Arial monospaced for SAP"),
      legend.position="none") 

set_null_device(cairo_pdf)
p_trajectores <- cowplot::plot_grid(p1,p2,p3, labels = c("A ", "B ", "C "), nrow = 3, ncol = 1)


ggsave(filename = file.path(fig_path, 'fig-ind-trajectories.png'), plot = p_trajectores, height = 14, width = 28)

```




<!-- ################################# TEMPORARY - DOUBLE/TRIPLE ROOM INFERENCE ############################## -->

## TEMP: EXTRACTING DOUBLE/TRIPLE ROOMS
```{r}
wd <- getwd()
knitr::opts_chunk$set(root.dir = wd)
data_path <- file.path(wd,"..", "..", "data")
nodscov2_path <- file.path(data_path, "data-nodscov2") 
loc_nodscov2_path <- file.path(wd, "..", "..", "out", "loc-nodscov2")
fig_path <- file.path(loc_nodscov2_path,"..","fig")
ind_paths_path <- file.path(fig_path, "individual-paths")
load(file.path(loc_nodscov2_path,"dev-location-nodscov2.RData")) ##overwrite admission
## TRUNCATE TO KEEP ONLY 24H (24/05/06 12:00 TO 24/05/07 12:00)
end_date - begin_date ##end of last interaction
new_begin_date <- begin_date + (5*60*60) ## OFFSET TO START THE DAY AT 12AM
new_end_date <- new_begin_date + (24*60*60)
print(new_end_date - new_begin_date)
t_begin <- 5*60*2 ## OFFSET t
t_end <- (t_begin + 24*60*2) - 1




id_patient <- admission %>% filter(status == 'PA') %>% pull(id)
## IN RP ICU DURING THE STUDY -> ADDED BEDS, 2 DOUBLE ROOMS and 2 "TRIPLE ROOMS"
# equivalence id_patient <-> integer
# will give NA if not a patient -> excluded
# if < 2 patients -> will be skipped
name_to_index <- setNames(seq_along(id_patient), id_patient)

update_co_occurrence_matrix <- function(cluster, matrix, name_to_index) {
  if (length(cluster) > 1) {
    for (i in 1:(length(cluster) - 1)) {
      for (j in (i + 1):length(cluster)) {
        idx_i <- name_to_index[cluster[i]]
        idx_j <- name_to_index[cluster[j]]
        matrix[idx_i, idx_j] <- matrix[idx_i, idx_j] + 1
        matrix[idx_j, idx_i] <- matrix[idx_j, idx_i] + 1
      }
    }
  }
  return(matrix)
}

# initialization
co_occurrence_matrix <- matrix(0, nrow = length(id_patient), ncol = length(id_patient))
rownames(co_occurrence_matrix) <- id_patient
colnames(co_occurrence_matrix) <- id_patient

## for each time step -> count
for (t in clusters[(u <- seq_along(clusters)) %in% t_begin:(t_end)]) {
  for (cluster in t) {
    co_occurrence_matrix <- update_co_occurrence_matrix(cluster, co_occurrence_matrix, name_to_index)
  }
}
total_occurrences <- colSums(co_occurrence_matrix)

## Adjacency graph
graph <- graph.adjacency(co_occurrence_matrix,
                         weighted=T,
                         mode="undirected",
                         diag=FALSE)

plot.igraph(graph,
            vertex.label=V(graph)$name,
            #edge.width=log10(E(graph)$weight),
            edge.label=E(graph)$weight,
            edge.label.cex=0.8,
            vertex.size=5,
            vertex.label.cex=0.8,
            layout=layout_with_kk) 

tkplot(graph,
          vertex.label=V(graph)$name,
            #edge.width=log10(E(graph)$weight),
            edge.label=E(graph)$weight,
            edge.label.cex=0.8,
            vertex.size=5,
            vertex.label.cex=0.8,
            layout=layout_with_kk)
```



```{r}
## MATRIX TO DF (filtering to remove duplicates, matrix is symmetrical..., and order it by highest count)
co_occurrence_df <- as.data.frame(as.table(co_occurrence_matrix))
co_occurrence_df <- co_occurrence_df[co_occurrence_df$Var1 != co_occurrence_df$Var2, ]
co_occurrence_df <- co_occurrence_df[!duplicated(t(apply(co_occurrence_df, 1, sort))), ]
co_occurrence_df <- co_occurrence_df[order(-co_occurrence_df$Freq), ]


## function to find double room
find_double_rooms <- function(df, n_double) {
  selected_clusters <- character()
  double_rooms <- list()

  # Select double rooms
  for (i in 1:n_double) {
    pair <- df[!df$Var1 %in% selected_clusters & !df$Var2 %in% selected_clusters, ][1, ]
    if (nrow(pair) > 0) {
      double_rooms[[i]] <- c(as.character(pair$Var1), as.character(pair$Var2))
      selected_clusters <- c(selected_clusters, as.character(pair$Var1), as.character(pair$Var2))
    }
  }

  return(double_rooms)
}

double_rooms <- find_double_rooms(co_occurrence_df, n_double = 2)
print(double_rooms)
```


## TRIPLE ROOMS (NOT WORKING ATM)
```{r}
# library(gtools)
# triplets <- as.data.frame(combinations(n = 18, r = 3, v = id_patient)) %>% mutate(Freq = 0)
# 
# ## Freq each triplet in a cluster
# for (t in clusters) {
#   for (cluster in t) {
#     if (length(cluster) > 2){
#       for (j in 1:nrow(triplets)) {
#         triplet <- triplets[j, ]
#         if (all(triplet %in% cluster)) {
#           triplets[j,]$Freq <- triplets[j,]$Freq + 1
#         }
#       }
#     }
#   }
# }
```

<!-- ################################# GARBAGE ############################## -->

```{r}
# ## check which indivuals have > 3 "shifts"
# sup_3_shifts <- shifts %>% 
#   group_by(individual) %>% 
#   summarise(n_shifts = n()) %>% 
#   filter(n_shifts > 3) %>%
#   left_join(admission %>% select(id,cat), by = c("individual" = "id")) %>%
#   select(individual, cat, n_shifts)
```

## SHIFTS VS INTERACTION
```{r}
# df_long <- data %>%
#   mutate(date_posix_end = date_posix_first + length) %>% 
#   pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
#   arrange(individual, date_posix_first)
# 
# calculate_actual_interaction_time <- function(df) {
#   if(nrow(df) == 0) return(0)
#   
#   df <- df %>% arrange(date_posix_first)
#   total_time <- 0
#   current_start <- df$date_posix_first[1]
#   current_end <- df$date_posix_end[1]
#   
#   for(i in 2:nrow(df)) {
#     if(df$date_posix_first[i] <= current_end) {
#       current_end <- max(current_end, df$date_posix_end[i])
#     } else {
#       total_time <- total_time + as.numeric(difftime(current_end, current_start, units = "hours"))
#       current_start <- df$date_posix_first[i]
#       current_end <- df$date_posix_end[i]
#     }
#   }
#   total_time <- total_time + as.numeric(difftime(current_end, current_start, units = "hours"))
#   return(total_time)
# }
# 
# len_int <- df_long %>%
#   group_by(individual) %>%
#   summarise(total_int = calculate_actual_interaction_time(cur_data()))
# 
# len_shifts <- shifts %>%
#   group_by(individual) %>%
#   summarise(total_shift = sum(shift_length))
# 
# len_tot <- left_join(len_shifts, len_int, by = join_by(individual))  %>%
#   mutate(len_diff = total_shift - total_int) %>%
#   left_join(admission %>% select(id,cat), by = c("individual" = "id"))
# 
# 
# len_tot %>% filter(total_int > total_shift) 
```