---
title: "localization-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-05-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(lubridate)
library(igraph)
library(tidyr)
library(viridis)
library(purrr)
library(stringr)
```

```{r Paths setup}
wd <- getwd()
knitr::opts_chunk$set(root.dir = wd)
data_path <- file.path(wd,"..", "..", "data")
nodscov2_path <- file.path(data_path, "data-nodscov2") 
loc_nodscov2_path <- file.path(wd, "..", "..", "out", "loc-nodscov2")
fig_path <- file.path(loc_nodscov2_path,"..","fig")
ind_paths_path <- file.path(fig_path, "individual-paths")
if (!dir.exists(ind_paths_path)) {
  dir.create(ind_paths_path, recursive = TRUE)
}
if (!dir.exists(loc_nodscov2_path)) {
  dir.create(loc_nodscov2_path, recursive = TRUE)
}
if (!dir.exists(fig_path)) {
  dir.create(fig_path, recursive = TRUE)
}
if (!dir.exists(nodscov2_path)) {
  dir.create(nodscov2_path, recursive = TRUE)
}
```

### WIP 

## NodsCov2 data (not shared)
```{r Load data}
load(file.path(nodscov2_path, "admission_ctc_nodscov2.RData"))
load(file.path(nodscov2_path, "list_ward.RData"))
# load("Y:/ogaufres/pacri-non-sync/data/data-nodscov2/admission_ctc_nodscov2.RData")
# load("Y:/ogaufres/pacri-non-sync/data/data-nodscov2/list_ward.RData")
```


## FIXING ENCODING
```{r Fixing encoding}
Encoding(admission$hospital) <- 'latin1'
```


## Raymond Poincaré reanimation ward
```{r Select ward of interest}
data <- list_ward[["Raymond_Poincare-Reanimation-20200506-20200507"]]
admission <- admission %>%
  ## Remove visitors/admin/logistics/investigators
  filter(ward == "Reanimation") %>% 
  filter(hospital == "APHP - RAYMOND POINCARÉ") %>%
  filter(!(cat %in% c("administration",
                  "investigation",
                  "logistic",
                  "visitor")))

## FILTER INTERACTIONS TO KEEP ONLY HCW AND PATIENTS
data <- data %>%
  filter(from %in% admission$id & to %in% admission$id)
  
## ADD INFO OF THE STATUS FOR INDIVIDUALS
data <- left_join(data, admission %>% select(id, status), by = c("from" = "id")) %>%
    rename(from_status = status) %>%
    left_join(admission %>% select(id, status), by = c("to" = "id")) %>%
    rename(to_status = status)

data <- unique(data)
```


## SUBDIVIDING EVERY 30s
```{r Subdividing interactions}
begin_date <- as.POSIXct(min(data$date_posix_first))
end_date <- as.POSIXct(max(data$date_posix_first + data$length))
time_spent <- difftime(end_date, begin_date, units = "mins")  

n_subdivisions <- floor(as.numeric(time_spent) * 2) ## Time spent * hours * minutes * 2 (number of time subdivisions)
## floor because of the manner we extract the interactions (=30sec, i.e. at  the end, interactions are <30sec -> we dont take these)


## t = 1 -> [0,30[sec
global_interaction <- lapply(1:n_subdivisions, function(t){
  interactions_t <- data %>%
    filter(date_posix_first <= (begin_date + (t-1)*30) & (date_posix_first + length > begin_date + (t)*30) ) %>%
    mutate(time = t) %>%
    select(from, to, time, from_status, to_status)
  
  return(interactions_t)
})

```


## ROOMS
```{r Rooms}
rooms <- admission %>%
  filter(status == "PA") %>%
  distinct(id) %>%
  mutate(room = as.factor(row_number())) %>%
  mutate(id_room = as.factor(row_number())) %>%
  mutate(volume = 20* 2.2) %>%  #18 square meters * 2.2 height
  select(id_room,room, volume,  id)

rooms <- rooms %>%
  bind_rows(data.frame(room = "Medical Restroom", id = "R-M-PE", volume = 30 * 2.2 ,  id_room = as.factor(nrow(rooms) + 1))) %>%
  bind_rows(data.frame(room = "Paramedical Restroom", id = "R-PM-PE", volume =  40 * 2.2 , id_room = as.factor(nrow(rooms) + 2))) %>%
  bind_rows(data.frame(room = "Nursing station", id = "PM-PE", volume = 20 * 2.2 , id_room = as.factor(nrow(rooms) + 3))) %>%
  bind_rows(data.frame(room = "Office", id = "M-PE", volume = 20 * 2.2 , id_room = as.factor(nrow(rooms) + 4))) %>%
  bind_rows(data.frame(room = "Corridor", id = "ALL", volume = 200 * 2.2 , id_room = as.factor(nrow(rooms) + 5)))

### DOUBLE ROOMS
## "001-0038-B-S" and = "001-0039-B-F" are in the same room
## "001-0127-B-A" and "001-0128-Z-K" are in the same room
rooms <- rooms %>% mutate(room = ifelse(id == "001-0038-B-S", rooms[rooms$id == "001-0039-B-F", "room"], room),
                          volume = ifelse(id == "001-0038-B-S", 30 * 2.2, volume),
                          id_room = ifelse(id == "001-0038-B-S", rooms[rooms$id == "001-0039-B-F", "id_room"], id_room))

rooms <- rooms %>% mutate(room = ifelse(id == "001-0128-Z-K", rooms[rooms$id == "001-0127-B-A", "room"], room),
                          volume = ifelse(id == "001-0128-Z-K", 30 * 2.2, volume),
                          id_room = ifelse(id == "001-0128-Z-K", rooms[rooms$id == "001-0127-B-A", "id_room"], id_room))

double_rooms <- list(c("001-0038-B-S", "001-0039-B-F"), c("001-0127-B-A", "001-0128-Z-K"))

id_room_patient <- rooms %>% 
  filter(id %in% (admission %>% filter(status == "PA") %>% pull(id))) %>%
  distinct(id_room) %>%
  pull()
```




## INTERACTION CLUSTERS FOR EACH TIME t
```{r Interaction clusters}
clusters <- lapply(global_interaction, function(df) {
  # df to non oriented graph based on interaction happening at time t
  graph <- graph_from_data_frame(df, directed = FALSE)
  # Extract connected component
  clusters <- components(graph)$membership
  # clusters to list (unique list of individual)
  clusters_list <- lapply(unique(clusters), function(i) {
    #for each cluster i, we extract the vertices/nodes of the graph -> individual names in each clusters 
    as.character(V(graph)[clusters == i]$name)
  })
  return(clusters_list)
})
```


## SHIFTS INFERENCE
```{r Shifts}
# Pivot -> get all int for each individual
df_long <- data %>%
  mutate(date_posix_end = date_posix_first + length) %>% 
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
  arrange(individual, date_posix_first)

# Time between 2 interactions for each individual (lag get the previous )
df_long <- df_long %>%
  group_by(individual) %>%
  mutate(test_filter = date_posix_first - lag(date_posix_end)) %>%
  filter(test_filter > 0 | is.na(test_filter)) %>%
  mutate(time_diff = difftime(date_posix_first, lag(date_posix_end), units = "mins"))


time_threshold <- 60*1.5

df_long <- df_long %>%
  mutate(new_shift = ifelse(is.na(time_diff) | time_diff > time_threshold, 1, 0)) %>%
  group_by(individual) %>%
  mutate(shift_id = cumsum(new_shift))

shifts <- df_long %>%
  group_by(individual, shift_id) %>%
  summarise(
    start_time = min(date_posix_first),
    end_time = max(date_posix_end),
    shift_length = as.numeric(difftime(max(date_posix_end), min(date_posix_first), units = "hours")),
    .groups = 'drop'
  ) %>%
  arrange(individual, shift_id) %>%
  left_join(admission %>% select(id,cat,status), by = c("individual" = "id")) %>%
  filter(status == "PE")

```


## CHECK INDIVIDUALS IN ADMISSION: HERE OR NOT HERE DURING THE STUDY?
```{r IDS interactings}
## IDS INTERACTING
id_interacting <- data %>%
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>% distinct(individual) %>% pull()
id_total <- admission %>% distinct(id) %>% pull()
id_not_interacting <- setdiff(id_total, id_interacting)

admission %>% distinct(cat) %>% pull()
cat_paramedical <- c("nurse", "student nurse", "aux nurse")
cat_medical <- c("physician", "ext physician", "reeducation staff", "other")
## IDS BY CATEGORY
id_paramedical <- admission %>% filter(id %in% id_interacting & cat %in% cat_paramedical) %>% pull(id)
id_medical <- admission %>% filter(id %in% id_interacting & cat %in% cat_medical) %>% pull(id)
id_hcw <- admission %>% filter(id %in% id_interacting & status == "PE") %>% pull(id)
id_patient <- admission %>% filter(id %in% id_interacting & status == "PA") %>% pull(id)
```



## Localization INFERENCE (FOR ALL INDIVIDUALS) - INTERACTIONS
```{r Loc for interactions}
############################################################
## ASSIGNING localization FOR THE INDIVIDUALS INTERACTING ##
############################################################

## Store info when there is more than one patient in clusters -> fix later
cluster_info_list <- list()
global_localization <- list()


global_localization <- lapply(1:n_subdivisions, function(t) {
  localization_t <- data.frame(id = id_interacting, localization = NA, time = t) ##only for individual that interacts
  # Interactions at time t
  interactions_t <- global_interaction[[t]] %>% mutate(localization = NA)
  clusters_t <- clusters[[t]]
  # For each clusters of individuals at time t
  lapply(clusters_t, function(cluster) {
    
    ###########################
    ## CLUSTER WITH PATIENTS ##
    ###########################
    # IF THERE IS NO PATIENTS
    NO_PATIENT <- length(unique(cluster[cluster %in% id_patient])) == 0
    # IF THERE IS ONLY ONE PATIENT IN THE CLUSTER
    ONE_PATIENT <- length(unique(cluster[cluster %in% id_patient])) == 1
    one_patient_room <- ifelse(ONE_PATIENT, rooms[rooms$id == cluster[cluster %in% id_patient], "id_room"], -2)
    ## IF IN DOUBLE ROOM (MUST BE ONLY THE TWO PATIENTS, NOT THE TWO PATIENT + ANOTHER PATIENT)
    IN_DOUBLE_ROOM_N1 <- !NO_PATIENT & all(cluster[cluster %in% id_patient] %in% double_rooms[[1]])
    IN_DOUBLE_ROOM_N2 <- !NO_PATIENT & all(cluster[cluster %in% id_patient] %in% double_rooms[[2]])
    # IF THERE IS MULTIPLE PATIENTS IN THE CLUSTER (AND NOT IN DOUBLE ROOM)
    MULTIPLE_PATIENT <- length(unique(cluster[cluster %in% id_patient])) > 1 & !(IN_DOUBLE_ROOM_N1 | IN_DOUBLE_ROOM_N2)
    
    ##############################
    ## CLUSTER WITHOUT PATIENTS ##
    ##############################
    NO_MEDICAL <- length(unique(cluster[cluster %in% id_medical])) == 0
    NO_PARAMEDICAL <- length(unique(cluster[cluster %in% id_paramedical])) == 0
    
    ONLY_PARAMEDICAL <- NO_PATIENT & NO_MEDICAL
    ONLY_MEDICAL <- NO_PATIENT & NO_PARAMEDICAL
    MEDICAL_AND_PARAMEDICAL <- NO_PATIENT & !NO_MEDICAL & !NO_PARAMEDICAL
    
    #####################
    ## TIME CONDITIONS ##
    #####################
    time_t <- begin_date + (t-1)*30
    DAY <- between(hour(time_t), 7, 21) 
    NIGHT <- between(hour(time_t), 22, 24) | between(hour(time_t), 0, 6)
    
    #################################
    ## Localization OF THE CLUSTER ##
    #################################
    cluster_localization <- case_when(
      MULTIPLE_PATIENT ~ rooms[rooms$id == "ALL", "id_room"],
      IN_DOUBLE_ROOM_N1 ~ unique(rooms[rooms$id == double_rooms[[1]][[1]], "id_room"]),
      IN_DOUBLE_ROOM_N2 ~ unique(rooms[rooms$id == double_rooms[[2]][[1]], "id_room"]),
      ONE_PATIENT ~ one_patient_room,
      ONLY_MEDICAL ~ rooms[rooms$id == "M-PE", "id_room"], ## ONLY MEDICAL INTERACTING -> OFFICE
      ONLY_PARAMEDICAL ~ rooms[rooms$id == "PM-PE", "id_room"], ## ONLY PARAMEDICAL INTERACTING -> NURSING STATION
      MEDICAL_AND_PARAMEDICAL ~ rooms[rooms$id == "PM-PE", "id_room"], ## ONLY MED AND PARAMED -> NURSING STATION
      .default = -3
    )
    ## Assign the localization for individuals inside the cluster 
    # <<- to edit localization_t defined outside clusters_t's lapply scope
    interactions_t$localization <<- ifelse(interactions_t$from %in% cluster, cluster_localization, interactions_t$localization) ## if from is in the cluster, to will be also
    localization_t$localization <<- ifelse(localization_t$id %in% cluster, cluster_localization, localization_t$localization)
    ### TEMP
    
    ## MULTIPLE PATIENTS IN THE CLUSTER --> TEMPORARY, FIXED LATER
    if (MULTIPLE_PATIENT) {
      cluster_possible_localization <- rooms[rooms$id %in% cluster[cluster %in% id_patient], "id_room"]
      cluster_info <- data.frame(time = t, Patients = cluster[cluster %in% id_patient], cluster = toString(cluster))
      cluster_info_list <<- append(cluster_info_list, list(cluster_info))
    }
  })
  
  ## ADD THE LOCALIZATION IN GLOBAL_INTERACTION (we could have added the cluster id but its useless for now)
  global_interaction[[t]] <<- interactions_t
  return(localization_t)
})
```


## SMOOTHING (SUCCESSIVE INTERACTION IN THE SAME ROOM WITH <5min GAP)
```{r}
smoothing_localization <- function(global_interaction, global_localization) {
  interactions <- do.call(rbind, global_interaction)
  localizations <- do.call(rbind, global_localization)
  smoothed_loc <- data.frame()
  
  interactions_long <- interactions %>%
    pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
    arrange(individual, time)

  for (ind in unique(interactions_long$individual)) {
    ind_interactions <- interactions_long %>% filter(individual == ind) %>% arrange(time)
    ind_localizations <- localizations %>% filter(id == ind)
    
    if (nrow(ind_interactions) > 2) {
      for (i in 2:nrow(ind_interactions)) {
        time_gap <- ind_interactions$time[i] - ind_interactions$time[i - 1]
        
        if (time_gap == 2){
          previous_loc <- ind_localizations %>% filter(time == ind_interactions$time[i - 1]) %>% pull(localization)
          current_loc <- ind_localizations %>% filter(time == ind_interactions$time[i]) %>% pull(localization)
          if (previous_loc == current_loc & current_loc %in% id_room_patient){
            ind_localizations[ind_localizations$time == ind_interactions$time[i] - 1, "localization"] <- current_loc
            }
        }
        if (time_gap > 2 & time_gap <= 10) {
          previous_loc <- ind_localizations %>% filter(time == ind_interactions$time[i - 1]) %>% pull(localization)
          current_loc <- ind_localizations %>% filter(time == ind_interactions$time[i]) %>% pull(localization)
          if (previous_loc == current_loc & current_loc %in% id_room_patient){
            for (t in (ind_interactions$time[i - 1] + 1):(ind_interactions$time[i] - 1)) {
            ind_localizations[ind_localizations$time == t, "localization"] <- current_loc
            }
          }
        }
      }
    }
    smoothed_loc <- rbind(smoothed_loc, ind_localizations)
  }
  smoothed_loc <- smoothed_loc %>% arrange(id, time)
  return(smoothed_loc)
}


smoothed_global_interaction <- smoothing_localization(global_interaction, global_localization)

## DF TO LIST
global_localization <- lapply(1:n_subdivisions, function(t) {
  localization_t <- smoothed_global_interaction %>% filter(time == t) %>% arrange(id)
  return(localization_t)
})

rm(smoothed_global_interaction)
```

## SMOOTHING (ADDING CORRIDOR BEFORE AN INTERACTION)
```{r}
smoothing_corridor <- function(global_interaction, global_localization) {
  interactions <- do.call(rbind, global_interaction)
  localizations <- do.call(rbind, global_localization)
  smoothed_corridor <- data.frame()
  
  interactions_long <- interactions %>%
    pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
    arrange(individual, time)
  id_corridor <- rooms[rooms$room == "Corridor", "id_room"]

  for (ind in unique(interactions_long$individual)) {
    ind_interactions <- interactions_long %>% filter(individual == ind) %>% arrange(time)
    ind_localizations <- localizations %>% filter(id == ind)
    
    if (nrow(ind_interactions) > 2) {
      for (i in 2:nrow(ind_interactions)) {
        time_gap <- ind_interactions$time[i] - ind_interactions$time[i - 1]
        
        if (time_gap == 2){
          ind_localizations[ind_localizations$time == ind_interactions$time[i] - 1, "localization"] <- id_corridor
        }
        if (time_gap > 2) {
          ind_localizations[ind_localizations$time == ind_interactions$time[i - 1] + 1, "localization"] <- id_corridor
          ind_localizations[ind_localizations$time == ind_interactions$time[i] - 1, "localization"] <- id_corridor
        }
      }
    }
    smoothed_corridor <- rbind(smoothed_corridor, ind_localizations)
  }
  smoothed_corridor <- smoothed_corridor %>% arrange(id, time)
  return(smoothed_corridor)
}

smoothed_corridor_global_interaction <- smoothing_corridor(global_interaction, global_localization)

## DF TO LIST
global_localization <- lapply(1:n_subdivisions, function(t) {
  localization_t <- smoothed_corridor_global_interaction %>% filter(time == t) %>% arrange(id)
  return(localization_t)
})

rm(smoothed_corridor_global_interaction)
```


## FILL LOCALIZATION FOR PATIENTS
```{r}
global_localization <- lapply(1:n_subdivisions, function(t) {
  localization_t <- global_localization[[t]]
  for (ind in id_patient) {
    if (is.na(localization_t[localization_t$id == ind, "localization"])) {
      localization_t[localization_t$id == ind, "localization"] <- rooms[rooms$id == ind, "id_room"]
    }
  }
  
  return(localization_t)
})
```




## localization INFERENCE - NO INTERACTION (PATIENTS STAY IN THEIR ROOM, SO WE ONLY CHECK/FILL HCW)
```{r Loc t1}
################################################################
## ASSIGNING localization FOR THE INDIVIDUALS NOT INTERACTING ##
################################################################

############
## t == 1 ##
############

# FIRST SUBDIVISION 
## RULES TO BE DEFINED
## IF NOT INTERACTING AT t == 1, assign localization to -1 (NOT HERE)
global_localization[[1]]$localization <- ifelse(is.na(global_localization[[1]]$localization), -1, global_localization[[1]]$localization )
```


```{r Loc t2}
############
## t == 2 ##
############

## SECOND SUBDIVISION
localization_t1 <- global_localization[[1]]
localization_t2 <- global_localization[[2]]

id_not_interacting_t2 <- localization_t2 %>% filter(is.na(localization)) %>% pull(id)
id_room_t1 <- localization_t1 %>% filter(localization %in% id_room_patient) %>% pull(id)
id_corridor_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
id_medical_restroom_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "R-M-PE", "id_room"]) %>% pull(id)
id_paramedical_restroom_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "R-PM-PE", "id_room"]) %>% pull(id)
id_nursing_station_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "PM-PE", "id_room"]) %>% pull(id)
id_office_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "M-PE", "id_room"]) %>% pull(id)
id_not_here_t1 <- localization_t1 %>% filter(localization == -1 ) %>% pull(id)


for (individual in id_not_interacting_t2){
  if (individual %in% id_paramedical){
    ind_loc_t2 <- case_when(
      individual %in% id_room_t1 ~ rooms[rooms$id == "ALL", "id_room"],
      individual %in% id_nursing_station_t1 ~ rooms[rooms$id == "ALL", "id_room"],
      individual %in% id_paramedical_restroom_t1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
      individual %in% id_corridor_t1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
      individual %in% id_not_here_t1 ~ -1,
      .default = -2 #"ERROR - WRONG LOC MED t2"
    )
  } else if (individual %in% id_medical){
    ind_loc_t2 <- case_when(
      individual %in% id_room_t1 ~ rooms[rooms$id == "ALL", "id_room"],
      individual %in% id_nursing_station_t1 ~ rooms[rooms$id == "ALL", "id_room"],
      individual %in% id_office_t1 ~ rooms[rooms$id == "ALL", "id_room"],
      individual %in% id_medical_restroom_t1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
      individual %in% id_corridor_t1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
      individual %in% id_not_here_t1 ~ -1,
      .default = -3 #"ERROR - WRONG LOC MED t2"
    )
  } else {
    ind_loc_t2 <- -4 #"ERROR - ID NOT IN MED/PARAMED"
  }
  ## ASSIGN THE localization OF THE INDIVIDUAL AT t==2
  localization_t2[localization_t2$id == individual, "localization"] <- ind_loc_t2
}

## CHANGE THE GLOBAL localization DATAFRAME AT t==2
global_localization[[2]]$localization <- localization_t2$localization
    
rm(localization_t1,
   localization_t2,
   id_not_interacting_t2,
   id_room_t1,
   id_corridor_t1,
   id_not_here_t1,
   id_medical_restroom_t1,
   id_paramedical_restroom_t1,
   id_nursing_station_t1,
   id_office_t1,
   ind_loc_t2)

```


```{r Loc tsup2}
############
## t > 2 ###
############
for (t in 3:n_subdivisions){
  localization_t <- global_localization[[t]]
  localization_tm1 <- global_localization[[t-1]]
  
  id_not_interacting_t <- localization_t %>% filter(is.na(localization)) %>% pull(id)
  
  id_room_tm1 <- localization_tm1 %>% filter(localization %in% id_room_patient) %>% pull(id)
  id_corridor_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
  id_office_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "M-PE", "id_room"]) %>% pull(id)
  id_medical_restroom_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "R-M-PE", "id_room"]) %>% pull(id)
  id_nursing_station_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "PM-PE", "id_room"]) %>% pull(id)
  id_paramedical_restroom_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "R-PM-PE", "id_room"]) %>% pull(id)
  
  id_not_here_tm1 <- localization_tm1 %>% filter(localization == -1 ) %>% pull(id)
  
  ## ITERATE ON THE INDIVIDUALS NOT INTERACTING at time t
  for (individual in id_not_interacting_t){
    shifts_j <- shifts[shifts$individual == individual, ]
    current_time <- begin_date + t * 30
    in_shift <- any(current_time >= shifts_j$start_time & current_time <= shifts_j$end_time)
    
    if (in_shift) {
      ## If the individual is within a shift
      
      if (individual %in% id_paramedical){
        ind_loc_t <- case_when(
          individual %in% id_room_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
          individual %in% id_nursing_station_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
          individual %in% id_paramedical_restroom_tm1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
          individual %in% id_corridor_tm1 ~ rooms[rooms$id == "R-PM-PE", "id_room"],
          individual %in% id_not_here_tm1 ~ -1,
          .default = -5 #"ERROR - WRONG LOC PARAMED t>2"
        )
      } else if (individual %in% id_medical){
        ind_loc_t <- case_when(
          individual %in% id_room_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
          individual %in% id_nursing_station_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
          individual %in% id_office_tm1 ~ rooms[rooms$id == "ALL", "id_room"],
          individual %in% id_medical_restroom_tm1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
          individual %in% id_corridor_tm1 ~ rooms[rooms$id == "R-M-PE", "id_room"],
          individual %in% id_not_here_tm1 ~ -1,
          .default = -6 #"ERROR - WRONG LOC MED t>2"
        )
      } else {
        ind_loc_t <- -7 #"ERROR - ID NOT IN MED/PARAMED t>2"
        }
    } else {
      ## If the individual is not within a shift
      ind_loc_t <- -1 #"NOT HERE"
    }
    ## ASSIGN THE localization OF THE INDIVIDUAL AT t>2
    localization_t[localization_t$id == individual, "localization"] <- ind_loc_t
  }
  
  global_localization[[t]] <- localization_t
}
```


#SAVE TO .RData FILES
```{r Save to .RData}
save(clusters,
     global_localization,
     global_interaction,
     admission,
     rooms,
     shifts,
     id_hcw,
     id_patient,
     begin_date,
     end_date,
     n_subdivisions,
     file = file.path(loc_nodscov2_path, "dev-localization-nodscov2.RData"))
```







