---
title: "localization-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-05-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
#library(tidyverse)
library(ggplot2)
library(lubridate)
library(igraph)
```

```{r}
wd <- getwd()
knitr::opts_chunk$set(root.dir = wd)

data_path <- file.path(wd,"..", "..", "data")
nodscov2_path <- file.path(data_path, "data-nodscov2") 
```

### WIP 

## NodsCov2 data (not shared)
```{r}
load("Y:/ogaufres/projet-pacri/data/data-nodscov2/admission_ctc_nodscov2.RData")
load("Y:/ogaufres/projet-pacri/data/data-nodscov2/list_ward.RData")
```


## FIXING ENCODING
```{r}
Encoding(admission$hospital) <- 'latin1'
```


## Raymond Poincaré reanimation ward
```{r}
data <- list_ward[["Raymond_Poincare-Reanimation-20200506-20200507"]]
admission <- admission %>%
  ## Remove visitors/admin/logistics/investigators
  filter(ward == "Reanimation") %>% 
  filter(hospital == "APHP - RAYMOND POINCARÉ") %>%
  filter(!(cat %in% c("administration",
                  "investigation",
                  "logistic",
                  "visitor"))) %>%
  ## ADD PE/PA IN ADMISSION'S IDs (id)
  mutate(id_bis = paste0(status,"-",id))
## FILTER INTERACTIONS TO KEEP ONLY HCW AND PATIENTS
data <- data %>%
  filter(from %in% admission$id & to %in% admission$id)
  
## ADD INFO OF THE STATUS FOR INDIVIDUALS
data <- left_join(data, admission %>% select(id, status), by = c("from" = "id")) %>%
    rename(from_status = status) %>%
    left_join(admission %>% select(id, status), by = c("to" = "id")) %>%
    rename(to_status = status)
```


## SUBDIVIDING EVERY 30s
```{r}
begin_date <- as.POSIXct(min(data$date_posix_first))
end_date <- as.POSIXct(max(data$date_posix_first + data$length))
time_spent <- end_date - begin_date
n_subdivisions <- as.integer(time_spent) * 24 * 60 * 2 ## Time spent * hours * minutes * 2 (number of time subdivisions)


data_list <- lapply(1:n_subdivisions, function(t){
  interactions_t <- data %>%
    filter(date_posix_first <= begin_date + (t)*30 & date_posix_first + length >= begin_date + (t+1)*30) %>%
    mutate(time = t) %>%
    select(from, to, time, from_status, to_status)
  
  return(interactions_t)
})


## Expand to a single DF + write to csv file
#data_tot <- do.call(rbind, data_list)
#write.csv2(x = data_tot, file = file.path(nodscov2_path, "int_tot_RP_test.csv"), row.names = FALSE)

## TO READ IT
#data_tot <- read.csv2(file = file.path(nodscov2_path, "int_tot_RP_test.csv"), row.names = F)
```

## DOUBLE ROOMS
```{r}
## EITHER CHOOSE TO REMOVE THE INTERACTION BETWEEN THE INDUVIDUALS OR PUT A PERMANENT INTERACTION BETWEEN THE INDIVIDUALS

##PERMANENT INTERACTION
# ## RP reanimation ward has 2 double rooms -> individuals are always in contact (c.f. R/nodscov2/interaction-nodscov2.Rmd)
# for(t in 1:n_subdivisions){
#   a_df <- data.frame(from = "001-0038-B-S", to = "001-0039-B-F", time = t, from_status = "PA", to_status = "PA")
#   b_df <- data.frame(from = "001-0127-B-A", to = "001-0128-Z-K", time = t, from_status = "PA", to_status = "PA")
#   data_tot <- bind_rows(data_tot, a_df, b_df)
# }
```


## ROOMS
```{r}
rooms <- admission %>%
  filter(status == "PA") %>%
  distinct(id) %>%
  mutate(room = as.factor(row_number())) %>%
  mutate(id_room = as.factor(row_number())) %>%
  select(id_room,room, id)

rooms <- rooms %>%
  bind_rows(data.frame(room = "Restroom", id = "PE", id_room = as.factor(nrow(rooms) + 1))) %>%
  bind_rows(data.frame(room = "Corridor", id = "ALL", id_room = as.factor(nrow(rooms) + 2)))

### DOUBLE ROOMS
## "001-0038-B-S" and = "001-0039-B-F" are in the same room
## "001-0127-B-A" and "001-0128-Z-K" are in the same room
rooms <-rooms %>% mutate(room = ifelse(id == "001-0038-B-S", rooms[rooms$id == "001-0039-B-F", "room"], room),
                         id_room = ifelse(id == "001-0038-B-S", rooms[rooms$id == "001-0039-B-F", "id_room"], id_room))

rooms <-rooms %>% mutate(room = ifelse(id == "001-0128-Z-K", rooms[rooms$id == "001-0127-B-A", "room"], room),
                         id_room = ifelse(id == "001-0128-Z-K", rooms[rooms$id == "001-0127-B-A", "id_room"], id_room))

double_rooms <- list(c("001-0038-B-S", "001-0039-B-F"), c("001-0127-B-A", "001-0128-Z-K"))

```


## INTERACTION localization
```{r}
data_list <- lapply(data_list, function(df) {
  df <- df %>% mutate(localization = NA)
  
  # Join data_tot with rooms based on the common column (id) for 'from'
  df <- df %>%
    left_join(rooms, by = c("from" = "id")) %>%  ## .x join
    left_join(rooms, by = c("to" = "id")) %>% ## .y join
    mutate(localization = case_when(
      from %in% c("001-0038-B-S", "001-0039-B-F") | to %in% c("001-0038-B-S", "001-0039-B-F") ~ rooms[rooms$id == "001-0038-B-S", "id_room"],
      from %in% c("001-0127-B-A", "001-0128-Z-K") | to %in% c("001-0127-B-A", "001-0128-Z-K") ~ rooms[rooms$id == "001-0127-B-A", "id_room"],
      from_status == "PE" & to_status == "PE" ~ rooms[rooms$id == "PE" , "id_room"],
      from_status == "PA" & to_status == "PE" ~ id_room.x,
      from_status == "PE" & to_status == "PA" ~ id_room.y,
    )) %>%
    select(-room.x, -id_room.x, -room.y, -id_room.y)
  
  ## Remove duplicated interactions (there is sometimes interactions recorded multiple times)
  df <- unique(df)
  
  return(df)
})

#### WE CAN UPDATE THIS localization MODEL TO USE:
## THE PREVIOUS INT OF INDIVIDUALS
## IF THERE IS ONLY 2 individuals interactings --> Corridor
## IF THERE IS MORE THAN TWO PATIENTS --> Corridor ? (c.f. overlap section )
## etc etc


#data_tot <- do.call(rbind, data_list)
```


## INTERACTION CLUSTERS FOR EACH TIME t
```{r}
clusters <- lapply(data_list, function(df) {
  # non oriented graph based on interaction happening at time t
  graph <- graph_from_data_frame(df, directed = FALSE)
  # Extract connected component
  clusters <- clusters(graph)$membership
  # clusters to list transformation
  clusters_list <- lapply(unique(clusters), function(i) {
    as.character(V(graph)[clusters == i]$name)
  })
  return(clusters_list)
})
```



## localization INFERENCE - inferred ADMISSIONS & HCW NOT PRESENT DURING THE WHOLE STUDY - TEMPORARY (assign first_time and last_time for individual --> TO KNOW WHEN THEY LEAVE)
```{r}
HCW_ids <- admission$id[admission$status == "PE"]
data_tot <- do.call(rbind,data_list)
## FOR PE-PA INTERACTIONS
a = data_tot %>%
  filter(!(from_status == "PA" & to_status == "PA") & !(from_status == "PE" & to_status == "PE")) %>%
  mutate(id = ifelse(from_status == "PE", from, to)) %>% 
  group_by(id) %>%
  mutate(first_time = min(time), last_time = max(time)) %>%
  ungroup() %>%
  distinct(id, .keep_all = T) %>%
  filter(id %in% HCW_ids) %>%
  select(id, first_time, last_time)

## FOR PE-PE INTERACTIONS | FROM
b = data_tot %>%
  filter(from_status == "PE" & to_status == "PE") %>%
  mutate(id = from) %>% 
  group_by(id) %>%
  mutate(first_time = min(time), last_time = max(time)) %>%
  ungroup() %>%
  distinct(id, .keep_all = T) %>%
  filter(id %in% HCW_ids) %>%
  select(id, first_time, last_time)

## FOR PE-PE INTERACTIONS | TO
c = data_tot %>%
  filter(from_status == "PE" & to_status == "PE") %>%
  mutate(id = to) %>% 
  group_by(id) %>%
  mutate(first_time = min(time), last_time = max(time)) %>%
  ungroup() %>%
  distinct(id, .keep_all = T) %>%
  filter(id %in% HCW_ids) %>%
  select(id, first_time, last_time)


inferred_admission <- bind_rows(a, b, c) %>%
  group_by(id) %>%
  summarise(
    first_time = min(first_time),
    last_time = max(last_time)
    ) %>%
  ungroup()

print(inferred_admission)

rm(a)
rm(b)
rm(c)
rm(data_tot)


## THERE IS HCW THAT ARE NOT PRESENT DURING THE STUDY --> WE CAN EXCLUDE THEM FROM THE localization INFERENCE MODEL
HCW_interacting_ids <- inferred_admission %>% pull(id)
length(HCW_interacting_ids)
HCW_not_here <- setdiff(HCW_ids, HCW_interacting_ids)
# data_tot %>% filter(from %in% HCW_not_here | to %in% HCW_not_here) 


## WE EXCLUDE THE HCWs NOT PRESENT DURING THE STUDY
# WE USE list_HCW_interacting INSTEAD OF HCW_ids
```



## localization INFERENCE (only for PE, PAs stay in their room) - INTERACTIONS
```{r}
############################################################
## ASSIGNING localization FOR THE INDIVIDUALS INTERACTING ##
############################################################

## Store info when there is more than one patient in clusters -> fix later
cluster_info_list <- list()
global_localization <- list()


global_localization <- lapply(1:n_subdivisions, function(t) {
  localization_t <- data.frame(id = HCW_interacting_ids, localization = NA, time = t)

  # Interactions at time t
  interactions_t <- data_list[[t]]
  clusters_t <- clusters[[t]]
  # For each clusters of individuals at time t
  lapply(clusters_t, function(cluster) {
    # IF THERE IS ONLY ONE PATIENT IN THE CLUSTER
    ONE_patient_in_cluster <- length(unique(cluster[!cluster %in% HCW_interacting_ids])) == 1
    ## IF IN DOUBLE ROOM (MUST BE ONLY THE TWO PATIENTS, NOT THE TWO PATIENT + ANOTHER PATIENT)
    IN_DOUBLE_ROOM_N1 <- identical(unique(cluster[!cluster %in% HCW_interacting_ids]),
                                   double_rooms[[1]])
    IN_DOUBLE_ROOM_N2 <- identical(unique(cluster[!cluster %in% HCW_interacting_ids]),
                                   double_rooms[[2]])
    # IF THERE IS MULTIPLE PATIENTS IN THE CLUSTER (AND NOT IN DOUBLE ROOM)
    MULTIPLE_patients_in_cluster <- length(unique(cluster[!cluster %in% HCW_interacting_ids])) > 1 & !(IN_DOUBLE_ROOM_N1 | IN_DOUBLE_ROOM_N2)
    
    ## localization OF THE CLUSTER
    if (MULTIPLE_patients_in_cluster){
      cluster_localization <- rooms[rooms$id == "ALL", "id_room"]
    } else if (IN_DOUBLE_ROOM_N1) {
      cluster_localization <- unique(rooms[rooms$id == double_rooms[[1]][[1]], "id_room"])
    } else if (IN_DOUBLE_ROOM_N2) {
      cluster_localization <- unique(rooms[rooms$id == double_rooms[[2]][[1]], "id_room"])
    } else if (ONE_patient_in_cluster) {
      cluster_localization <- rooms[rooms$id == cluster[!cluster %in% HCW_interacting_ids], "id_room"]
    } else {
      cluster_localization <- rooms[rooms$id == "PE", "id_room"] ## ONLY HCW INTERACTING
    }
    ## Assign the localization for individuals inside the cluster (<<- to edit localization_t defined outside clusters_t's lapply)
    localization_t$localization <<- ifelse(localization_t$id %in% cluster, cluster_localization, localization_t$localization)

    ## MULTIPLE PATIENTS IN THE CLUSTER --> TEMPORARY, FIXED LATER
    if (MULTIPLE_patients_in_cluster) {
      cluster_possible_localization <- rooms[rooms$id %in% cluster[!cluster %in% HCW_interacting_ids], "id_room"]
      cluster_info <- data.frame(Cluster = t, Patients = cluster[!cluster %in% HCW_interacting_ids])
      cluster_info_list <<- append(cluster_info_list, list(cluster_info))
    }
  })
  
  return(localization_t)
})
```


## localization INFERENCE (only for PE, PAs stay in their room) - NO INTERACTION
```{r}
################################################################
## ASSIGNING localization FOR THE INDIVIDUALS NOT INTERACTING ##
################################################################

############
## t == 1 ##
############

# FIRST SUBDIVISION 
## RULES TO BE DEFINED
## IF NOT INTERACTING AT t == 1, assign localization to "NOT HERE"

global_localization[[1]]$localization <- ifelse(is.na(global_localization[[1]]$localization), "NOT HERE", global_localization[[1]]$localization )
```


```{r}
############
## t == 2 ##
############

## SECOND SUBDIVISION
localization_t1 <- global_localization[[1]]
localization_t2 <- global_localization[[2]]
id_not_interacting_t2 <- localization_t2 %>% filter(is.na(localization)) %>% pull(id)
id_room_t1 <- localization_t1 %>% filter(localization != rooms[rooms$id == "PE", "id_room"] &
                                           localization != rooms[rooms$id == "ALL", "id_room"] &
                                           localization != "NOT HERE" &
                                           !is.na(localization)
                                         ) %>% pull(id)
  

id_corridor_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
id_restroom_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "PE", "id_room"]) %>% pull(id)
id_not_here_t1 <- localization_t1 %>% filter(localization == "NOT HERE") %>% pull(id)


for (individual in id_not_interacting_t2){
  ## 1. IF INDIVIDUAL IS INTERACTING AT t-1 (localization_tm1$localization != "NOT HERE")
  if (individual %in% id_room_t1){
    #IF IN ROOM -> CORRIDOR
    ind_loc_t2 <- rooms[rooms$id == "ALL", "id_room"]
  } else if (individual %in% id_corridor_t1){
    #IF IN CORRIDOR -> RESTROOM
    ind_loc_t2 <- rooms[rooms$id == "PE", "id_room"]
  } else if (individual %in% id_restroom_t1){
    #IF RESTROOM --> STAYS IN RESTROOM
    ind_loc_t2 <- rooms[rooms$id == "PE", "id_room"]
    
    ## 2. IF INDIVIDUAL NOT INTERACTING AT t-1 --> (localization_tm1$localization == "NOT HERE") --> "NOT HERE"
  } else if (individual %in% id_not_here_t1){
    ind_loc_t2 <- "NOT HERE"
  }
  ## ASSIGN THE localization OF THE INDIVIDUAL AT t==2
  localization_t2[localization_t2$id == individual, "localization"] <- ind_loc_t2
}

## CHANGE THE GLOBAL localization DATAFRAME AT t==2
global_localization[[2]]$localization <- localization_t2$localization
    
rm(localization_t1)
rm(localization_t2)
rm(id_not_interacting_t2)
rm(id_room_t1)
rm(id_corridor_t1)
rm(id_restroom_t1)
rm(id_not_here_t1)
rm(ind_loc_t2)
```


```{r}
############
## t > 2 ###
############

## THREE CASES -> 
    ## 1. IF INDIVIDUAL IS INTERACTING AT t-1 (localization_tm1$localization != "NOT HERE") --> IF IN ROOM -> CORRIDOR, IF IN CORRIDOR -> RESTROOM
    ## 2. IF INDIVIDUAL NOT INTERACTING AT t-1 AND INTERACTING AT t-2  --> CANNOT BE IN ROOM/CORRIDOR -> Restroom or alone etc
    ## 3. IF INDIVIDUAL NOT INTERACTING AT t-1 AND NEITHER AT t-2 --> RULES TO BE DEFINED


## RULES TO BE DEFINED
  ## IF IN A ROOM (i.e. localization < 19) at t-1 --> Corridor 
  ## IF IN CORRIDOR (i.e. localization = 19) at t-1 --> Restroom
  ## IF NO INTERACTION AT T-1 --> ?
ta_no_int <- Sys.time()
for (t in 3:n_subdivisions){
  localization_t <- global_localization[[t]]
  localization_tm1 <- global_localization[[t-1]]
  
  id_not_interacting_t <- localization_t %>% filter(is.na(localization)) %>% pull(id)
  
  id_room_tm1 <- localization_tm1 %>% filter(localization != rooms[rooms$id == "PE", "id_room"] &
                                           localization != rooms[rooms$id == "ALL", "id_room"] &
                                           localization != "NOT HERE" &
                                           !is.na(localization)
                                         ) %>% pull(id)
  

  id_corridor_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
  id_restroom_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "PE", "id_room"]) %>% pull(id)
  id_not_here_tm1 <- localization_tm1 %>% filter(localization == "NOT HERE") %>% pull(id)
  
  ## ITERATE ON THE INDIVIDUALS NOT INTERACTING at time t
  for (individual in id_not_interacting_t){
    ## LAST INTERACTION KNOWN FOR THE INDIVIDUAL (C.F. inferred ADMISSION)
    
    ## 1. IF INDIVIDUAL IS INTERACTING AT t-1 (localization_tm1$localization != "NOT HERE")
    if (inferred_admission[inferred_admission$id == individual, "last_time"] < t){
      ind_loc_t <- "NOT HERE"
    } else if (individual %in% id_room_tm1){
      #IF IN ROOM -> CORRIDOR
      ind_loc_t <- rooms[rooms$id == "ALL", "id_room"]
    } else if (individual %in% id_corridor_tm1){
      #IF IN CORRIDOR -> RESTROOM
      ind_loc_t <- rooms[rooms$id == "PE", "id_room"]
    } else if (individual %in% id_restroom_tm1){
      #IF RESTROOM --> STAYS IN RESTROOM #### TEMPORARY #########
      ind_loc_t <- rooms[rooms$id == "PE", "id_room"]
      ## 2. IF INDIVIDUAL NOT INTERACTING AT t-1 --> (localization_tm1$localization == "NOT HERE") --> "NOT HERE"
    } else if (individual %in% id_not_here_tm1){
      ind_loc_t <- "NOT HERE"
    }  else {
      ind_loc_t <- "ERROR"
    }
    ## ASSIGN THE localization OF THE INDIVIDUAL AT t==2
    localization_t[localization_t$id == individual, "localization"] <- ind_loc_t
  }
  
  global_localization[[t]] <- localization_t
}
tb_no_int <- Sys.time()
print(tb_no_int - ta_no_int)


```
## TEMPORARY
#SAVE TO .RData FILES
```{r}
save(clusters, global_localization, inferred_admission, rooms, data_list, admission, HCW_interacting_ids, n_subdivisions, begin_date, end_date, file = "localization-nodscov2.RData")
```


<!-- ################################# GARBAGE ############################## -->

## OVERLAP
```{r}
## MULTIPLE PATIENTS IN INTERACTION CLUSTERS (without double rooms)
u = do.call(rbind, cluster_info_list)


## TEMPORARY

# ta <- Sys.time()
# overlap <- data.frame()
# 
# 
# 
# for (t in 1:n_subdivisions){
#   for (individual in admission$id){
#     if (dim(data_tot %>% filter(from == individual | to == individual) %>% filter(time == t) %>% distinct(localization))[1] > 1){
#       overlap <- bind_rows(overlap, data_tot %>% filter(from == individual | to == individual) %>% filter(time == t) )
#     }
#   }
# }
# tb <- Sys.time()
# print(tb-ta)
# 
# ## 18min 07/05/24
# 
#     # previous_int <- data_tot %>% filter(from == individual | to == individual) %>% filter(time == t-1)
#     # current_int <- data_tot %>% filter(from == individual | to == individual) %>% filter(time == t)
#     # future_int <- data_tot %>% filter(from == individual | to == individual) %>% filter(time == t+1)
#     # overlap <- current_int %>% distinct(localization)
# write.csv2(data = overlap, file = file.path(nodscov2_path, "overlap-RP-test.csv"), row.names = F, header = T)

overlap <- read.csv2(file = file.path(nodscov2_path, "overlap-RP-test.csv"))
## Only checking for multiple CHAMBER assignation
overlap_bis <- overlap %>%
  filter(!(from_status == "PE" & to_status == "PE")) %>% 
  filter(!(from_status == "PA" & to_status == "PA")) %>%
  mutate(id = if_else(from_status == "PE", from, to)) ## ID OF THE HCW


result <- overlap_bis %>%
  group_by(id, time) %>%
  mutate(unique_loc = n_distinct(localization)) %>% # Nb of distinct localization assigned to each HCWs 
  filter(unique_loc > 1) %>%
  select(-unique_loc)

View(result)

## Distinct nb of room each HCW is assigned to during the 
result %>% group_by(id) %>% distinct(localization, .keep_all = T) %>% summarise( n = n())
```







