---
title: "localization-nodscov2"
author: "Olivier GAUFRÈS"
date: "2024-05-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
#library(tidyverse)
library(ggplot2)
library(lubridate)
library(igraph)
library(tidyr)
```

```{r}
wd <- getwd()
knitr::opts_chunk$set(root.dir = wd)


data_path <- file.path(wd,"..", "..", "data")
nodscov2_path <- file.path(data_path, "data-nodscov2") 
loc_nodscov2_path <- file.path(wd, "..", "..", "out", "loc-nodscov2")

if (!dir.exists(loc_nodscov2_path)) {
  dir.create(loc_nodscov2_path, recursive = TRUE)
}
```

### WIP 

## NodsCov2 data (not shared)
```{r}
load(file.path(nodscov2_path, "admission_ctc_nodscov2.RData"))
load(file.path(nodscov2_path, "list_ward.RData"))
# load("Y:/ogaufres/pacri-non-sync/data/data-nodscov2/admission_ctc_nodscov2.RData")
# load("Y:/ogaufres/pacri-non-sync/data/data-nodscov2/list_ward.RData")
```


## FIXING ENCODING
```{r}
Encoding(admission$hospital) <- 'latin1'
```


## Raymond Poincaré reanimation ward
```{r}
data <- list_ward[["Raymond_Poincare-Reanimation-20200506-20200507"]]
admission <- admission %>%
  ## Remove visitors/admin/logistics/investigators
  filter(ward == "Reanimation") %>% 
  filter(hospital == "APHP - RAYMOND POINCARÉ") %>%
  filter(!(cat %in% c("administration",
                  "investigation",
                  "logistic",
                  "visitor"))) %>%
  ## ADD PE/PA IN ADMISSION'S IDs (id)
  mutate(id_bis = paste0(status,"-",id))
## FILTER INTERACTIONS TO KEEP ONLY HCW AND PATIENTS
data <- data %>%
  filter(from %in% admission$id & to %in% admission$id)
  
## ADD INFO OF THE STATUS FOR INDIVIDUALS
data <- left_join(data, admission %>% select(id, status), by = c("from" = "id")) %>%
    rename(from_status = status) %>%
    left_join(admission %>% select(id, status), by = c("to" = "id")) %>%
    rename(to_status = status)

data <- unique(data)
```


## SUBDIVIDING EVERY 30s
```{r}
begin_date <- as.POSIXct(min(data$date_posix_first))
end_date <- as.POSIXct(max(data$date_posix_first + data$length))
time_spent <- difftime(end_date, begin_date, units = "mins")  

n_subdivisions <- floor(as.numeric(time_spent) * 2) ## Time spent * hours * minutes * 2 (number of time subdivisions)
## floor because of the manner we extract the interactions (=30sec, i.e. at  the end, interactions are <30sec -> we dont take these)


## t = 1 -> [0,30]sec
global_interaction <- lapply(1:n_subdivisions, function(t){
  interactions_t <- data %>%
    filter(date_posix_first <= (begin_date + (t-1)*30) & (date_posix_first + length >= begin_date + (t)*30) ) %>%
    mutate(time = t) %>%
    select(from, to, time, from_status, to_status)
  
  return(interactions_t)
})


## Expand to a single DF + write to csv file
#data_tot <- do.call(rbind, global_interaction)
#write.csv2(x = data_tot, file = file.path(nodscov2_path, "int_tot_RP_test.csv"), row.names = FALSE)

## TO READ IT
#data_tot <- read.csv2(file = file.path(nodscov2_path, "int_tot_RP_test.csv"), row.names = F)
```

## DOUBLE ROOMS
```{r}
## 3 CHOICES
# 1. KEEP THE INTERACTION REGARDLESS OF THE SINGLE/DOUBLE ROOM ASSIGNATION (WE CHOSE THIS ASSUMPTION)


## 2. CHOOSE TO REMOVE THE INTERACTION BETWEEN THE INDUVIDUALS
# data_tot <- data_tot %>%
#   filter(! (from == "001-0038-B-S" & to == "001-0039-B-F")) %>%
#   filter(! (from == "001-0039-B-F" & to == "001-0038-B-S")) %>%
#   filter(! (from == "001-0128-Z-K" & to == "001-0127-B-A")) %>%
#   filter(! (from == "001-0127-B-A" & to == "001-0128-Z-K")) %>%
  

# 3. CHOOSE TO PUT A PERMANENT INTERACTION BETWEEN THE INDIVIDUALS
# ## RP reanimation ward has 2 double rooms (c.f. R/nodscov2/interaction-nodscov2.Rmd)
# for(t in 1:n_subdivisions){
#   a_df <- data.frame(from = "001-0038-B-S", to = "001-0039-B-F", time = t, from_status = "PA", to_status = "PA")
#   b_df <- data.frame(from = "001-0127-B-A", to = "001-0128-Z-K", time = t, from_status = "PA", to_status = "PA")
#   data_tot <- bind_rows(data_tot, a_df, b_df)
# }
```


## ROOMS
```{r}
rooms <- admission %>%
  filter(status == "PA") %>%
  distinct(id) %>%
  mutate(room = as.factor(row_number())) %>%
  mutate(id_room = as.factor(row_number())) %>%
  select(id_room,room, id)

rooms <- rooms %>%
  bind_rows(data.frame(room = "Restroom", id = "PE", id_room = as.factor(nrow(rooms) + 1))) %>%
  bind_rows(data.frame(room = "Corridor", id = "ALL", id_room = as.factor(nrow(rooms) + 2)))

### DOUBLE ROOMS
## "001-0038-B-S" and = "001-0039-B-F" are in the same room
## "001-0127-B-A" and "001-0128-Z-K" are in the same room
rooms <-rooms %>% mutate(room = ifelse(id == "001-0038-B-S", rooms[rooms$id == "001-0039-B-F", "room"], room),
                         id_room = ifelse(id == "001-0038-B-S", rooms[rooms$id == "001-0039-B-F", "id_room"], id_room))

rooms <-rooms %>% mutate(room = ifelse(id == "001-0128-Z-K", rooms[rooms$id == "001-0127-B-A", "room"], room),
                         id_room = ifelse(id == "001-0128-Z-K", rooms[rooms$id == "001-0127-B-A", "id_room"], id_room))

double_rooms <- list(c("001-0038-B-S", "001-0039-B-F"), c("001-0127-B-A", "001-0128-Z-K"))
```




## INTERACTION CLUSTERS FOR EACH TIME t
```{r}
clusters <- lapply(global_interaction, function(df) {
  # df to non oriented graph based on interaction happening at time t
  graph <- graph_from_data_frame(df, directed = FALSE)
  # Extract connected component
  clusters <- components(graph)$membership
  # clusters to list (unique list of individual)
  clusters_list <- lapply(unique(clusters), function(i) {
    #for each cluster i, we extract the vertices/nodes of the graph -> individual names in each clusters 
    as.character(V(graph)[clusters == i]$name)
  })
  return(clusters_list)
})
```



## SHIFTS INFERENCE
```{r}
# Pivot -> get all int for each individual
df_long <- data %>%
  mutate(date_posix_end = date_posix_first + length) %>% 
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>%
  arrange(individual, date_posix_first)

# Time between 2 interactions for each individual (lag get the previous )
df_long <- df_long %>%
  group_by(individual) %>%
  mutate(test_filter = date_posix_first - lag(date_posix_end)) %>%
  filter(test_filter > 0 | is.na(test_filter)) %>%
  mutate(time_diff = difftime(date_posix_first, lag(date_posix_end), units = "mins"))


time_threshold <- 60*2

df_long <- df_long %>%
  mutate(new_shift = ifelse(is.na(time_diff) | time_diff > time_threshold, 1, 0)) %>%
  group_by(individual) %>%
  mutate(shift_id = cumsum(new_shift))

shifts <- df_long %>%
  group_by(individual, shift_id) %>%
  summarise(
    start_time = min(date_posix_first),
    end_time = max(date_posix_end),
    shift_length = as.numeric(difftime(max(date_posix_end), min(date_posix_first), units = "hours")),
    .groups = 'drop'
  ) %>%
  arrange(individual, shift_id) %>%
  left_join(admission %>% select(id,status), by = c("individual" = "id")) %>%
  filter(status == "PE")

```

## CHECK INDIVIDUALS IN ADMISSION: HERE OR NOT HERE DURING THE STUDY?
```{r}
id_interacting <- data %>%
  pivot_longer(cols = c(from, to), names_to = "direction", values_to = "individual") %>% distinct(individual) %>% pull()
id_total <- admission %>% distinct(id) %>% pull()



id_not_interacting <- setdiff(id_total, id_interacting)
print(admission %>% filter(id %in% id_not_interacting))
## INDIVIDUALS WITH 0 INTERACTIONS ARE HCWs -> WE REMOVE THEM
HCW_interacting_ids <- admission %>% filter(status == "PE") %>% filter(id %in% id_interacting) %>% pull(id)
```


## Localization INFERENCE (only for PE, PAs stay in their room) - INTERACTIONS
```{r}
############################################################
## ASSIGNING localization FOR THE INDIVIDUALS INTERACTING ##
############################################################

## Store info when there is more than one patient in clusters -> fix later
cluster_info_list <- list()
global_localization <- list()


global_localization <- lapply(1:n_subdivisions, function(t) {
  localization_t <- data.frame(id = HCW_interacting_ids, localization = NA, time = t) ##only hcw that are actually here 

  # Interactions at time t
  interactions_t <- global_interaction[[t]]
  clusters_t <- clusters[[t]]
  # For each clusters of individuals at time t
  lapply(clusters_t, function(cluster) {
    # IF THERE IS ONLY ONE PATIENT IN THE CLUSTER
    ONE_patient_in_cluster <- length(unique(cluster[!cluster %in% HCW_interacting_ids])) == 1
    ## IF IN DOUBLE ROOM (MUST BE ONLY THE TWO PATIENTS, NOT THE TWO PATIENT + ANOTHER PATIENT)
    IN_DOUBLE_ROOM_N1 <- identical(unique(cluster[!cluster %in% HCW_interacting_ids]),
                                   double_rooms[[1]])
    IN_DOUBLE_ROOM_N2 <- identical(unique(cluster[!cluster %in% HCW_interacting_ids]),
                                   double_rooms[[2]])
    # IF THERE IS MULTIPLE PATIENTS IN THE CLUSTER (AND NOT IN DOUBLE ROOM)
    MULTIPLE_patients_in_cluster <- length(unique(cluster[!cluster %in% HCW_interacting_ids])) > 1 & !(IN_DOUBLE_ROOM_N1 | IN_DOUBLE_ROOM_N2)
    
    ## localization OF THE CLUSTER
    if (MULTIPLE_patients_in_cluster){
      cluster_localization <- rooms[rooms$id == "ALL", "id_room"]
    } else if (IN_DOUBLE_ROOM_N1) {
      cluster_localization <- unique(rooms[rooms$id == double_rooms[[1]][[1]], "id_room"])
    } else if (IN_DOUBLE_ROOM_N2) {
      cluster_localization <- unique(rooms[rooms$id == double_rooms[[2]][[1]], "id_room"])
    } else if (ONE_patient_in_cluster) {
      cluster_localization <- rooms[rooms$id == cluster[!cluster %in% HCW_interacting_ids], "id_room"]
    } else {
      cluster_localization <- rooms[rooms$id == "PE", "id_room"] ## ONLY HCW INTERACTING
    }
    ## Assign the localization for individuals inside the cluster (<<- to edit localization_t defined outside clusters_t's lapply scope)
    localization_t$localization <<- ifelse(localization_t$id %in% cluster, cluster_localization, localization_t$localization)

    ## MULTIPLE PATIENTS IN THE CLUSTER --> TEMPORARY, FIXED LATER
    if (MULTIPLE_patients_in_cluster) {
      cluster_possible_localization <- rooms[rooms$id %in% cluster[!cluster %in% HCW_interacting_ids], "id_room"]
      cluster_info <- data.frame(Cluster = t, Patients = cluster[!cluster %in% HCW_interacting_ids])
      cluster_info_list <<- append(cluster_info_list, list(cluster_info))
    }
  })
  
  return(localization_t)
})
```


## localization INFERENCE (only for PE, PAs stay in their room) - NO INTERACTION
```{r}
################################################################
## ASSIGNING localization FOR THE INDIVIDUALS NOT INTERACTING ##
################################################################

############
## t == 1 ##
############

# FIRST SUBDIVISION 
## RULES TO BE DEFINED
## IF NOT INTERACTING AT t == 1, assign localization to "NOT HERE"

global_localization[[1]]$localization <- ifelse(is.na(global_localization[[1]]$localization), "NOT HERE", global_localization[[1]]$localization )
```


```{r}
############
## t == 2 ##
############

## SECOND SUBDIVISION
localization_t1 <- global_localization[[1]]
localization_t2 <- global_localization[[2]]
id_not_interacting_t2 <- localization_t2 %>% filter(is.na(localization)) %>% pull(id)
id_room_t1 <- localization_t1 %>% filter(localization != rooms[rooms$id == "PE", "id_room"] &
                                           localization != rooms[rooms$id == "ALL", "id_room"] &
                                           localization != "NOT HERE" &
                                           !is.na(localization)
                                         ) %>% pull(id)
  

id_corridor_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
id_restroom_t1 <- localization_t1 %>% filter(localization == rooms[rooms$id == "PE", "id_room"]) %>% pull(id)
id_not_here_t1 <- localization_t1 %>% filter(localization == "NOT HERE") %>% pull(id)


for (individual in id_not_interacting_t2){
  ## 1. IF INDIVIDUAL IS INTERACTING AT t-1 (localization_tm1$localization != "NOT HERE")
  if (individual %in% id_room_t1){
    #IF IN ROOM -> CORRIDOR
    ind_loc_t2 <- rooms[rooms$id == "ALL", "id_room"]
  } else if (individual %in% id_corridor_t1){
    #IF IN CORRIDOR -> RESTROOM
    ind_loc_t2 <- rooms[rooms$id == "PE", "id_room"]
  } else if (individual %in% id_restroom_t1){
    #IF RESTROOM --> STAYS IN RESTROOM
    ind_loc_t2 <- rooms[rooms$id == "PE", "id_room"]
    
    ## 2. IF INDIVIDUAL NOT INTERACTING AT t-1 --> (localization_tm1$localization == "NOT HERE") --> "NOT HERE"
  } else if (individual %in% id_not_here_t1){
    ind_loc_t2 <- "NOT HERE"
  }
  ## ASSIGN THE localization OF THE INDIVIDUAL AT t==2
  localization_t2[localization_t2$id == individual, "localization"] <- ind_loc_t2
}

## CHANGE THE GLOBAL localization DATAFRAME AT t==2
global_localization[[2]]$localization <- localization_t2$localization
    
rm(localization_t1)
rm(localization_t2)
rm(id_not_interacting_t2)
rm(id_room_t1)
rm(id_corridor_t1)
rm(id_restroom_t1)
rm(id_not_here_t1)
rm(ind_loc_t2)
```


```{r}
############
## t > 2 ###
############

## THREE CASES -> 
    ## 1. IF INDIVIDUAL IS INTERACTING AT t-1 (localization_tm1$localization != "NOT HERE") --> IF IN ROOM -> CORRIDOR, IF IN CORRIDOR -> RESTROOM
    ## 2. IF INDIVIDUAL NOT INTERACTING AT t-1 AND INTERACTING AT t-2  --> CANNOT BE IN ROOM/CORRIDOR -> Restroom or alone etc
    ## 3. IF INDIVIDUAL NOT INTERACTING AT t-1 AND NEITHER AT t-2 --> RULES TO BE DEFINED


## RULES TO BE DEFINED
  ## IF IN A ROOM (i.e. localization < 19) at t-1 --> Corridor 
  ## IF IN CORRIDOR (i.e. localization = 19) at t-1 --> Restroom
  ## IF NO INTERACTION AT T-1 --> ?
ta_no_int <- Sys.time()
for (t in 3:n_subdivisions){
  localization_t <- global_localization[[t]]
  localization_tm1 <- global_localization[[t-1]]
  
  id_not_interacting_t <- localization_t %>% filter(is.na(localization)) %>% pull(id)
  
  id_room_tm1 <- localization_tm1 %>% filter(localization != rooms[rooms$id == "PE", "id_room"] &
                                           localization != rooms[rooms$id == "ALL", "id_room"] &
                                           localization != "NOT HERE" &
                                           !is.na(localization)
                                         ) %>% pull(id)
  

  id_corridor_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "ALL", "id_room"]) %>% pull(id)
  id_restroom_tm1 <- localization_tm1 %>% filter(localization == rooms[rooms$id == "PE", "id_room"]) %>% pull(id)
  id_not_here_tm1 <- localization_tm1 %>% filter(localization == "NOT HERE") %>% pull(id)
  
  ## ITERATE ON THE INDIVIDUALS NOT INTERACTING at time t
  for (individual in id_not_interacting_t){
    shifts_j <- shifts[shifts$individual == individual, ]
    current_time <- begin_date + t * 30
    in_shift <- any(current_time >= shifts_j$start_time & current_time <= shifts_j$end_time)
    
    if (in_shift) {
      ## If the individual is within a shift
      if (individual %in% id_room_tm1) {
        ind_loc_t <- rooms[rooms$id == "ALL", "id_room"] #IF IN ROOM -> CORRIDOR
      } else if (individual %in% id_corridor_tm1) {
        ind_loc_t <- rooms[rooms$id == "PE", "id_room"] #IF IN CORRIDOR -> RESTROOM
      } else if (individual %in% id_restroom_tm1) {
        ind_loc_t <- rooms[rooms$id == "PE", "id_room"] #IF RESTROOM --> STAYS IN RESTROOM #### TEMPORARY #########
      } else if (individual %in% id_not_here_tm1){
        ind_loc_t <- "NOT HERE"
      } else {
        ind_loc_t <- "ERROR"
      }
    } else {
      ## If the individual is not within a shift
      ind_loc_t <- "NOT HERE"
    }
    
    ## ASSIGN THE localization OF THE INDIVIDUAL AT t==2
    localization_t[localization_t$id == individual, "localization"] <- ind_loc_t
  }
  
  global_localization[[t]] <- localization_t
}
tb_no_int <- Sys.time()
print(tb_no_int - ta_no_int)

y <- do.call(rbind,global_localization)
```


## MUTATE "NOT HERE" TO -1 (for Rcpp) 
```{r}
global_localization <- lapply( 1:n_subdivisions, function(t){
  loc_t <- global_localization[[t]]
  loc_t <- loc_t %>% mutate(localization = ifelse(localization == "NOT HERE", -1, localization))
  loc_t$localization <- as.integer(loc_t$localization)
  return(loc_t)
})
```



## REBUILD GLOBAL_INTERACTION WITH CORRECT LOCALIZATION
```{r}
test_global_int <- global_interaction

# FOR EACH t
for (t in 1:length(test_global_int)) {
  interactions <- test_global_int[[t]]
  cluster <- clusters[[t]]
  
  # FOR EACH INT 
  for (j in 1:nrow(interactions)) {
    interaction <- interactions[j, ]
    id_from <- interaction$from ##from and to are in the same cluster
    # CLUSTER ASSOCIATED WITH THIS INTERACTION
    cluster_id <- NA  
    for (k in 1:length(cluster)) {
      if (id_from %in% cluster[[k]]) {
        cluster_id <- k
        break
      }
    }
    localization <- "NOT ASSIGNED"
    # ID ROOM
    if (interaction$from_status == "PA" & interaction$to_status == "PA"){ ## IF PA-PA
      localization1 <- rooms[rooms$id == interaction$from, "id_room"] ## DOUBLE ROOM, FROM/TO SAME THING
      localization2 <- rooms[rooms$id == interaction$to, "id_room"]
      localization <- ifelse(localization1 == localization2, localization1, "PROBLEM PA-PA NOT SAME ROOM")
    } else{ # IF PE-PE OR PA-PE OR PE-PA -> CAUTION, GLOBAL_LOCALIZATION ONLY TRACK HCW (PE) LOCALIZATION, WE CANNOT ACCESS TO CLUSTER'S LOCALIZATION USING A PATIENT (PA) ID
      patient_id <- ifelse(interaction$from_status == "PA", interaction$to, interaction$from)
      patient_room <- rooms[rooms$id == patient_id, "id_room"]
      localization <- global_localization[[t]] %>% filter(id == patient_id) %>% pull(localization)
    }

    # EDIT GLOBAL_INTERACTION
    test_global_int[[t]]$cluster_id[j] <- cluster_id
    test_global_int[[t]]$localization[j] <- localization
  }
}

global_interaction <- test_global_int
```


## TEMPORARY
#SAVE TO .RData FILES
```{r}
save(clusters,
     global_localization,
     shifts,
     rooms,
     global_interaction,
     admission,
     HCW_interacting_ids,
     n_subdivisions,
     begin_date,
     end_date,
     file = file.path(loc_nodscov2_path, "localization-nodscov2.RData"))
```



## DISTRIBUTION OF TIME SPENT IN RESTROOM/CORRIDOR BY CATEGORY OF HCW
```{r}
load(file.path(loc_nodscov2_path,"localization-nodscov2.RData")) ##overwrite admission

test_loc <- do.call(rbind, global_localization) %>%
  filter(localization %in% c(19,20)) %>%
  left_join(admission %>% select(id, cat), by = join_by(id)) %>% 
  left_join(rooms %>% select(id_room, room), by = c("localization" = "id_room")) %>% 
  group_by(id, cat, localization, room) %>%
  summarise(
    sum_room = n() * 30,
    n = n(),
    .groups = 'drop'
  )

## Violin and jitter
library(tidyverse)
library(hrbrthemes)
library(viridis)


test_loc %>%
  ggplot( aes(x=cat, y=sum_room/3600, fill=cat)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    ggh4x::facet_grid2(cols = vars(room), scales = "free_y", independent  ="y") +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    ggtitle("Cumulative time spent in restroom or corridor by category of HCW") +
    xlab("") +
    ylab("Cumulative time interacting (s)")

    
test_loc %>%
  ggplot( aes(x=cat, y=sum_room/3600, fill=cat)) +
    geom_violin() +
    geom_boxplot(width=.1) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    ggh4x::facet_grid2(cols = vars(room), scales = "free_y", independent  ="y") +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    ggtitle("Cumulative time spent in restroom or corridor by category of HCW") +
    xlab("") +
    ylab("Cumulative time interacting (s)")
    

test_loc %>% filter(room == "Restroom") %>%
  ggplot( aes(x=cat, y=sum_room/3600, fill=cat)) +
    geom_violin() +
    geom_boxplot(width=.1) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(angle = 35, hjust = 1)
    ) +
    ggtitle("Cumulative time spent in restroom or corridor by category of HCW") +
    xlab("") +
    ylab("Cumulative time interacting (s)")
```

## TEMPORARY
```{r}
ind_restroom <- test_loc %>% filter(sum_room > 15*3600) %>% pull(id)

summarise_int_restroom <- data %>%
  filter(from %in% ind_restroom | to %in% ind_restroom ) %>%
  mutate(id_restroom = ifelse(from %in% ind_restroom, from, to)) %>%
  left_join(admission %>% select(id,cat), by = c("id_restroom" = "id" )) %>%
  group_by(id_restroom) %>%
  summarise(date_min = min(date_posix_first), date_max = max(date_posix_first), .groups = "drop") %>%
  ungroup() 
  
int_restroom <- data %>%
  filter(from %in% ind_restroom | to %in% ind_restroom ) %>%
  mutate(id_restroom = ifelse(from %in% ind_restroom, from, to)) %>%
  left_join(admission %>% select(id,cat), by = c("id_restroom" = "id" ))

```





<!-- ################################# GARBAGE ############################## -->

## localization INFERENCE - inferred ADMISSIONS & HCW NOT PRESENT DURING THE WHOLE STUDY - TEMPORARY (assign first_time and last_time for individual --> TO KNOW WHEN THEY LEAVE)
```{r}
HCW_ids <- admission$id[admission$status == "PE"]
data_tot <- do.call(rbind,global_interaction)

## FOR PE-PA INTERACTIONS
a <- data_tot %>%
  filter(!(from_status == "PA" & to_status == "PA") & !(from_status == "PE" & to_status == "PE")) %>%
  mutate(id = ifelse(from_status == "PE", from, to)) %>% ## we want HCW ids
  group_by(id) %>%
  mutate(first_time = min(time), last_time = max(time)) %>%
  ungroup() %>%
  distinct(id, .keep_all = T) %>%
  filter(id %in% HCW_ids) %>%
  select(id, first_time, last_time)


## FOR PE-PE INTERACTIONS | FROM ids
b <- data_tot %>%
  filter(from_status == "PE" & to_status == "PE") %>%
  mutate(id = from) %>% 
  group_by(id) %>%
  mutate(first_time = min(time), last_time = max(time)) %>%
  ungroup() %>%
  distinct(id, .keep_all = T) %>%
  filter(id %in% HCW_ids) %>%
  select(id, first_time, last_time)


## FOR PE-PE INTERACTIONS | TO ids
c <- data_tot %>%
  filter(from_status == "PE" & to_status == "PE") %>%
  mutate(id = to) %>% 
  group_by(id) %>%
  mutate(first_time = min(time), last_time = max(time)) %>%
  ungroup() %>%
  distinct(id, .keep_all = T) %>%
  filter(id %in% HCW_ids) %>%
  select(id, first_time, last_time)

## BIND DFs
inferred_admission <- bind_rows(a, b, c) %>%
  group_by(id) %>%
  summarise(
    first_time = min(first_time),
    last_time = max(last_time)
    ) %>%
  ungroup()

print(inferred_admission)

rm(a)
rm(b)
rm(c)
rm(data_tot)


## THERE IS HCWs THAT ARE NOT PRESENT DURING THE STUDY --> WE CAN EXCLUDE THEM FROM THE localization INFERENCE MODEL
HCW_interacting_ids <- inferred_admission %>% pull(id)
length(HCW_interacting_ids)
HCW_not_here <- setdiff(HCW_ids, HCW_interacting_ids)
# data_tot %>% filter(from %in% HCW_not_here | to %in% HCW_not_here) 


## WE EXCLUDE THE HCWs NOT PRESENT DURING THE STUDY
# WE USE list_HCW_interacting INSTEAD OF HCW_ids
```

## INTERACTION localization
```{r}
## "NAIVE" INDIVIDUAL LOCATION
test_global_interaction <- lapply(global_interaction, function(df) {
  df <- df %>% mutate(localization = NA)
  
  # Join df with rooms based on df$from/to and rooms$id
  df <- df %>%
    left_join(rooms, by = c("from" = "id")) %>%  ## .x join
    left_join(rooms, by = c("to" = "id")) %>% ## .y join
    mutate(localization = case_when(
      from %in% c("001-0038-B-S", "001-0039-B-F") | to %in% c("001-0038-B-S", "001-0039-B-F") ~ rooms[rooms$id == "001-0038-B-S", "id_room"],
      from %in% c("001-0127-B-A", "001-0128-Z-K") | to %in% c("001-0127-B-A", "001-0128-Z-K") ~ rooms[rooms$id == "001-0127-B-A", "id_room"],
      from_status == "PE" & to_status == "PE" ~ rooms[rooms$id == "PE" , "id_room"],
      from_status == "PA" & to_status == "PE" ~ id_room.x,
      from_status == "PE" & to_status == "PA" ~ id_room.y,
    )) %>%
    select(-room.x, -id_room.x, -room.y, -id_room.y)
  
  ## Remove duplicated interactions (there is sometimes interactions recorded multiple times)
  df <- unique(df)
  
  return(df)
})

#### WE CAN UPDATE THIS localization MODEL TO USE:
## THE PREVIOUS INT OF INDIVIDUALS
## IF THERE IS ONLY 2 individuals interactings --> Corridor
## IF THERE IS MORE THAN TWO PATIENTS --> Corridor ? (c.f. overlap section )
## etc etc


#data_tot <- do.call(rbind, global_interaction)
```



## OVERLAP
```{r}
## MULTIPLE PATIENTS IN INTERACTION CLUSTERS (without double rooms)
u = do.call(rbind, cluster_info_list)


## TEMPORARY

# ta <- Sys.time()
# overlap <- data.frame()
# 
# 
# 
# for (t in 1:n_subdivisions){
#   for (individual in admission$id){
#     if (dim(data_tot %>% filter(from == individual | to == individual) %>% filter(time == t) %>% distinct(localization))[1] > 1){
#       overlap <- bind_rows(overlap, data_tot %>% filter(from == individual | to == individual) %>% filter(time == t) )
#     }
#   }
# }
# tb <- Sys.time()
# print(tb-ta)
# 
# ## 18min 07/05/24
# 
#     # previous_int <- data_tot %>% filter(from == individual | to == individual) %>% filter(time == t-1)
#     # current_int <- data_tot %>% filter(from == individual | to == individual) %>% filter(time == t)
#     # future_int <- data_tot %>% filter(from == individual | to == individual) %>% filter(time == t+1)
#     # overlap <- current_int %>% distinct(localization)
# write.csv2(data = overlap, file = file.path(nodscov2_path, "overlap-RP-test.csv"), row.names = F, header = T)

overlap <- read.csv2(file = file.path(nodscov2_path, "overlap-RP-test.csv"))
## Only checking for multiple CHAMBER assignation
overlap_bis <- overlap %>%
  filter(!(from_status == "PE" & to_status == "PE")) %>% 
  filter(!(from_status == "PA" & to_status == "PA")) %>%
  mutate(id = if_else(from_status == "PE", from, to)) ## ID OF THE HCW


result <- overlap_bis %>%
  group_by(id, time) %>%
  mutate(unique_loc = n_distinct(localization)) %>% # Nb of distinct localization assigned to each HCWs 
  filter(unique_loc > 1) %>%
  select(-unique_loc)

View(result)

## Distinct nb of room each HCW is assigned to during the 
result %>% group_by(id) %>% distinct(localization, .keep_all = T) %>% summarise( n = n())
```







